### 2016-03-30 ms.tex
initial commit

%\documentclass[preprint]{aastex}
%\documentclass[preprint2]{aastex}
%\documentclass{aastex}
\documentclass[iop]{emulateapj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{natbib}
\usepackage{color}
\usepackage{hhline}
\usepackage{subfigure}
%\usepackage{bm,upgreek}
\usepackage{xspace}

\usepackage{mymacros}
\usepackage{affils} % Peter Williams' affiliation macro

\bibliographystyle{apj}

\begin{document}

\title{First Season MWA EoR Power Spectrum Results at Redshift 7}
\shortauthors{Beardsley et al.}
\shorttitle{First Season MWA EoR}

\def\myemail{\altaffilmark{*}}
\def\myemailtxt{\altaffiltext{*}{e-mail: Adam.Beardsley@asu.edu}}

\DeclareAffil{ASU}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
\DeclareAffil{UW}{University of Washington, Department of Physics, Seattle, WA 98195, USA}
\DeclareAffil{UWeSci}{University of Washington, eScience Institute, Seattle, WA 98195, USA}
\DeclareAffil{Brown}{Brown University, Department of Physics, Providence, RI 02912, USA}
\DeclareAffil{SKASA}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}
\DeclareAffil{RU}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}
\DeclareAffil{CfA}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
\DeclareAffil{ANU}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}
\DeclareAffil{CAASTRO}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\DeclareAffil{Haystack}{MIT Haystack Observatory, Westford, MA 01886, USA}
\DeclareAffil{MIT}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}
\DeclareAffil{Curtin}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}
\DeclareAffil{USydney}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}
\DeclareAffil{Dunlap}{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON M5S 3H4, Canada}
\DeclareAffil{Victoria}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}
\DeclareAffil{UWisc}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}
\DeclareAffil{UMichigan}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}
\DeclareAffil{UMelbourne}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}
\DeclareAffil{CASS}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}
\DeclareAffil{Tata}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}
\DeclareAffil{ASTRON}{Netherlands Institute for Radio Astronomy (ASTRON), PO Box 2, 7990 AA Dwingeloo, The Netherlands}
\DeclareAffil{RRI}{Raman Research Institute, Bangalore 560080, India}
\DeclareAffil{NRAO}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}
\DeclareAffil{UWA}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}
\DeclareAffil{Berkeley}{Department of Astronomy, UC Berkeley, Berkeley, CA 94720, USA}
\DeclareAffil{RAL}{Radio Astronomy Laboratory, UC Berkeley, Berkeley, CA 94720, USA}
\DeclareAffil{BCCP}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, USA}

\affilauthorlist{
A.~P.~Beardsley\affils{ASU,UW}\myemail,
B.~J.~Hazelton\affils{UW,UWeSci},
I.~S.~Sullivan\affils{UW},
J.~C.~Pober\affils{Brown,UW},
P.~Carroll\affils{UW},
N.~Barry\affils{UW},
M.~F.~Morales\affils{UW}, 
Daniel~C.~Jacobs\affils{ASU},
G.~Bernardi\affils{SKASA,RU,CfA},
Judd~D.~Bowman\affils{ASU},
M.~P.~Busch\affils{ASU},
F.~Briggs\affils{ANU,CAASTRO},
R.~J.~Cappallo\affils{Haystack}, 
B.~E.~Corey\affils{Haystack}, 
A.~de~Oliveira-Costa\affils{MIT},
Joshua~S.~Dillon\affils{Berkeley, RAL, BCCP,MIT},
D.~Emrich\affils{Curtin},
A.~Ewall-Wice\affils{MIT},
L.~Feng\affils{MIT},
B.~M.~Gaensler\affils{USydney,CAASTRO,Dunlap}, 
R.~Goeke\affils{MIT},
L.~J.~Greenhill\affils{CfA},
J.~N.~Hewitt\affils{MIT},
N.~Hurley-Walker\affils{Curtin},
M.~Johnston-Hollitt\affils{Victoria},
D.~L.~Kaplan\affils{UWisc}, 
J.~C.~Kasper\affils{UMichigan,CfA}, 
HS Kim\affils{UMelbourne,CAASTRO},
E.~Kratzenberg\affils{Haystack}, 
E.~Lenc\affils{USydney,CAASTRO},
J.~Line\affils{UMelbourne,CAASTRO},
A.~Loeb\affils{CfA},
C.~J.~Lonsdale\affils{Haystack}, 
M.~J.~Lynch\affils{Curtin}, 
B.~McKinley\affils{UMelbourne,CAASTRO},
S.~R.~McWhirter\affils{Haystack},
D.~A.~Mitchell\affils{CASS,CAASTRO}, 
E.~Morgan\affils{MIT}, 
A.~R.~Neben\affils{MIT},
N.~Thyagarajan\affils{ASU},
D.~Oberoi\affils{Tata}, 
A.~R.~Offringa\affils{ASTRON,CAASTRO}, 
S.~M.~Ord\affils{Curtin,CAASTRO},
S. Paul\affils{RRI},
B.~Pindor\affils{UMelbourne,CAASTRO},
T.~Prabu\affils{RRI}, 
P.~Procopio\affils{UMelbourne,CAASTRO},
J.~Riding\affils{UMelbourne,CAASTRO},
A.~E.~E.~Rogers\affils{Haystack}, 
A.~Roshi\affils{NRAO}, 
N.~Udaya~Shankar\affils{RRI}, 
Shiv~K.~Sethi\affils{RRI},
K.~S.~Srivani\affils{RRI}, 
R.~Subrahmanyan\affils{RRI,CAASTRO}, 
M.~Tegmark\affils{MIT},
S.~J.~Tingay\affils{Curtin,CAASTRO}, 
C.~M.~Trott\affils{Curtin,CAASTRO},
M.~Waterson\affils{Curtin,ANU},
R.~B.~Wayth\affils{Curtin,CAASTRO}, 
R.~L.~Webster\affils{UMelbourne,CAASTRO}, 
A.~R.~Whitney\affils{Haystack}, 
A.~Williams\affils{Curtin}, 
C.~L.~Williams\affils{MIT},
C.~Wu\affils{UWA},
J.~S.~B.~Wyithe\affils{UMelbourne,CAASTRO}
}

\begin{abstract}
The Murchison Widefield Array (MWA) has collected hundreds of hours of Epoch of 
Reionization (EoR) data and now faces the challenge of overcoming foreground and 
systematic contamination to reduce the data to a cosmological measurement. We introduce 
several novel analysis techniques such as cable reflection calibration, high resolution 
gridding kernels, diffuse foreground model subtraction, and quality control methods. Each 
change to the analysis pipeline is tested against a two dimensional power spectrum figure 
of merit to demonstrate improvement. We incorporate the new techniques into a deep 
integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.17 \times 10^4$ mK
$^2$ at $k=0.24$ h~Mpc$^{-1}$ and $z=6.8$, consistent with other published limits, and a 
modest improvement (factor of 1.7) over previous MWA results. While our result is 
systematic limited, we identify several strategies to overcome these systematics in future 
analysis.
\end{abstract}
\keywords{cosmology: observations - cosmology: reionization}
\maketitle

\section{Introduction}

Detection and characterization of the cosmic dark ages and the Epoch of Reionization 
(EoR) have the potential to inform our picture of the cosmos in ways analogous to the 
Cosmic Microwave Background (CMB) over the past several decades. The EoR in 
particular is rich with both cosmological and astrophysical dynamics as early-universe linear 
evolution gives way to non-linear structure growth and stars and galaxies reionize the 
intergalactic medium (IGM).

Several probes are being used to investigate the EoR, but to date, a direct detection eludes 
researchers. Studies of the polarization of the CMB have placed integrated constraints on 
the timing of reionization \citep[e.g.][]{Planck:2015b, Planck:2015, WMAP9}. Meanwhile, 
observations of highly redshifted quasars have placed upper bounds on redshifts by which 
reionization is complete. For example, \citealt{Fan:2006a} showed that reionization must be 
complete by $z \approx 6$, a result which was confirmed independent of model by 
\citealt{McGreer:2015}. Deep optical and infrared galaxy surveys are also beginning to 
reach the redshifts necessary to further constrain reionization \citep[e.g.][]{Bouwens:2014}, 
and the James Webb Space Telescope will improve on their sensitivity 
\citep{Gardner:2006}.

The 21 cm hyperfine transition from neutral hydrogen residing in the IGM during reionization 
offers another promising method to study the EoR. Not only is the 21cm signal a 
\emph{direct} probe of the IGM, but, due to the narrow width of the transition and the 
relationship between observed frequency and line-of-sight distance, it can be used to map 
the full three dimensional space of the epoch. (For reviews, see \citealt{Furlanetto:2006} 
and \citealt{Morales:2010}.) The first generation of instruments with primary science goals 
to detect the 21cm EoR signal have been built, including the GMRT (Giant Metrewave 
Radio Telescope, \citealt{Paciga:2013}), LOFAR (LOw Frequency Array\footnote{http://
www.lofar.org}, \citealt{Yatawatta:2013}), PAPER (Precision Array for Probing the Epoch of 
Reionization\footnote{http://eor.berkeley.edu}, \citealt{Parsons:2010}), and the MWA 
(Murchison Widefield Array\footnote{http://www.mwatelescope.org}, \citealt{Tingay:2013}). 
Due to relatively low signal to noise, these instruments aim for a statistical measurement of 
the EoR in the form of a cosmological power spectrum. Meanwhile, the second generation 
21cm EoR machines is on its way with the Hydrogen Epoch of Reionization Array (HERA
\footnote{http://reionization.org}, D.~R.~DeBoer, et al. 2016, in prep), which will further 
refine the power spectrum measurement in early build-out stages, but will ultimately be 
capable of imaging the ionized bubbles of reionization in its later stages 
\citep{Beardsley:2015,Malloy:2013}.

Using the first generation of instruments, several upper limits have been placed on the 21 cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}, and \citealt{Pober:2015} was able to place constraints on physical reionization models. However, much work is to be done to understand the data produced by these arrays. Foreground subtraction and isolation has emerged as a priority in the field. Central to most analysis strategies is the concept of an ``EoR window" -- the region of Fourier space where spectrally smooth foregrounds have been isolated from the isotropic (spherically symmetric in Fourier space) cosmological signal \citep{Morales:2006, Bowman:2009}. More recent studies have shown the existence of a foreground ``wedge", the result of instrumental mode mixing, throwing power from spectrally smooth foregrounds to higher Fourier modes \citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2014, Liu:2014a, Liu:2014b, Hazelton:2013, Pober:2013, Vedantham:2012, Morales:2012, Datta:2010}. Despite this setback, the EoR window is preserved above the wedge, and the field is pushing forward with several analysis pipelines under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in prep; D.~A.~Mitchell et al. 2016, in prep; D.~C.~Jacobs et al. 2016, in review; ][]{Trott:2016, Dillon:2013, Trott:2012}.

This paper serves two purposes: to demonstrate several new analysis techniques and their impact on power spectrum estimation, and to present the first attempt at a deep integration power spectrum from the MWA. Using a three hour test set of data, we introduce several novel techniques including calibration of cable reflection contamination, high resolution gridding kernels, subtraction of a diffuse foreground model, and development of quality control methods which will be crucial for deeper integrations. We apply these new techniques to a deep integration of data from the first semester of MWA observations (August, 2013 -- November, 2013) on a single EoR field and redshift range, $6.2<z<7.5$. While not expecting to detect the EoR with less than a hundred hours of observations, this intermediate integration will serve to identify and diagnose systematics, allowing for improved analysis in future work.

The remainder of this paper is organized as follows. In Section~\ref{sec:MWA} we briefly describe the MWA instrument and the observations used in this work, in Section~\ref{sec:analysis} we describe our analysis pipeline, in Section~\ref{sec:techniques} we describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our efforts to apply the analysis pipeline to a deep data integration, and we discuss future work in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM cosmology with $\Omega_m=0.73$, $\Omega_\Lambda=0.27$, and $h = 0.7$, consistent with WMAP seven year results \citep{Komatsu:2011}. All distances and wavenumbers are in comoving coordinates.

\section{The Murchison Widefield Array and Observations}\label{sec:MWA}
The Murchison Widefield Array is one of several first generation radio interferometers with a primary science goal of detecting the 21cm EoR power spectrum. The remote Australian outback offers relative isolation from man-made radio frequency interference (RFI) such as FM radio, or TV stations. A recent study of the RFI environment at the Murchison Radio Observatory can be found in \citealt{Offringa:2015}.

While the 21 cm EoR signal is priority, the MWA is a general observatory serving several science programs beyond cosmology including galactic and extragalactic surveys, time domain astrophysics, solar monitoring, and ionospheric science. The array was thus designed with these programs in consideration and the layout was optimized using a pseudo-random antenna placement algorithm \citep{Beardsley:2012} to obtain a well behaved point spread function while retaining a dense core for EoR sensitivity \citep{Beardsley:2013}. This is in contrast to more pointed EoR experiments like PAPER, which utilize a highly redundant layout to enhance sensitivity. Redundant arrays can leverage symmetries of the instrument for quick calibration and analysis, but have poor point spread functions, making foregrounds more difficult to characterize. Conversely we use the high imaging capability of the MWA to calibrate and subtract foregrounds based on sky models. A full description of the science capabilities of the array is found in \citealt{Bowman:2013}.

The technical design of the MWA is reviewed in \citealt{Tingay:2013}, and we highlight a few key characteristics that will become important in our analysis of the data. Each antenna of the MWA comprises 16 dual-polarization dipoles placed on a regular grid, lying on a ground screen. The radio frequency signals from these dipoles feed into an analog beamformer which uses physical delays to ``point" the antenna. The MWA contains 128 of these antennas, with a tightly packed core of radius 50 m, and extending out to a radius 1.5 km for higher resolution calibration and imaging.

The beamformed signals (one for each polarization) are then transmitted to receivers in the field, which digitize the signal and perform a first stage coarse frequency channelization of the data (1.28 MHz sub-bands)\citep{Prabu:2015}. This channelization applies a filter shape and aliases edge channels, which will later be flagged in our analysis. The observer now selects 24 sub-bands (30.72 MHz total bandwidth) to pass onto the correlator via fiber optic link. The correlator further channelizes the data to 10 kHz resolution, cross multiplies signals between antennas to form visibilities, and averages in time and frequency to a resolution specified by the observer. For the data in this work, the correlator output resolutions were 0.5 seconds in time and 40 kHz in frequency. The data are then written to disk on a cadence of 112 seconds, constituting a single observation, or snapshot.

The EoR observing campaign has adopted a ``drift and shift" tracking strategy -- we point the telescope towards a sky field of interest, allow the field to drift overhead for about 30 minutes until it begins to leave our field of view, then repoint the instrument at the field. The telescope is thus only pointed at discrete positions, or ``pointings". This tracking is repeated until the field is too low in the sky to track. We have identified three EoR fields relatively devoid of galactic emission and bright extragalactic sources for observing: ``EoR0" (RA $=0.00$ h, dec $= -27^\circ$), ``EoR1" (RA $=4.00$ h, dec $= -27^\circ$), and ``EoR2" (RA $=11.33$ h, dec $= -10^\circ$). In addition, we observe these fields in high and low bands centered at 182 MHz ($z\approx6.8$) and 154 MHz ($z\approx8.2$) respectively.

The data for this work includes two sets. First we use a set of 94 high band observations of the EoR0 field from August 23, 2013, which were taken early in telescope operations and found to be particularly well behaved. The MWA EoR collaboration has designated this set as a ``golden data set'', which is used to build analysis tools and compare early results. All techniques demonstrated here will use this golden data set. In Section~\ref{sec:deep} we will use a larger data set to move toward a deep integration. This data set consists of all EoR0 high band observations beginning August 23, 2013 (including the golden data set), and concluding when the field was no longer accessible for the season: when the sun was above the horizon for most or all of the field's transit. The final observation of this set was on November 29, 2013. The individual snapshots are 112 seconds of data at 0.5 second, 40 kHz resolution. In total we analyze 2,780 snapshots, or about 86.5 hours of data.

\section{Analysis Pipeline}\label{sec:analysis}
In order to ensure consistency in analysis, the international MWA EoR collaboration has defined two independent reference analysis pipelines. The details of this strategy are outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al. 2016, in prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we give an overview below.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{pipe.pdf}
\caption[Pipeline diagram]{
Schematic of the analysis pipeline used in this work. The raw correlator data is preprocessed by performing RFI and other flagging. Then the data are calibrated and imaged using an iterative foreground modeling approach with the FHD package. Finally, a power spectrum is formed using the \eppsilon package.
\label{fig:pipe}
}
\end{center}
\end{figure}

\subsection{Preprocessing}\label{subsec:preprocessing}
The preprocessing step converts the data from the non-standard memory dump format from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, performs flagging, averages in time and freqeuncy, and writes to disk. For this step we use the \cotter package, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://aoflagger.sourceforge.net/}} to perform RFI flagging \citep{Offringa:2010}.

Besides RFI, we manually flag data to remove three other effects. As mentioned in Section~\ref{sec:MWA}, the edges of the coarse bands contain high levels of aliasing from the filter applied in the digital receivers. We flag two 40 kHz channels on either side of the coarse band edges (total of four channels per coarse band edge). In principle the aliasing could be calibrated out and these channels could be recovered, but this is left for future work. Second, early data from the MWA also contained some instances where antennas were not pointed properly at the beginning of observations due to a beamformer error. This problem has since been resolved, but exists in our data. We therefore flag the first two seconds of each observation to avoid any potentially mis-pointed data. Finally, we flag the central fine channel of each coarse band because it corresponds to the DC mode of that sub-band and can easily float, washing out useful information.

In the final step of preprocessing, \cotter averages the data to 2 second, 80 kHz resolution and writes to disk. At this stage each snapshot is contained in a single UVFITS file, which serves as the base unit for calibration and imaging.

\subsection{Calibration and Imaging}\label{subsec:cal_imaging}
The next step in our pipeline is to calibrate the visibilities. As shown in Figure~\ref{fig:pipe}, a sky model is derived from our imaged data, which feeds back into the calibration. This is naturally an iterative process as the sky model is refined with improved calibration solutions. We will describe the sky model in detail in Section~\ref{sec:techniques}, but here we present the production mode of analysis after the model has been determined.

Calibration is accomplished within the FHD package in two steps. First we match the raw data to model visibilities formed using a realistic simulation of the array response to our foreground model. This step results in independent complex gains for each antenna, frequency channel, and polarization. In the second step we impose restrictions on these gains motivated by our understanding of the spectral response of the instrument. By reducing the number of free parameters in this step we increase our signal to noise on calibration solutions and avoid absorbing unmodeled confusion source flux into our gain solutions which has been shown to contaminate the EoR window \citep{Barry:2016}.

In the first calibration step we allow our complex gains to account for any direction-independent response on a per antenna, per frequency channel, per polarization basis. To define our gains in this way, we have made two simplifications. First we push all direction-dependence of the antenna response into the model of the primary beam. FHD is capable of using separate models for each antenna, though this has not yet been implemented for the MWA due to lack of individual models. The second simplification is to ignore any cross terms between our different axes, for example a mutual coupling between two antennas. In principle these terms would introduce baseline dependent gains, rather than antenna dependent. The MWA has not yet seen evidence of these terms, and so we currently neglect them in our solutions.

Under these assumptions we can express the measured, uncalibrated visibility for an antenna pair $(i,j)$ as
\begin{equation}
V'_{ij}(\nu) \approx g_i(\nu)g^*_jV_{ij}(\nu),
\end{equation}
where $g_i(\nu)$ and $g_j(\nu)$ are the complex gains for antennas $i$ and $j$ respectively. Because we are treating polarizations independently, we allow the antenna subscript to run over both East-West (E-W) and North-South (N-S) polarizations.

FHD utilizes the StEFCal algorithm described in \citealt{Salvini:2014} to find the minimum $\chi^2$ estimate with respect to the complex gains. The result of this operation is estimated gains for every antenna, frequency channel, and polarization. However, with certain known properties of the antenna response we can reduce the number of free parameters in our solution. This takes us to the second step of calibration.

Our initial gain model included an amplitude bandpass common to all antennas, $B(\nu)$, and an antenna dependent low order polynomial in frequency. Mathematically we can express our restricted gain as
\begin{equation}\label{eq:cal1}
\hat{g}_i(\nu)=B(\nu)P_i(\nu),
\end{equation}
where the polynomial term can be further decomposed as
\begin{equation}
P_i(\nu) = (A_{i,0} + \nu A_{i,1} + \nu^2 A_{i,2})e^{i (\phi_{i,0} + \nu \phi_{i,1})}
\end{equation}
The coefficients $B(\nu)$, $A_{i,n}$, and $\phi_{i,n}$ are real quantities. This model allows 
us to capture arbitrary spectral response due to common antenna factors (such as the 
polyphase filter shapes or phased array response), as well as slowly varying antenna-
dependent deviations. We also found it necessary to include terms dependent on the 
beamformer to receiver cable length, which we will discuss in Subsection~\ref{sec:cables}.

Once all calibration terms are found, we complete the calibration by dividing the raw data by 
the gain estimates to produce calibrated visibilities. The entire calibration process is done 
for every snapshot of EoR data, providing both a two-minute resolution time dependence of 
calibration solutions, as well as model visibilities which are used for foreground subtraction 
and diagnostic purposes.

After calibration, we form snapshot image cubes (frequency mapping to line-of-sight 
direction). The visibilities are gridded using the primary beam as the gridding kernel, placing 
the data in the holographic frame, which has been shown to be the optimal frame for 
combining images in the sense that it preserves all information for parameter estimation 
\citep{Morales:2009,Bhatnagar:2008}. We use a simulation based beam model for MWA 
antennas developed by \citealt{Sutinjo:2015}. At this stage we also average in frequency by 
a factor of two by gridding pairs of frequency channels to the same $uv$ plane, resulting in 
a frequency resolution of 160 kHz.

The gridded $uv$ data are then Fourier transformed to create sky-frame images. To avoid 
aliasing we image out 90$^\circ$ from phase center (gridding resolution of a half 
wavelength), and crop the image. We found that cropping the image based on beam value 
resulting in hard edges in integrated images from different snapshots having beams pointed 
in slightly different directions. To avoid the hard edges, we predetermine a set of HEALPix 
pixels to interpolate to, and use the same set for all snapshots on a given field. The final 
cropped field of view for this work is a 21$^\circ$ square centered at RA~$=0$ h, dec~
$=-27^\circ$.

In principle the foregrounds could be subtracted from the data immediately after calibration, 
before gridding and imaging. However, for diagnostic reasons, we have found it beneficial to 
carry the model through the entire pipeline, and only subtract just before squaring to power 
spectrum units, allowing to form power spectra of the dirty, model, and residual data.

FHD provides all inputs needed for the \eppsilon package, which include weights cubes (for 
proper accumulation of data), variance cubes (for error propagation), and even/odd 
interleaved data cubes (for an unbiased estimator and a direct measurement of the noise). 
We also retain both East-West and North-South polarizations. At this time we can remap 
our coordinates to cosmological units according to the relationships given in 
\citealt{Morales:2004}, where angular and frequency units $(\theta_x,\theta_y,f)$ map to 
cosmological distance units $(r_x,r_y,r_z)$. Often $r_z$ is referred to as the line of sight 
dimension, and denoted as $r_{||}$. Similarly, $(r_x,r_y)$ is the plane perpendicular to the 
line of sight and is denoted as $\mathbf{r_{\perp}}$.

\subsection{Power Spectra}
In the final steps of our pipeline we integrate the snapshot image cubes, and calculate a 
power spectrum estimate. Though the integration step is formally an imaging component, 
we conceptually group it with the power spectrum step. This is because all steps of the 
pipeline up to here have been performed on a per-snapshot basis (no communication 
between snapshots beyond foreground modeling), and the integration step can be used to 
select subsets of data for diagnosing power spectrum artifacts. The images produced by 
FHD are in the holographic frame, which is already properly weighted for combining 
images, so the integration is simply adding the cubes together, and propagating the 
weights.

The \eppsilon package performs a discrete Fourier transform (DFT) on each $r_{||}$ slice of 
the integrated HEALPix cube, forming a cube in $(\mathbf{k}_{\perp},r_{||})$, where $
\mathbf{k}_{\perp}$ represents the cosmological wavenumber in the plane perpendicular to 
our line of sight, and $r_{||}$ is the distance to the observed redshift slice along the line of 
sight. The Fourier transform along the $r_{||}$ dimension is treated separately due to 
incomplete $uv$ sampling and flagged frequency channels, which leads to structure in the 
frequency sampling along any given $k_{\perp}$ pixel. We thus adopt the Lomb-Scargle 
least-squares method to determine the orthogonal eigenfunctions given our sampling 
function and estimating the total power in each $k_{||}$ mode \citep{Scargle:1982}. In 
addition, because the spectrally smooth foregrounds contain vastly more power than the 
expected EoR signal, we apply a Blackman-Harris window function prior to the $r_{||}$ to 
$k_{||}$ transform. This has the effect of trading off lower effective bandwidth for higher 
dynamic range.

After squaring and dividing by our observation window function \citep{Bowman:2006}, we 
arrive in three dimensional power spectrum space. We use the even/odd interleaved cubes 
to form a signal (odd plus even) and noise (odd minus even) power spectrum, which we 
subtract from one another to form an unbiased estimate of our signal power. This is 
mathematically equivalent to cross multiplying the even and odd cubes. The three 
dimensional power spectrum cube can next be averaged in annuli to form two dimensional 
power spectra, or spherical shells to form one dimensional power spectra where we will 
ultimately constrain the EoR.

\begin{figure}
\begin{center}
\includegraphics[width=.9\columnwidth]{example_ps.pdf}
\caption{
An example two dimensional, E-W polarization residual power spectrum formed using the 
three hour golden data set. The foreground wedge dominates the region below the solid 
black horizon line, while regions above are mostly noise-like with the exception of horizontal 
coarse band harmonic lines. 
\label{fig:example_ps}
}
\end{center}
\end{figure}

An example two dimensional residual power spectrum formed from the three hour golden 
data set is shown in Figure~\ref{fig:example_ps}. The bulk of the residual power is in the 
so-called foreground ``wedge", indicated with the diagonal black lines where the solid line 
corresponds to sky emission at the horizon, and the dashed lines corresponds to emission 
at the edge of the MWA field of view. Above the wedge we see horizontal lines of 
contamination due to the periodic frequency sampling function. These lines are often 
referred to as the coarse band harmonics. We see vertical streaks at high $k_{||}$ and high 
$k_{\perp}$. These are due to sparse $uv$ sampling beyond the dense core of the MWA 
(starting $\sim70\lambda$), and the foreground power getting thrown to high spectral 
modes. Between the coarse band lines and to the left of the vertical streaks we see regions 
which contain both positive and negative (indicated by blue on the color bar) pixels. These 
regions are where we have successfully isolated the foregrounds and retained a noise-like 
EoR window in the three hour integration.

\section{Novel Analysis Methods}\label{sec:techniques}
\textcolor{red}{Needs a better section title}

The two dimensional power spectrum is a useful figure of merit (FoM) as we improve and 
refine our analysis pipeline. Foregrounds and systematics often manifest with characteristic 
shapes in this space, enabling us to diagnose problems and quantify improvements 
\citep{Morales:2012}. We use the MWA 3 hour ``golden'' data set from August 23, 2013, to 
repeatedly form power spectra to test and refine our analysis. While an exhaustive catalog 
of these improvements would be unsuited for this article (and likely bore the reader), we 
demonstrate the utility of the 2D power spectrum as a FoM with a few key techniques we 
have employed in our analysis.

\subsection{Cable Dependent Calibration}\label{sec:cables}

Early in our analysis it became apparent that the bandpass of each MWA antenna requires 
more free parameters than those described in equation~\ref{eq:cal1}. In particular, differing 
beamformer to receiver cables lead to different bandpass shapes due to signal attenuation. 
We therefore allow the amplitude bandpass factor to depend on cable length, $B_{\alpha}
(\nu)$, where $\alpha$ denotes the cable type.\footnote{For logistical purposes the 
beamformer to receiver cables were installed in six set lengths. Cables of length 90, 150, 
and 230 meters are RG-6, while 320, 400, and 524 meter cables are LMR400-75.}

The top panel of Figure~\ref{fig:cables} shows a 2D power spectrum using the gain model 
described so far. Three of the horizontal lines in the EoR window can be attributed to the 
coarse band gaps, as they reside at the harmonics expected for 1.28~MHz periodic 
sampling. But the sampling cannot account for the fourth line, highlighted by the arrow. The 
corresponding delay time of the line, $\tau \approx 1.23$~$\mu$s, corresponds almost 
exactly to twice the signal travel time through the 150 meter cables (with velocity 0.81c). We 
therefore introduced a reflection term into our gain model, which allows our restricted gains 
to account for the interference of the incident signal with a round-trip reflected signal in the 
cable. The full gain model is expressed as
\begin{equation}\label{eq:cal2}
\hat{g}_i(\nu)=B_{\alpha}(\nu)\left(P_i(\nu)+R_i(\nu)\right),
\end{equation}
where the reflection term can be further decomposed as
\begin{equation}
R_i(\nu) = R_{i,0} e^{-2\pi i \tau_{i} \nu}.
\end{equation}
The reflection coefficient, $R_{i,0}$ is allowed to be complex, while the reflection delay, 
$\tau_i$ is real. After fitting for all other parameters, we fit for the reflection mode. This is 
done for antennas with suspected reflections, the most offensive of which is seen in the 
antennas with cables of 150 meters. Because the cables were not cut at exact lengths 
(variations on order tens of centimeters), we solve for both the reflection coefficient and 
delay by performing a direct Fourier transform to a highly over resolved delay grid and 
selecting the mode where the reflection amplitude is largest.

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_pre.pdf}}
~
\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_post.pdf}}
\caption{
\emph{Top:} Single polarization dirty power spectrum formed from the golden data set, 
before implementing cable reflection fitting into the calibration loop. The black arrow points 
to a horizontal band at $k_{||} \approx 0.6$~h~Mpc$^{-1}$, which cannot be accounted for 
by the coarse bands. \emph{Bottom:} After we implement the cable reflection fitting in our 
calibration solutions, we see the reflection line disappears.
\label{fig:cables}
}
\end{center}
\end{figure}

The resulting 2D power spectrum after fitting for cable reflections is shown in the bottom 
panel of Figure~\ref{fig:cables}, where the reflection line is suppressed below the noise 
level. This example demonstrates the power of the 2D power spectrum as a figure of merit. 
The power in the reflection line was about five orders of magnitude below the foregrounds, 
making it very difficult to detect in image-based metrics. However the power spectrum is 
specifically designed to be sensitive to low-level spectral structure, and using the two 
dimensional spectrum allows us to identify the ``shape'' of contamination, enabling a 
precise diagnosis.

\subsection{Gridding Kernel Resolution}
A similar, low level effect which had the potential to contaminate the EoR window is shown 
in Figure~\ref{fig:beam_res}. The spectra shown are the \emph{model} spectra -- calculated 
by propagating the sky model visibilities through the entire pipeline. Despite our foreground 
model not containing spectral structure, the EoR window in the left panel seems to have a 
floor at a level $\sim 10^7$~mK$^2$~h$^{-3}$~Mpc$^3$, comparable to predicted EoR 
signals. In addition there is a faint line in the upper-left of the plot which has the same slope 
as the wedge, but seems to originate far beyond the horizon.

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=.9\columnwidth]{before_beam_resolution_golden.pdf}}
~
\subfigure{\includegraphics[width=.9\columnwidth]{after_beam_resolution_golden.pdf}}
\caption{
\emph{Top:} Single polarization model power spectrum demonstrating the contamination in 
the EoR window when using insufficient gridding kernel resolution. The window has a floor 
comparable to an expected EoR signal, and a faint super-horizon line appears at high 
$k_{||}$. \emph{Bottom:} Model power spectrum after increasing the gridding kernel 
resolution from 0.04 wavelengths to 0.007 wavelengths. The floor is now far below the 
expected EoR signal level. 
\label{fig:beam_res}
}
\end{center}
\end{figure}

The source of this floor and super-horizon line ended up being the resolution at which we 
formed the gridding kernel when gridding visibilities. In the interest of computational speed 
and efficiency, the kernel is pre-calculated at a high resolution, then a nearest neighbor 
lookup table is used to approximate the beam values at discrete pixels. The kernel 
resolution used in the top panel of Figure~\ref{fig:beam_res} was 0.04 wavelengths -- much 
smaller than the half wavelength grid corresponding to horizon to horizon imaging. 
However, as a baseline migrates in $\emph{uv}$ coordinates across frequencies, it 
undergoes discrete steps between kernel values used. This effectively results in small 
baseline position errors which shift periodically in frequency, resulting in power being thrown 
up into the window and a relatively strong harmonic at the frequency of the shifting (the faint 
line in the upper left of the window). While we illustrate this effect with a model power 
spectrum, the same problem exists in the data, but is below the noise levels at three hours 
of integration.

We resolved this issue by increasing the resolution at which we form the kernel. While the 
most accurate answer is to model at infinite resolution, it is not feasible to do so 
computationally. Instead we chose a resolution at which the effect no longer materially 
impacts the power spectrum. With experimentation we found a kernel resolution of 0.007 
wavelengths was sufficient. The resulting model power spectrum is shown in the bottom 
panel of Figure~\ref{fig:beam_res}. The contamination within the EoR window now drops 
significantly below the predicted cosmological signal levels.

\subsection{Improving Point Source Model}

Our pipeline uses two modes of FHD -- the full deconvolution mode to identify point sources 
and build a catalog, and a production mode where we calibrate using the sky model and 
subtract it from the data without further fitting. Because full deconvolution on every 
observation from the MWA is computationally not feasible, we currently restrict ourselves to 
the golden data set to build our model. The process of building the catalog is presented in 
P.~A.~Carroll et al. 2016 (in review). They applied machine learning classification methods 
to select reliable detections from the full deconvolution FHD mode, culminating in the KGS 
catalog. The work here uses an early iteration of the KGS catalog that was available at the 
time of analysis.

It has been shown that subtracting a foreground model strictly within the main lobe of the 
primary beam will not be sufficient to suppress the power spectrum wedge and unlock the 
EoR window \citep{Pober:2016, Thyagarajan:2015, Thyagarajan:2015b}. In principle we 
can repeat the model building described above using additional MWA observations pointed 
away from our field of interest. But until that work is complete we supplement the extent of 
our point source model using additional catalogs. We accomplish this through a hierarchical 
catalog pulling from our early KGS catalog, the MWA Commissioning Survey\footnote{The 
more complete GLEAM Survey \citep[][Hurley-Walker et al., in collaboration review]
{Wayth:2015} was not available at the time of analysis.} \citep[MWACS, ][]
{Hurley-Walker:2014}, Culgoora \citep{Slee:1977}, and the Molonglo Reference Catalog 
\citep[MRC, ][]{Large:1981}. Source fluxes are prioritized in this order based on our 
confidence in their predicted flux at 182 MHz. We first cluster the source lists to avoid 
redundant sources, using a 3.5 arcmin neighborhood radius, then select the flux from the 
highest priority catalog. Spectral indices were obtained from the MWACS and Culgoora 
catalogs when available, otherwise a two-point spectral index was estimated for Culgoora-
MRC matches or MRC-SUMSS matches. All other sources were given a spectral index of 
$-0.8$. The spectral index was used to extrapolate the flux from the catalog frequency to 
182 MHz, but a uniform spectral index of $-0.8$ is used within our band when forming 
model visibilities for calibration and foreground subtraction.

The resulting hierarchical catalog is shown in Figure~\ref{fig:master_catalog}. The EoR0 
field corresponds to the red FHD source patch. All sources above the horizon and within a 
primary beam value greater than 1\% maximum (including sidelobes) are included in both 
our calibration and foreground subtraction models.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{master_catalog.png}
\caption{
Hierarchical catalog used for foreground subtraction. This catalog combines the source lists 
from our own FHD catalog, the MWACS catalog, Culgoora sources, and the MRC, 
prioritizing in that order. The EoR0 field corresponds to the red FHD patch, while we use the 
other catalogs to fill in the sidelobes of the MWA. The size of each dot is proportional to the 
182~MHz flux of the source, clipped at 20~Jy.
\label{fig:master_catalog}
}
\end{center}
\end{figure*}

To show the effect our hierarchical catalog has on the power spectrum figure of merit, we 
ran our entire analysis pipeline on the golden data set with two foreground models -- first 
with only the MWACS catalog, and again with the full hierarchical catalog. We then 
compare the resulting 2D power spectra to inspect whether the new catalog results in more 
accurate calibration and foreground subtraction.

Because we use the input foreground model to calibrate our visibilities, the gain estimates 
for our two runs differed. In particular we saw the overall flux scale of the calibrated 
visibilities was higher when using the full hierarchical catalog. In order to put both residual 
2D power spectra onto the same scale for comparison, we first divide each pixel by the 
corresponding dirty power spectrum pixel, then subtract to arrive at a ratio difference. 
\begin{equation}\label{eq:diff_ratio}
\mathtt{ratio\;difference = \frac{residual_1}{dirty_1} - \frac{residual_2}{dirty_2}}
\end{equation}
Here we use subscript 1 to represent the MWACS catalog spectra, and 2 for the 
hierarchical catalog spectra. The ratio difference is shown in Figure~\ref{fig:mwacs_ratio}. 
The entire wedge being positive (blue) demonstrates that using the new catalog resulted in 
successfully subtracting higher fractional power. Not only does this indicate we subtract 
more power, but it also confirms that our calibrated data is more closely matched to the 
model, meaning that the higher flux scale seen in the left panel of Figure~
\ref{fig:mwacs_diff}, and our calibration solutions in general, are more accurate.

\begin{figure}
\includegraphics[width=\columnwidth]{mwacs_ratio.pdf}
\caption{Power spectrum ratio difference, according to equation~\ref{eq:diff_ratio}. This 
metric shows the difference in the fractional E-W residual 2D power spectrum, comparing 
the MWACS catalog and our hierarchical catalog. By dividing the residual spectrum by the 
corresponding dirty spectrum before subtracting we remove the effect of the overall flux 
scale change due to differing calibration solutions. We see that the wedge is completely 
positive (higher fractional residual when using the MWACS catalog), confirming that the 
hierarchical catalog subtracts more power from the data. This also reassures that the 
calibration using the new catalog is more accurate. 
\label{fig:mwacs_ratio}
}
\end{figure}

\subsection{Diffuse Foreground Model Subtraction}

In addition to a point source foreground model, we also introduce a diffuse emission model 
within the primary field of view of the MWA. Though the EoR0 field was chosen to be 
relatively devoid of galactic emission, we find this diffuse structure still highly contaminating 
due to the very high sensitivity of the MWA at large scales. For computational purposes we 
have divided the galactic emission into two regimes -- the faint clouds in our main lobe, and 
the bright plane and other structures in the sidelobes. While the latter has been studied by 
many people and a Global Sky Model (GSM) is readily available 
\citep{deOliveira-Costa:2008}, the computational obstacle of simulating the instrument 
response to a full sky diffuse model is yet prohibitive, though under active pursuit 
\citep{Thyagarajan:2015}. We instead focus here on diffuse structure within the primary field 
and leave the full-sky model to future iterations of analysis.

This first iteration of modeling the diffuse structure within our primary field was done by 
simply using output point-source subtracted residual images of FHD from the three hour 
golden data set. We combine the images from three hours to leverage the rotation of the 
earth to improve the point spread function (PSF) of the instrument. This integrating of 
images is done in a uniformly weighted frame to minimize the effect of double instrument 
convolution (once when the data is taken, again when we use the output as a model). We 
then form a pseudo Stokes I image by adding beam-weighted East-West and North-South 
polarizations. We also integrate in frequency to form a single continuum image for our 
model. By forcing our model to contain no spectral structure we mitigate the risk of 
subtracting cosmological signal. Future iterations of this model will contain a spectral index 
and multiple polarization components.

Ultimately we need model visibilities to subtract from our data. However, rather than storing 
a model for all observations (different pointings and phase centers), we find it most simple 
to treat the model as a single HEALPix image which can be used to create model visibilities 
for each independent observation. FHD treats each pixel in the image as a point source at 
the pixel location with total flux equal to the flux density of the diffuse image times the area 
of the pixel and creates model visibilities for each snapshot in the same way that it imports 
a catalog of point sources.

The diffuse model used for this work is shown in Figure~\ref{fig:diffuse}. While the actual 
model image is uniform weighted with resolution $\sim\!6$~arcminutes, we show it 
smoothed to degree scales to emphasize the large scale structure and approximate what 
the MWA instrument observes with a natural weight.

For this iteration of analysis we only use the diffuse model for subtraction, and omit it for 
calibration. At the time of writing short baselines were not producing reliable results in the 
calibration loop. Instead we chose to omit the diffuse model and mask baselines shorter 
than 50 wavelengths for calibration purposes. However, we add the diffuse model and 
unmask short baselines when performing foreground subtraction, and have seen a 90\% 
decrease in total residual power -- a strong indication that our diffuse model improves our 
subtraction. Future iterations will incorporate the model in calibration and gradually improve 
the model itself.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{diffuse_sky.pdf}
\caption[Diffuse model used for subtraction]{
The diffuse foreground model within the EoR0 field used for foreground subtraction. This 
model was created using residual images from the golden data set. The image shown is 
smoothed to degree scales to emphasize the large scale structure and approximate an 
MWA snapshot natural weighting. The color scale is in units of Jy/degree$^2$.
\label{fig:diffuse}
}
\end{center}
\end{figure}

We demonstrate the impact of our diffuse model again by running the golden data set 
through our entire analysis pipeline with and without using the diffuse model. Because the 
foreground models used for calibration in the two runs are identical (diffuse is omitted for 
calibration), the calibration solutions were identical and therefore the dirty power spectra 
were identical as well. We compare the model and residual power spectra by direct 
subtraction in Figure~\ref{fig:diffuse_diff}. The top panel shows the model power with the 
diffuse subtracted from the model power without. The entire plot is negative (red) because 
we only added power with the diffuse model. The bottom panel is the difference in residual 
power. The wedge is completely positive (blue), indicating that the diffuse model 
successfully subtracted from the dirty visibilities. The differences in the window are positive 
and negative, indicating that any differences are below the three hour noise level.

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=.9\columnwidth]{diffuse_diff_model.pdf}}
~
\subfigure{\includegraphics[width=.9\columnwidth]{diffuse_diff_residual.pdf}}
\caption{
Single polarization (E-W) power spectrum differences from the golden data set showing the 
effect of subtracting a diffuse foreground model. The calibration is identical with and without 
the diffuse model, so the dirty power spectra are identical. The diffuse model adds a large 
amount of power to the model (top), and the residual power (bottom) is significantly lower in 
the wedge when using the diffuse model (positive difference), demonstrating a successful 
subtraction. While this first attempt at a diffuse model was rudimentary, it shows promise as 
it successfully removed 90\% of the residual power. 
\label{fig:diffuse_diff}
}
\end{center}
\end{figure}

\section{A Deep Integration}\label{sec:deep}
Up to this point we have only discussed testing and analysis on the three hour golden data 
set. We next turn towards a deep integration, incorporating the techniques described above. 
We start with all MWA observations taken on the EoR0 field at 182~MHz between August 
23, 2013 and November 29, 2013. This includes 2,780 snapshots, or about 86.5 hours of 
data. We first make data quality cuts, then form power spectra.

\subsection{Data Selection}\label{sec:selection}
All 2,780 snapshots in the data set are preprocessed, calibrated, and imaged using the 
pipeline described in the previous sections of this article. Similar to tests on the golden data 
set, we rely heavily on the 2D power spectrum as a diagnostic tool, this time to identify and 
excise poor quality data.

We use the jackknife method -- dividing the data into many subgroups -- to filter out bad 
data and detect patterns. A powerful grouping is to divide the data into the observation day 
and ``pointing" (which direction the antennas were pointed while tracking the EoR0 field). 
We show an example of one day's worth of per-pointing power spectra in Figure~
\ref{fig:jackknife}. The pointings are labeled sequentially with $-5$ corresponding to five 
pointing steps prior to zenith transit, $0$ corresponding to zenith, and $+4$ corresponding 
to four steps after zenith. Early in the night ($-5$ through $-3$) the bulk of the galactic plane 
was still above the horizon, and despite being very far from our primary field of view, highly 
contaminated our observations through the sidelobes of the instrument. We then have 
relatively well behaved pointings, with the EoR window dominated by noise, until the final 
pointing of the night when we can see evidence of the galaxy rising again indicated by 
strong lines of power at the edge of the foreground wedge. We saw the same contamination 
on all days of observation and decided to cut all $-5$, $-4$, $-3$, and $+4$ pointings from 
our data set. In principle it may be possible to model the galactic disk well enough to 
account for its presence, but with a lack of sufficient galactic model, beam model, and the 
analysis tools to include it, we leave this to future work.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{jackknife.pdf}
\caption[Per pointing jackknife]{An example jackknife test. For this test we divided the data 
into days and pointings. This is an example array of power spectra (residual E-W 
polarization) for a single day, August 26, 2013. The early pointings are heavily contaminated 
by the galaxy in the sidelobes, the window becomes more clear near zenith, and we can 
see trace contamination at the end of the night (pointing +4) when the galaxy has risen 
again.
\label{fig:jackknife}
}
\end{center}
\end{figure*}

Motivated by the hand grading done with power spectrum jackknives, we developed 
another metric to quickly predict power spectrum quality for each snapshot in our data set. 
We do this by forming a delay spectrum \citep{Parsons:2012b} from the raw, uncalibrated 
visibilities. We then calculate an estimated total EoR window power by integrating the 
power above the horizon line and below the first coarse band line. While we would ideally 
use calibrated visibilities for this metric, we have found that the uncalibrated power is 
strongly correlated to the calibrated power, and the cuts we make below are independent of 
calibration. This is encouraging because future analysis could use this metric before 
processing the snapshots, saving valuable computing resources.

We plot the window power for each snapshot in our data set in Figure~\ref{fig:wedge_cut1}. 
We first note that our conclusion from the jackknife tests is confirmed here -- early pointings 
contain strong contamination and have high window power. We also see many outlier 
snapshots with excess power. Inspecting power spectra from these individual snapshots 
confirmed poor data quality, even after calibration. The cause of these contaminants is yet 
unknown, but could easily be attributed to low-level RFI that was missed by the 
\texttt{AOFLAGGER}, or intermittent hardware failures. To remove the poor data we made 
the cut shown with the black box, keeping only snapshots inside.

\begin{figure}
\begin{center}
\subfigure[]{\includegraphics[width=\columnwidth]{window_x_no_cut_box_pointings.pdf}\label{fig:wedge_cut1}}
~
\subfigure[]{\includegraphics[width=\columnwidth]{window_ratio_cut_v1_box_pointings.pdf}\label{fig:wedge_cut2}}
\caption[Window power cut]{
\emph{Top:} Window power for each observation in our data set. The window power is 
calculated from the delay spectrum of uncalibrated data as a fast quality metric. Each color 
is a distinct day of observing, and the vertical dashed lines represent pointing shifts, with 
the pointing numbers indicated at the bottom of the plot above the horizontal axis. The black 
box indicates observations which passed this cut. \emph{Bottom:} Data cut based on 
window power polarization ratio. For each snapshot that passed the total power cut, we plot 
the ratio of window powers in the N-S and E-W polarizations. Clear outliers can be seen, 
including the whole of pointing +3. The black box again indicates the selected data.
\label{fig:wedge_cut}
}
\end{center}
\end{figure}

Next we compare the power in our two instrumental polarizations. When conducting our 
jackknife tests we saw contamination could exist in one polarization and not the other -- 
potentially due to RFI, or an instrumental failure. We plot the ratio of N-S power to E-W 
power in Figure~\ref{fig:wedge_cut2}, after applying the previous cut. We see the ratio is 
generally flat, with the exception of some outliers and almost all of pointing $+3$. We 
suspect that the excess N-S power in the later pointing is due to the galaxy leaking back 
into the sidelobe of the N-S polarization, but not in the other. Again, we make the cut shown 
with a black box.

Our final data cut was made when inspecting the residual continuum images output from 
FHD. We calculate a fractional residual flux RMS in the following way. For each snapshot 
continuum image, we find the residual flux in the pixels of all sources greater than 0.5 Jy 
subtracted within half-beam power and scale by the integrated flux of the sources. This 
gives us a list of fractional residual fluxes for the snapshot, which we then use to calculate 
an RMS. We found that most snapshots had residual flux RMS $<10\%$ with some outliers, 
which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
additional 95 observations. The cause of the high residual flux RMS is yet unknown and is 
not localized by observation day, LST, pointing, or any other jackknife we have performed.

After the cuts described above, we are left with 1,029 snapshots, or just over 32 hours of 
data. This is an aggressive cut, with the aim of removing all poor quality data and retaining 
a clean data set. As mentioned earlier, more sophisticated analysis could allow us to 
recover data cut from this study in the future (e.g. modeling and removing the galaxy in 
observations pointing far off zenith).

\subsection{Results}\label{sec:results}

In this section we discuss the results after processing the remaining 32~hours of data 
through the \eppsilon pipeline, and place an upper limit on the EoR power spectrum.

The bandwidth of the MWA and our data set is 30.72 MHz, but in order to avoid the effects 
of cosmic evolution over the span of our measured redshift range, we limit observations to 
about 8 MHz, or $\Delta z \sim 0.4$ at our frequency. We do this by dividing the band into 
three overlapping sub-bands of 15.36 MHz each, which, after applying the Blackman-Harris 
window function, will result in effective bandwidths of 7.68 MHz. We label these sub-bands 
as ``low" ($z\approx 7.1$), ``mid" ($z\approx 6.8$), and ``high" ($z\approx 6.5$).

The 32 hour integrated residual power spectra for our three sub-bands and both 
instrumental polarizations are shown in Figure~\ref{fig:2d_ps_subband}. A number of 
features can be seen in these spectra. In all cases the foreground wedge is prominent, with 
extra power at large scales (low $k_{\perp}$). This is indication that our diffuse model can 
improve for deeper subtraction.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{2d_res.pdf}
\caption[Deep 2D sub-band power spectra]{
Residual two dimensional power spectra for the three sub-bands used to place limits on the 
cosmological signal. The left panels show the low band, centered at 174.7 MHz, or a 
redshift of 7.1. The middle panels show the mid band, centered at 182.4 MHz, or a redshift 
of 6.8. The right panels show the high band, centered at 190.1 MHz, or a redshift of 6.5. 
The red box in the upper left panel shows the window used for averaging to one dimension.
\label{fig:2d_ps_subband}
}
\end{center}
\end{figure*}

The lowest region of the EoR window, above the horizon line and around $k_{||} \approx 
0.25$ h Mpc$^{-1}$, contains purely positive bins, indicating non-noise-like power. The 
cause for this seeming leakage is yet unknown, but will ultimately limit our integration in this 
analysis. One suspected origin of this contamination was individual snapshots with high 
contamination that slipped through our cuts. However, dividing the data into random 
subsets and comparing results indicated that there is not a small number of offending 
observations, instead the leakage appears to exist at a low level in all the data.

Moving up in the window, between the first two coarse band harmonic lines we can see an 
additional faint line. This is the re-emergence of the 150 meter cable reflections. While the 
method described in Section~\ref{subsec:cal_imaging} sufficiently calibrated out this 
reflection line for the three hour golden set integration, the lower noise level in this deeper 
integration shows it is not completely removed. Future analysis will require higher signal-to-
noise on the reflection fitting, which may require combining snapshots for calibration 
solutions.

Between the coarse band harmonic lines and the reflection line, we do see regions where 
our spectra appear noise-like (positive and negative values). This is encouraging despite 
the leakage at lower $k_{||}$. The red box in the upper left 2D spectrum shows the region of 
$\mathbf{k}$-space we use when averaging to one dimension. We exclude any voxels 
below the solid black horizon line, as well as $k_{||}<0.1$ h Mpc$^{-1}$ due to foreground 
contamination. We limit the $k_{\perp}$ range due to higher power in the coarse bands at 
low $k_{\perp}$, and the poor $uv$ coverage at high $k_{\perp}$, leading to the vertical 
streaks seen on the right side of the 2D spectra. We set our range to be $0.015$ h Mpc
$^{-1} \leq k_{\perp} \leq 0.03$ h Mpc$^{-1}$. This is an aggressive cut, but confidently 
avoids the vertical streaks of leaked power.

One could additionally mask the coarse band harmonic lines when averaging to one 
dimension. However, because $k_{||} \gg k_{\perp}$ within the red box, our spherical shells 
are approximately constant $k_{||}$, so the coarse bands are still isolated in our average. 
We choose to retain them to avoid empty bins, and to help guide the reader when 
comparing the 2D and 1D spectra. While the red box is shown on the 2D plot, the actual 1D 
averaging is done by returning to the full three dimensional power cubes and performing a 
weighted average in shells.

The resulting one dimensional power spectra are shown in Figure~\ref{fig:1d_ps}, where 
the measured power is shown with solid blue, the 1-$\sigma$ noise level is shown with 
dashed red, and the 2-$\sigma$ upper limit for each bin is shown with dashed magenta. 
Where our unbiased estimator is negative, the absolute value is shown, but with a dashed 
green line. For consistency with the literature, we plot our one dimensional power spectra 
as $\Delta^2(k)=k^3P_{21}(k)/(2\pi^2)$, which has units of mK$^2$.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{1D_spectra.pdf}
\caption[1D deep power spectra]{
One dimensional power spectra for our three sub-bands and both instrumental 
polarizations. The solid blue line shows the measured power spectrum with step widths 
corresponding to the bin size used in the average. Where the measured signal is negative 
we plot the absolute value in green. The red dashed line is the 1-$\sigma$ noise level, and 
the dashed magenta line is the 2-$\sigma$ upper limit for each $k$ bin. Theoretical models 
from \citet{Lidz:2008} for $\overline{x}_i=0.54$, $0.82$, and $0.96$ are shown in the low, 
mid, and high band spectra, respectively, in solid black. from \citet{Lidz:2008} are shown in 
solid black. An additional theoretical model for a fully neutral IGM from 
\citet{Furlanetto:2006} is shown with a dashed black line.
\label{fig:1d_ps}
}
\end{center}
\end{figure*}

In all bands and polarizations, we are heavily signal dominated in our most sensitive region 
(low $k$). This is not surprising based on the 2D spectra we examined earlier. We can see 
the strong coarse band harmonic lines, and the cable reflection line between the first two 
coarse band lines. But between these coarse lines there are bins which approach the noise 
level and are consistent with zero (notably the North-South polarization for the $z=7.1$ and 
$z=6.8$ bands). These regions are encouraging because they have the potential to 
continue integrating down with more data.

However, our best upper limits for a cosmological signal are still at low $k$, despite the 
strong leakage. Because any foreground leakage should not correlate with the EoR signal, 
we can assume that the power of the sum of leakage and cosmological signal is greater 
than the power of the EoR signal alone, allowing us to set an upper limit. We quote the best 
2-$\sigma$ upper limits, $\Delta^2_{\text{UL}}$, for each polarization and band in Table~
\ref{tbl:limits}. These limits and their context in the field are further discussed in Section~
\ref{sec:discussion}.

\begin{table}
\begin{center}
\caption[EoR power spectrum limits]{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level.
\label{tbl:limits}
}
\begin{tabular}{ccccc}
\tableline\tableline
Sub-band & $z_0$ & Polarization & $k$ (h Mpc$^{-1}$) & $\Delta^2_{\text{UL}}$ (mK$^2$) \\
\tableline
Low & 7.1 & E-W & 0.231 & 3.02 $\times 10^4$\\
Low & 7.1 & N-S & 0.231 & 2.22 $\times 10^4$\\
Mid & 6.8 & E-W & 0.2361 & 2.84 $\times 10^4$\\
Mid & 6.8 & N-S & 0.2361 & 2.17 $\times 10^4$\\
High & 6.5 & E-W & 0.204 & 5.24 $\times 10^4$\\
High & 6.5 & N-S & 0.241 & 3.11 $\times 10^4$\\
\tableline
\end{tabular}
\end{center}
\end{table}

\subsection{Comparison with reference pipeline}\label{subsec:ref_pipe}
\textcolor{red}{Will inject comparison with RTS/CHIPS here.}

\section{Discussion}\label{sec:discussion}
Inspecting our 32 hour integrated power spectra we see two places where we are limited. 
First there is a region that is leakage-dominated at low $k$. The cause of this leakage is yet 
unknown, but likely due to imperfect calibration, beam models, and/or foreground models. 
In order to improve on our limit in this regime, future analysis will require calibration which 
better accounts for the instrumental response, perhaps by increasing signal to noise 
through multiple-snapshot solutions or refined antenna response models. Studies of the 
beam are underway \citep[e.g.][]{Neben:2015}, and will likely help to further isolate the 
foreground contaminates in our power spectra. The foreground model is a constant area of 
investigation, but improved spectral dependence in both the point source catalog and the 
diffuse model, as well as the addition of an all-sky galactic model, will continue to improve 
the foreground subtraction and further unlock the EoR window.

The second limited region in our 1D power spectra is between the coarse band harmonics 
where our measured signal approaches the noise level. Additional data will likely reduce the 
noise, and therefore our upper limit, in this regime. However, until the leakage at low $k$ is 
understood, progress at higher $k$ is susceptible to running into the same systematic. 
While a longer integration may improve the upper limit in the short term, the hope for an 
eventual detection lies in understanding the contaminants at low $k$.

Finally, we place our best upper limits in context with the 21cm EoR field as a whole. A 
direct comparison between measurements from different instruments is difficult due to the 
varying methods, redshifts, and scales probed. However, if we approximate the power 
spectrum in units of mK$^2$ to be roughly flat over the scales probed by the MWA, PAPER, 
and GMRT, we can glean a view of the current state of the field. The results from this 
analysis are a modest improvement over the previous best MWA results \citep{Dillon:2015}, 
which is not surprising given that this integration contains about ten times more data, but 
has a strong signal to noise on the power spectrum. Our results are also consistent with the 
GMRT limit of $\Delta^2\le6.15\times10^4$~mK$^2$ at $z=8.6$ \citep{Paciga:2013}, though 
probe significantly different periods of the EoR. The frontrunner in terms of an upper limit is 
the PAPER experiment \citep{Ali:2015, Jacobs:2015, Parsons:2014}. The PAPER-64 limit of 
$\Delta^2\le502$~mK$^2$ at $z=8.4$ is about one and a half orders of magnitude lower 
than our best limit in power units, though again probing a significantly different redshift. 
While the MWA analysis is not yet at that level of maturity, there is room for rapid 
improvement. The dashed red line in Figure~\ref{fig:1d_ps} indicate the noise level possible 
to reach with this data set if systematics can be overcome.

While this analysis has not reached full potential, it represents the deepest power spectrum 
integration to date produced by an imaging pipeline. Imaging involves many difficulties (e.g. 
efficient gridding and mapmaking, foreground modeling), but if systematics can be 
overcome, it has the potential to quickly compete with other more pointed experiments and 
analysis styles. Here we have identified a crucial region of power spectrum space that is 
currently contaminated, with suggestions for improvement in future analysis. With improved 
calibration techniques, primary beam models, and understanding of foregrounds, the MWA 
and other imaging analyses will be able to quickly approach the most competitive upper 
limits in the field.

\section{Acknowledgements}
This work was supported by NSF grants AST-1410484 and AST-1206552.
JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award 
AST-1302774. This scientific work makes use of the Murchison Radio-astronomy 
Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the 
traditional owners of the Observatory site. Support for the MWA comes from the U.S. 
National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and 
AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), 
the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for 
All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant 
CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the 
MIT School of Science, the Raman Research Institute, the Australian National University, 
and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand 
Ministry of Economic Development and an IBM Shared University Research Grant). The 
Australian Federal government provides additional support via the Commonwealth Scientific 
and Industrial Research Organisation (CSIRO), National Collaborative Research 
Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic 
Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We 
acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the 
CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the 
International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin 
University and The University of Western Australia, funded by the Western Australian State 
government.

\bibliography{bib}

\end{document}

### 2016-03-31 ms.tex
Apparently I didnt save all the line breaks earlier.

@@
 
-Using the first generation of instruments, several upper limits have been placed on the 21 cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}, and \citealt{Pober:2015} was able to place constraints on physical reionization models.
+Using the first generation of instruments, several upper limits have been placed on the 21 
+cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}, and 
+\citealt{Pober:2015} was able to place constraints on physical reionization models. 
 However, much work is to be done to understand the data produced by these arrays. 
-Foreground subtraction and isolation has emerged as a priority in the field.
-Central to most analysis strategies is the concept of an ``EoR window" -- the region of Fourier space where spectrally smooth foregrounds have been isolated from the isotropic (spherically symmetric in Fourier space) cosmological signal \citep{Morales:2006, Bowman:2009}.
-More recent studies have shown the existence of a foreground ``wedge", the result of instrumental mode mixing, throwing power from spectrally smooth foregrounds to higher Fourier modes \citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2014, Liu:2014a, Liu:2014b, Hazelton:2013, Pober:2013, Vedantham:2012, Morales:2012, Datta:2010}.
-Despite this setback, the EoR window is preserved above the wedge, and the field is pushing forward with several analysis pipelines under active development \citep[e.g.
-B.~J.~Hazelton et al.
-2016, in prep; D.~A.~Mitchell et al.
-2016, in prep; D.~C.~Jacobs et al.
-2016, in review; ][]{Trott:2016, Dillon:2013, Trott:2012}.
-
-This paper serves two purposes: to demonstrate several new analysis techniques and their impact on power spectrum estimation, and to present the first attempt at a deep integration power spectrum from the MWA.
-Using a three hour test set of data, we introduce several novel techniques including calibration of cable reflection contamination, high resolution gridding kernels, subtraction of a diffuse foreground model, and development of quality control methods which will be crucial for deeper integrations.
-We apply these new techniques to a deep integration of data from the first semester of MWA observations (August, 2013 -- November, 2013) on a single EoR field and redshift range, $6.2<z<7.5$.
-While not expecting to detect the EoR with less than a hundred hours of observations, this intermediate integration will serve to identify and diagnose systematics, allowing for improved analysis in future work.
-
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:MWA} we briefly describe the MWA instrument and the observations used in this work, in Section~\ref{sec:analysis} we describe our analysis pipeline, in Section~\ref{sec:techniques} we describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our efforts to apply the analysis pipeline to a deep data integration, and we discuss future work in Section~\ref{sec:discussion}.
-Throughout this paper we use a $\Lambda$CDM cosmology with $\Omega_m=0.73$, $\Omega_\Lambda=0.27$, and $h = 0.7$, consistent with WMAP seven year results \citep{Komatsu:2011}.
-All distances and wavenumbers are in comoving coordinates.
+Foreground subtraction and isolation has emerged as a priority in the field. Central to most 
+analysis strategies is the concept of an ``EoR window" -- the region of Fourier space where 
+spectrally smooth foregrounds have been isolated from the isotropic (spherically symmetric 
+in Fourier space) cosmological signal \citep{Morales:2006, Bowman:2009}. More recent 
+studies have shown the existence of a foreground ``wedge", the result of instrumental mode 
+mixing, throwing power from spectrally smooth foregrounds to higher Fourier modes 
+\citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2014, Liu:2014a, Liu:2014b, 
+Hazelton:2013, Pober:2013, Vedantham:2012, Morales:2012, Datta:2010}. Despite this 
+setback, the EoR window is preserved above the wedge, and the field is pushing forward with 
+several analysis pipelines under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
+prep; D.~A.~Mitchell et al. 2016, in prep; D.~C.~Jacobs et al. 2016, in review; ][]{Trott:2016, 
+Dillon:2013, Trott:2012}.
+
+This paper serves two purposes: to demonstrate several new analysis techniques and their 
+impact on power spectrum estimation, and to present the first attempt at a deep integration 
+power spectrum from the MWA. Using a three hour test set of data, we introduce several 
+novel techniques including calibration of cable reflection contamination, high resolution 
+gridding kernels, subtraction of a diffuse foreground model, and development of quality 
+control methods which will be crucial for deeper integrations. We apply these new 
+techniques to a deep integration of data from the first semester of MWA observations 
+(August, 2013 -- November, 2013) on a single EoR field and redshift range, $6.2<z<7.5$. 
+While not expecting to detect the EoR with less than a hundred hours of observations, this 
+intermediate integration will serve to identify and diagnose systematics, allowing for 
+improved analysis in future work.
+
+The remainder of this paper is organized as follows. In Section~\ref{sec:MWA} we briefly 
+describe the MWA instrument and the observations used in this work, in Section~
+\ref{sec:analysis} we describe our analysis pipeline, in Section~\ref{sec:techniques} we 
+describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our 
+efforts to apply the analysis pipeline to a deep data integration, and we discuss future work 
+in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM 
+cosmology with $\Omega_m=0.73$, $\Omega_\Lambda=0.27$, and $h = 0.7$, consistent 
+with WMAP seven year results \citep{Komatsu:2011}. All distances and wavenumbers are in 
+comoving coordinates.
 
 \section{The Murchison Widefield Array and Observations}\label{sec:MWA}
-The Murchison Widefield Array is one of several first generation radio interferometers with a primary science goal of detecting the 21cm EoR power spectrum.
-The remote Australian outback offers relative isolation from man-made radio frequency interference (RFI) such as FM radio, or TV stations.
-A recent study of the RFI environment at the Murchison Radio Observatory can be found in \citealt{Offringa:2015}.
-
-While the 21 cm EoR signal is priority, the MWA is a general observatory serving several science programs beyond cosmology including galactic and extragalactic surveys, time domain astrophysics, solar monitoring, and ionospheric science.
-The array was thus designed with these programs in consideration and the layout was optimized using a pseudo-random antenna placement algorithm \citep{Beardsley:2012} to obtain a well behaved point spread function while retaining a dense core for EoR sensitivity \citep{Beardsley:2013}.
-This is in contrast to more pointed EoR experiments like PAPER, which utilize a highly redundant layout to enhance sensitivity.
-Redundant arrays can leverage symmetries of the instrument for quick calibration and analysis, but have poor point spread functions, making foregrounds more difficult to characterize.
-Conversely we use the high imaging capability of the MWA to calibrate and subtract foregrounds based on sky models.
-A full description of the science capabilities of the array is found in \citealt{Bowman:2013}.
-
-The technical design of the MWA is reviewed in \citealt{Tingay:2013}, and we highlight a few key characteristics that will become important in our analysis of the data.
-Each antenna of the MWA comprises 16 dual-polarization dipoles placed on a regular grid, lying on a ground screen.
-The radio frequency signals from these dipoles feed into an analog beamformer which uses physical delays to ``point" the antenna.
-The MWA contains 128 of these antennas, with a tightly packed core of radius 50 m, and extending out to a radius 1.5 km for higher resolution calibration and imaging.
-
-The beamformed signals (one for each polarization) are then transmitted to receivers in the field, which digitize the signal and perform a first stage coarse frequency channelization of the data (1.28 MHz sub-bands)\citep{Prabu:2015}.
-This channelization applies a filter shape and aliases edge channels, which will later be flagged in our analysis.
-The observer now selects 24 sub-bands (30.72 MHz total bandwidth) to pass onto the correlator via fiber optic link.
-The correlator further channelizes the data to 10 kHz resolution, cross multiplies signals between antennas to form visibilities, and averages in time and frequency to a resolution specified by the observer.
-For the data in this work, the correlator output resolutions were 0.5 seconds in time and 40 kHz in frequency.
-The data are then written to disk on a cadence of 112 seconds, constituting a single observation, or snapshot.
-
-The EoR observing campaign has adopted a ``drift and shift" tracking strategy -- we point the telescope towards a sky field of interest, allow the field to drift overhead for about 30 minutes until it begins to leave our field of view, then repoint the instrument at the field.
-The telescope is thus only pointed at discrete positions, or ``pointings".
-This tracking is repeated until the field is too low in the sky to track.
-We have identified three EoR fields relatively devoid of galactic emission and bright extragalactic sources for observing: ``EoR0" (RA $=0.00$ h, dec $= -27^\circ$), ``EoR1" (RA $=4.00$ h, dec $= -27^\circ$), and ``EoR2" (RA $=11.33$ h, dec $= -10^\circ$).
-In addition, we observe these fields in high and low bands centered at 182 MHz ($z\approx6.8$) and 154 MHz ($z\approx8.2$) respectively.
-
-The data for this work includes two sets.
-First we use a set of 94 high band observations of the EoR0 field from August 23, 2013, which were taken early in telescope operations and found to be particularly well behaved.
-The MWA EoR collaboration has designated this set as a ``golden data set'', which is used to build analysis tools and compare early results.
-All techniques demonstrated here will use this golden data set.
-In Section~\ref{sec:deep} we will use a larger data set to move toward a deep integration.
-This data set consists of all EoR0 high band observations beginning August 23, 2013 (including the golden data set), and concluding when the field was no longer accessible for the season: when the sun was above the horizon for most or all of the field's transit.
-The final observation of this set was on November 29, 2013.
-The individual snapshots are 112 seconds of data at 0.5 second, 40 kHz resolution.
-In total we analyze 2,780 snapshots, or about 86.5 hours of data.
+The Murchison Widefield Array is one of several first generation radio interferometers with 
+a primary science goal of detecting the 21cm EoR power spectrum. The remote Australian 
+outback offers relative isolation from man-made radio frequency interference (RFI) such as 
+FM radio, or TV stations. A recent study of the RFI environment at the Murchison Radio 
+Observatory can be found in \citealt{Offringa:2015}.
+
+While the 21 cm EoR signal is priority, the MWA is a general observatory serving several 
+science programs beyond cosmology including galactic and extragalactic surveys, time 
+domain astrophysics, solar monitoring, and ionospheric science. The array was thus 
+designed with these programs in consideration and the layout was optimized using a 
+pseudo-random antenna placement algorithm \citep{Beardsley:2012} to obtain a well 
+behaved point spread function while retaining a dense core for EoR sensitivity 
+\citep{Beardsley:2013}. This is in contrast to more pointed EoR experiments like PAPER, 
+which utilize a highly redundant layout to enhance sensitivity. Redundant arrays can 
+leverage symmetries of the instrument for quick calibration and analysis, but have poor 
+point spread functions, making foregrounds more difficult to characterize. Conversely we 
+use the high imaging capability of the MWA to calibrate and subtract foregrounds based on 
+sky models. A full description of the science capabilities of the array is found in 
+\citealt{Bowman:2013}.
+
+The technical design of the MWA is reviewed in \citealt{Tingay:2013}, and we highlight a 
+few key characteristics that will become important in our analysis of the data. Each 
+antenna of the MWA comprises 16 dual-polarization dipoles placed on a regular grid, lying 
+on a ground screen. The radio frequency signals from these dipoles feed into an analog 
+beamformer which uses physical delays to ``point" the antenna. The MWA contains 128 of 
+these antennas, with a tightly packed core of radius 50 m, and extending out to a radius 
+1.5 km for higher resolution calibration and imaging.
+
+The beamformed signals (one for each polarization) are then transmitted to receivers in 
+the field, which digitize the signal and perform a first stage coarse frequency 
+channelization of the data (1.28 MHz sub-bands)\citep{Prabu:2015}. This channelization 
+applies a filter shape and aliases edge channels, which will later be flagged in our analysis. 
+The observer now selects 24 sub-bands (30.72 MHz total bandwidth) to pass onto the 
+correlator via fiber optic link. The correlator further channelizes the data to 10 kHz 
+resolution, cross multiplies signals between antennas to form visibilities, and averages in 
+time and frequency to a resolution specified by the observer. For the data in this work, the 
+correlator output resolutions were 0.5 seconds in time and 40 kHz in frequency. The data 
+are then written to disk on a cadence of 112 seconds, constituting a single observation, or 
+snapshot.
+
+The EoR observing campaign has adopted a ``drift and shift" tracking strategy -- we point 
+the telescope towards a sky field of interest, allow the field to drift overhead for about 30 
+minutes until it begins to leave our field of view, then repoint the instrument at the field. The 
+telescope is thus only pointed at discrete positions, or ``pointings". This tracking is 
+repeated until the field is too low in the sky to track. We have identified three EoR fields 
+relatively devoid of galactic emission and bright extragalactic sources for observing: 
+``EoR0" (RA $=0.00$ h, dec $= -27^\circ$), ``EoR1" (RA $=4.00$ h, dec $= -27^\circ$), 
+and ``EoR2" (RA $=11.33$ h, dec $= -10^\circ$). In addition, we observe these fields in 
+high and low bands centered at 182 MHz ($z\approx6.8$) and 154 MHz ($z\approx8.2$) 
+respectively.
+
+The data for this work includes two sets. First we use a set of 94 high band observations of 
+the EoR0 field from August 23, 2013, which were taken early in telescope operations and 
+found to be particularly well behaved. The MWA EoR collaboration has designated this set 
+as a ``golden data set'', which is used to build analysis tools and compare early results. All 
+techniques demonstrated here will use this golden data set. In Section~\ref{sec:deep} we 
+will use a larger data set to move toward a deep integration. This data set consists of all 
+EoR0 high band observations beginning August 23, 2013 (including the golden data set), 
+and concluding when the field was no longer accessible for the season: when the sun was 
+above the horizon for most or all of the field's transit. The final observation of this set was 
+on November 29, 2013. The individual snapshots are 112 seconds of data at 0.5 second, 
+40 kHz resolution. In total we analyze 2,780 snapshots, or about 86.5 hours of data.
 
 \section{Analysis Pipeline}\label{sec:analysis}
-In order to ensure consistency in analysis, the international MWA EoR collaboration has defined two independent reference analysis pipelines.
-The details of this strategy are outlined in D.~C.~Jacobs et al.
-2016 (in review).
-This study is based on the FHD-to-\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al.
-2016, in prep) packages.
-The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we give an overview below.
+In order to ensure consistency in analysis, the international MWA EoR collaboration has 
+defined two independent reference analysis pipelines. The details of this strategy are 
+outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-
+\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD
+\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error 
+Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
+\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
+prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
+give an overview below.
 
@@
 \caption[Pipeline diagram]{
-Schematic of the analysis pipeline used in this work.
-The raw correlator data is preprocessed by performing RFI and other flagging.
-Then the data are calibrated and imaged using an iterative foreground modeling approach with the FHD package.
-Finally, a power spectrum is formed using the \eppsilon package.
+Schematic of the analysis pipeline used in this work. The raw correlator data is 
+preprocessed by performing RFI and other flagging. Then the data are calibrated and 
+imaged using an iterative foreground modeling approach with the FHD package. Finally, a 
+power spectrum is formed using the \eppsilon package.
 \label{fig:pipe}
@@
 \subsection{Preprocessing}\label{subsec:preprocessing}
-The preprocessing step converts the data from the non-standard memory dump format from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, performs flagging, averages in time and freqeuncy, and writes to disk.
-For this step we use the \cotter package, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://aoflagger.sourceforge.net/}} to perform RFI flagging \citep{Offringa:2010}.
-
-Besides RFI, we manually flag data to remove three other effects.
-As mentioned in Section~\ref{sec:MWA}, the edges of the coarse bands contain high levels of aliasing from the filter applied in the digital receivers.
-We flag two 40 kHz channels on either side of the coarse band edges (total of four channels per coarse band edge).
-In principle the aliasing could be calibrated out and these channels could be recovered, but this is left for future work.
-Second, early data from the MWA also contained some instances where antennas were not pointed properly at the beginning of observations due to a beamformer error.
-This problem has since been resolved, but exists in our data.
-We therefore flag the first two seconds of each observation to avoid any potentially mis-pointed data.
-Finally, we flag the central fine channel of each coarse band because it corresponds to the DC mode of that sub-band and can easily float, washing out useful information.
-
-In the final step of preprocessing, \cotter averages the data to 2 second, 80 kHz resolution and writes to disk.
-At this stage each snapshot is contained in a single UVFITS file, which serves as the base unit for calibration and imaging.
+The preprocessing step converts the data from the non-standard memory dump format 
+from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, performs 
+flagging, averages in time and freqeuncy, and writes to disk. For this step we use the 
+\cotter package, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://
+aoflagger.sourceforge.net/}} to perform RFI flagging \citep{Offringa:2010}.
+
+Besides RFI, we manually flag data to remove three other effects. As mentioned in 
+Section~\ref{sec:MWA}, the edges of the coarse bands contain high levels of aliasing from 
+the filter applied in the digital receivers. We flag two 40 kHz channels on either side of the 
+coarse band edges (total of four channels per coarse band edge). In principle the aliasing 
+could be calibrated out and these channels could be recovered, but this is left for future 
+work. Second, early data from the MWA also contained some instances where antennas 
+were not pointed properly at the beginning of observations due to a beamformer error. This 
+problem has since been resolved, but exists in our data. We therefore flag the first two 
+seconds of each observation to avoid any potentially mis-pointed data. Finally, we flag the 
+central fine channel of each coarse band because it corresponds to the DC mode of that 
+sub-band and can easily float, washing out useful information.
+
+In the final step of preprocessing, \cotter averages the data to 2 second, 80 kHz resolution 
+and writes to disk. At this stage each snapshot is contained in a single UVFITS file, which 
+serves as the base unit for calibration and imaging.
 
 \subsection{Calibration and Imaging}\label{subsec:cal_imaging}
-The next step in our pipeline is to calibrate the visibilities.
-As shown in Figure~\ref{fig:pipe}, a sky model is derived from our imaged data, which feeds back into the calibration.
-This is naturally an iterative process as the sky model is refined with improved calibration solutions.
-We will describe the sky model in detail in Section~\ref{sec:techniques}, but here we present the production mode of analysis after the model has been determined.
-
-Calibration is accomplished within the FHD package in two steps.
-First we match the raw data to model visibilities formed using a realistic simulation of the array response to our foreground model.
-This step results in independent complex gains for each antenna, frequency channel, and polarization.
-In the second step we impose restrictions on these gains motivated by our understanding of the spectral response of the instrument.
-By reducing the number of free parameters in this step we increase our signal to noise on calibration solutions and avoid absorbing unmodeled confusion source flux into our gain solutions which has been shown to contaminate the EoR window \citep{Barry:2016}.
-
-In the first calibration step we allow our complex gains to account for any direction-independent response on a per antenna, per frequency channel, per polarization basis.
-To define our gains in this way, we have made two simplifications.
-First we push all direction-dependence of the antenna response into the model of the primary beam.
-FHD is capable of using separate models for each antenna, though this has not yet been implemented for the MWA due to lack of individual models.
-The second simplification is to ignore any cross terms between our different axes, for example a mutual coupling between two antennas.
-In principle these terms would introduce baseline dependent gains, rather than antenna dependent.
-The MWA has not yet seen evidence of these terms, and so we currently neglect them in our solutions.
-
-Under these assumptions we can express the measured, uncalibrated visibility for an antenna pair $(i,j)$ as
+The next step in our pipeline is to calibrate the visibilities. As shown in Figure~\ref{fig:pipe}, 
+a sky model is derived from our imaged data, which feeds back into the calibration. This is 
+naturally an iterative process as the sky model is refined with improved calibration 
+solutions. We will describe the sky model in detail in Section~\ref{sec:techniques}, but here 
+we present the production mode of analysis after the model has been determined.
+
+Calibration is accomplished within the FHD package in two steps. First we match the raw 
+data to model visibilities formed using a realistic simulation of the array response to our 
+foreground model. This step results in independent complex gains for each antenna, 
+frequency channel, and polarization. In the second step we impose restrictions on these 
+gains motivated by our understanding of the spectral response of the instrument. By 
+reducing the number of free parameters in this step we increase our signal to noise on 
+calibration solutions and avoid absorbing unmodeled confusion source flux into our gain 
+solutions which has been shown to contaminate the EoR window \citep{Barry:2016}.
+
+In the first calibration step we allow our complex gains to account for any direction-
+independent response on a per antenna, per frequency channel, per polarization basis. To 
+define our gains in this way, we have made two simplifications. First we push all direction-
+dependence of the antenna response into the model of the primary beam. FHD is capable 
+of using separate models for each antenna, though this has not yet been implemented for 
+the MWA due to lack of individual models. The second simplification is to ignore any cross 
+terms between our different axes, for example a mutual coupling between two antennas. In 
+principle these terms would introduce baseline dependent gains, rather than antenna 
+dependent. The MWA has not yet seen evidence of these terms, and so we currently 
+neglect them in our solutions.
+
+Under these assumptions we can express the measured, uncalibrated visibility for an 
+antenna pair $(i,j)$ as
 \begin{equation}
@@
 \end{equation}
-where $g_i(\nu)$ and $g_j(\nu)$ are the complex gains for antennas $i$ and $j$ respectively.
-Because we are treating polarizations independently, we allow the antenna subscript to run over both East-West (E-W) and North-South (N-S) polarizations.
-
-FHD utilizes the StEFCal algorithm described in \citealt{Salvini:2014} to find the minimum $\chi^2$ estimate with respect to the complex gains.
-The result of this operation is estimated gains for every antenna, frequency channel, and polarization.
-However, with certain known properties of the antenna response we can reduce the number of free parameters in our solution.
-This takes us to the second step of calibration.
-
-Our initial gain model included an amplitude bandpass common to all antennas, $B(\nu)$, and an antenna dependent low order polynomial in frequency. Mathematically we can express our restricted gain as
+where $g_i(\nu)$ and $g_j(\nu)$ are the complex gains for antennas $i$ and $j$ 
+respectively. Because we are treating polarizations independently, we allow the antenna 
+subscript to run over both East-West (E-W) and North-South (N-S) polarizations.
+
+FHD utilizes the StEFCal algorithm described in \citealt{Salvini:2014} to find the minimum 
+$\chi^2$ estimate with respect to the complex gains. The result of this operation is 
+estimated gains for every antenna, frequency channel, and polarization. However, with 
+certain known properties of the antenna response we can reduce the number of free 
+parameters in our solution. This takes us to the second step of calibration.
+
+Our initial gain model included an amplitude bandpass common to all antennas, $B(\nu)$, 
+and an antenna dependent low order polynomial in frequency. Mathematically we can 
+express our restricted gain as
 \begin{equation}\label{eq:cal1}

### 2016-04-26 ms.tex
Added TODOs for pipeline comparison
added mahsa as author

@@
 P.~Procopio\affils{UMelbourne,CAASTRO},
+M.~Rahimi\affils{UMelbourne},
 J.~Riding\affils{UMelbourne,CAASTRO},
@@
 \textcolor{red}{Will inject comparison with RTS/CHIPS here.}
+% ADAM: Motivation why a pipeline is being discussed
+% MAHSA: Summary of RTS to power spectrum (e.g. calibration, etc)
+% MAHSA QA: - bad day, forward reference Jordan et al, Beam nulls - fixed for future analysis
+% CATH: Plots
+%     by pointing - diff zenith vs +2 
+%	2D PS vs redshift
+%	1D
 

### 2016-05-04 ms.tex
fixed units in diffuse model plot
Adding pointing cartoon figure
Starting text for ref pipe section

@@
 smoothed to degree scales to emphasize the large scale structure and approximate an 
-MWA snapshot natural weighting. The color scale is in units of Jy/degree$^2$.
+MWA snapshot natural weighting. The color scale is in units of Jy/str.
 \label{fig:diffuse}
@@
 \begin{center}
+%\subfigure{\includegraphics[width=\textwidth]{jackknife.pdf}}
 \includegraphics[width=\textwidth]{jackknife.pdf}
+%\subfigure{\includegraphics[width=.5\textwidth]{pointing_cartoon.pdf}}
 \caption[Per pointing jackknife]{An example jackknife test. For this test we divided the data 
@@
 \end{figure*}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{pointing_cartoon.pdf}
+\caption{\textcolor{red}{caption!}
+\label{fig:pointing}
+}
+\end{center}
+\end{figure}
 
@@
 \subsection{Comparison with reference pipeline}\label{subsec:ref_pipe}
-\textcolor{red}{Will inject comparison with RTS/CHIPS here.}
+
+As demonstrated in D.~C.~Jacobs et al. 2016 (in review), comparison between independent 
+analysis pipelines is essential to evaluate the validity of algorithms under active development. 
+Such comparison provides insight into the strengths and weaknesses of the pipelines, as well 
+as confirmation of results. The analysis discussed so far has been based on the FHD to 
+\eppsilon pipeline, and here we compare with the Real Time System \citep[RTS,][]
+{Mitchell:2008,Ord:2010} to Cosmological \ion{H}{1} Power Spectrum \citep[CHIPS,][]
+{Trott:2016} pipeline. Below we present a brief overview of the reference pipeline and 
+highlight lessons learned from the comparison.
+
 % ADAM: Motivation why a pipeline is being discussed

### 2016-05-14 ms.tex
Major additions to text to explain slice figure, also minor tweaks

@@
 integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
-upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.17 \times 10^4$ mK
-$^2$ at $k=0.24$ h~Mpc$^{-1}$ and $z=6.8$, consistent with other published limits, and a 
-modest improvement (factor of 1.7) over previous MWA results. While our result is 
+upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ mK
+$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
+modest improvement (factor of 1.4) over previous MWA results. While our result is 
 systematic limited, we identify several strategies to overcome these systematics in future 
@@
 \eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD
-\footnote{\url{https://github.com/miguelfmorales/FHD}}, \citealt{Sullivan:2012}) and Error 
+\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
 Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
-\footnote{\url{https://github.com/miguelfmorales/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
+\footnote{\url{https://github.com/EoRImaging/eppsilon}}, B.~J.~Hazelton et al. 2016, in 
 prep) packages. The general flow of the pipeline is shown in Figure~\ref{fig:pipe}, and we 
@@
 \begin{equation}
-V'_{ij}(\nu) \approx g_i(\nu)g^*_jV_{ij}(\nu),
+V'_{ij}(\nu) \approx g_i(\nu)g^*_j(\nu)V_{ij}(\nu),
 \end{equation}
@@
 wavelength), and crop the image. We found that cropping the image based on beam value 
-resulting in hard edges in integrated images from different snapshots having beams pointed 
+resulted in hard edges when integrating images from different snapshots having beams pointed 
 in slightly different directions. To avoid the hard edges, we predetermine a set of HEALPix 
@@
 before implementing cable reflection fitting into the calibration loop. The black arrow points 
-to a horizontal band at $k_{||} \approx 0.6$~h~Mpc$^{-1}$, which cannot be accounted for 
+to a horizontal band at $k_{||} \approx 0.7$~h~Mpc$^{-1}$, which cannot be accounted for 
 by the coarse bands. \emph{Bottom:} After we implement the cable reflection fitting in our 
@@
 by propagating the sky model visibilities through the entire pipeline. Despite our foreground 
-model not containing spectral structure, the EoR window in the left panel seems to have a 
+model not containing spectral structure, the EoR window in the top panel seems to have a 
 floor at a level $\sim 10^7$~mK$^2$~h$^{-3}$~Mpc$^3$, comparable to predicted EoR 
@@
 
-The source of this floor and super-horizon line ended up being the resolution at which we 
+The source of this floor and super-horizon line was traced to the resolution at which we 
 formed the gridding kernel when gridding visibilities. In the interest of computational speed 
@@
 {Wayth:2015} was not available at the time of analysis.} \citep[MWACS, ][]
-{Hurley-Walker:2014}, Culgoora \citep{Slee:1977}, and the Molonglo Reference Catalog 
+{Hurley-Walker:2014}, the Culgoora catalog \citep{Slee:1977}, and the Molonglo Reference Catalog 
 \citep[MRC, ][]{Large:1981}. Source fluxes are prioritized in this order based on our 
@@
 more power, but it also confirms that our calibrated data is more closely matched to the 
-model, meaning that the higher flux scale seen in the left panel of Figure~
-\ref{fig:mwacs_diff}, and our calibration solutions in general, are more accurate.
+model, meaning that our calibration solutions in general are more accurate.
 
@@
 pointing steps prior to zenith transit, $0$ corresponding to zenith, and $+4$ corresponding 
-to four steps after zenith. Early in the night ($-5$ through $-3$) the bulk of the galactic plane 
+to four steps after zenith. 
+This numbering scheme is shown graphically in Figure~\ref{fig:pointing}.
+Early in the night ($-5$ through $-3$) the bulk of the galactic plane 
 was still above the horizon, and despite being very far from our primary field of view, highly 
@@
 \includegraphics[width=\columnwidth]{pointing_cartoon.pdf}
-\caption{\textcolor{red}{caption!}
+\caption{This is a cartoon depiction of the numbering scheme used to label pointings in
+Figures~\ref{fig:jackknife} and \ref{fig:wedge_cut}. Looking South, a field transits from the
+East (left), and the telescope begins observing about 5 pointings before zenith (-5). As the
+field drifts overhead, we periodically repoint the telescope to recenter the field. Each shift
+increments the pointing label by one, and the zenith pointing is defined as zero.
 \label{fig:pointing}
@@
 of 6.8. The right panels show the high band, centered at 190.1 MHz, or a redshift of 6.5. 
-The red box in the upper left panel shows the window used for averaging to one dimension.
+The contours show the window used for averaging to one dimension.
 \label{fig:2d_ps_subband}
@@
 our spectra appear noise-like (positive and negative values). This is encouraging despite 
-the leakage at lower $k_{||}$. The red box in the upper left 2D spectrum shows the region of 
-$\mathbf{k}$-space we use when averaging to one dimension. We exclude any voxels 
-below the solid black horizon line, as well as $k_{||}<0.1$ h Mpc$^{-1}$ due to foreground 
-contamination. We limit the $k_{\perp}$ range due to higher power in the coarse bands at 
-low $k_{\perp}$, and the poor $uv$ coverage at high $k_{\perp}$, leading to the vertical 
-streaks seen on the right side of the 2D spectra. We set our range to be $0.015$ h Mpc
-$^{-1} \leq k_{\perp} \leq 0.03$ h Mpc$^{-1}$. This is an aggressive cut, but confidently 
-avoids the vertical streaks of leaked power.
-
-One could additionally mask the coarse band harmonic lines when averaging to one 
-dimension. However, because $k_{||} \gg k_{\perp}$ within the red box, our spherical shells 
-are approximately constant $k_{||}$, so the coarse bands are still isolated in our average. 
-We choose to retain them to avoid empty bins, and to help guide the reader when 
-comparing the 2D and 1D spectra. While the red box is shown on the 2D plot, the actual 1D 
-averaging is done by returning to the full three dimensional power cubes and performing a 
-weighted average in shells.
+the leakage at lower $k_{||}$, and motivates us to be selective when binning to one 
+dimensional power spectra.
+
+Figure~\ref{fig:slices} shows slices of power that help isolate the contamination. The two 
+dimensional power spectrum is the N-S, mid band spectrum from 
+Figure~\ref{fig:2d_ps_subband}. We have drawn a horizontal solid blue line to indicate the 
+slice used to plot power as a function of $k_{\perp}$ for a fixed $k_{||}$ (top right), and a 
+vertical dashed line to show the slice used to plot power as a function of $k_{||}$ for a fixed 
+$k_{\perp}$ (bottom right). In the $k_{\perp}$ power plot we can see leakage at low and high
+$k_{\perp}$. On the low end this is due to the width of the coarse band harmonics and the
+exceptionally bright foregrounds at large scales. On the high end we are seeing the residual
+of the vertical streaks due to poor sampling at large $uv$. While the increased noise would
+mean that we will down weight the bins at large $k_{\perp}$, the contamination is even
+larger, meaning it would bias our estimate even though those bins are down weighted. 
+We exclude bins with $u<10\lambda$ and $u>70\lambda$, shown with grey boxes.
+Between these two regimes are many bins consistent with the noise level, which we include
+in our one dimensional averages.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{slices.pdf}
+\caption{
+\emph{Left:} The N-S, $z=6.8$ two dimensional power spectrum repeated from 
+Figure~\ref{fig:2d_ps_subband}. Here we have superimposed blue lines to show slices in
+$k_{\perp}$ (solid) and $k_{||}$ (dashed). \emph{Top right:} Residual power as a function
+of $k_{\perp}$ for fixed $k_{||}$. The grey boxes show regions which will be excluded from
+the one dimensional averages. The red dashed line shows the 1-$\sigma$ noise level, and
+the vertical black dashed line shows the intersection of this slice with the wedge. 
+\emph{Bottom right:} Residual power as a function of $k_{||}$ for fixed $k_{\perp}$. The strong
+foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
+appear as expected. 
+\label{fig:slices}
+}
+\end{center}
+\end{figure*}
+
+Similarly we inspect the $k_{||}$ power in the bottom right plot of Figure~\ref{fig:slices}. Here
+we see the huge contamination from foregrounds at low $k_{||}$. While the leakage drops 
+significantly, our measurements do not reach the noise level until after the first coarse
+band harmonic. However, we chose to include bins below the first coarse band with 
+$k_{||}>0.15$ h Mpc$^{-1}$ because the cosmological signal is expected to contain 
+substantially higher power at large scales, and ultimately these low $k_{||}$ bins provide
+our most competitive limits despite being systematic limited. We exclude the coarse band
+harmonics by masking out the harmonic bin itself and two bins on either side (total of five
+bins per harmonic).
+
+The final mask we apply is the wedge. We found that a small buffer beyond the horizon was
+necessary to completely mask out the wedge, consistent with \citealt{Dillon:2015}. We
+implement the buffer by extending the horizon line by 15 degrees. This line is shown as the
+dashed diagonal line in the left panel of Figure~\ref{fig:slices}.
+
+The various masking described above is summarized with the black contours shown on the
+two dimensional power spectra in Figure~\ref{fig:2d_ps_subband}. The contours show
+the cuts in two dimensional space, but the masking is actually performed directly in the
+three dimensional power spectrum cube and averaged directly to one dimension.
 
@@
 %	1D
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{1D_spectra_comparison.pdf}
+\caption{
+\textcolor{red}{Caption!}
+\label{fig:ps_comparison}
+}
+\end{figure}
 

### 2016-05-14 ms.tex
Starting to change text to match new(er) figures

@@
 the measured power is shown with solid blue, the 1-$\sigma$ noise level is shown with 
-dashed red, and the 2-$\sigma$ upper limit for each bin is shown with dashed magenta. 
-Where our unbiased estimator is negative, the absolute value is shown, but with a dashed 
-green line. For consistency with the literature, we plot our one dimensional power spectra 
+thin red, and the 2-$\sigma$ upper limit for each bin is shown with dashed magenta. 
+Where our unbiased estimator is negative, the absolute value is shown, but with a dotted 
+blue line. For consistency with the literature, we plot our one dimensional power spectra 
 as $\Delta^2(k)=k^3P_{21}(k)/(2\pi^2)$, which has units of mK$^2$.
@@
 corresponding to the bin size used in the average. Where the measured signal is negative 
-we plot the absolute value in green. The red dashed line is the 1-$\sigma$ noise level, and 
-the dashed magenta line is the 2-$\sigma$ upper limit for each $k$ bin. Theoretical models 
-from \citet{Lidz:2008} for $\overline{x}_i=0.54$, $0.82$, and $0.96$ are shown in the low, 
-mid, and high band spectra, respectively, in solid black. from \citet{Lidz:2008} are shown in 
-solid black. An additional theoretical model for a fully neutral IGM from 
-\citet{Furlanetto:2006} is shown with a dashed black line.
+we plot the absolute value with a dotted line. The thin red line is the 1-$\sigma$ noise level, and 
+the dashed magenta line is the 2-$\sigma$ upper limit for each $k$ bin. 
+A fiducial theoretical model for a fully neutral IGM from \citet{Furlanetto:2006} is shown
+in black for reference.
 \label{fig:1d_ps}
@@
 
+\textcolor{red}{this needs to be rewritten}
 In all bands and polarizations, we are heavily signal dominated in our most sensitive region 

### 2016-05-16 ms.tex
More touchups to text of paper

@@
 to account for the interference of the incident signal with a round-trip reflected signal in the 
-cable. The full gain model is expressed as
+cable. 
+A similar approach was taken at lower frequencies in \citealt{Ewall-Wice:2016}.
+The full gain model is expressed as
 \begin{equation}\label{eq:cal2}
@@
 
-\textcolor{red}{this needs to be rewritten}
 In all bands and polarizations, we are heavily signal dominated in our most sensitive region
-(low $k$). This is not surprising based on the 2D spectra we examined earlier. We can see 
-the strong coarse band harmonic lines, and the cable reflection line between the first two 
-coarse band lines. But between these coarse lines there are bins which approach the noise 
-level and are consistent with zero (notably the North-South polarization for the $z=7.1$ and 
-$z=6.8$ bands). These regions are encouraging because they have the potential to 
-continue integrating down with more data.
-
-However, our best upper limits for a cosmological signal are still at low $k$, despite the 
+(low $k$). This is not surprising based on the 2D spectra we examined earlier. The gaps in
+the data are due to the excised coarse band harmonics. We can see the cable reflection line
+between the first two gaps in all polarizations and sub-bands. Between the coarse band
+harmonic lines, especially at larger $k$, are bins which approach the noise level and are
+consistent with zero (notably the North-South polarization for the low and mid bands). The
+bin just above the first coarse band harmonic is also consistent with zero in the low band.
+These regions are encouraging because they have the potential to continue integrating down
+with more data. Improved suppression of the coarse band harmonic and cable reflection lines
+will also improve the limits presented here.
+
+Our best upper limits for a cosmological signal are at low $k$, despite the 
 strong leakage. Because any foreground leakage should not correlate with the EoR signal, 
@@
 \tableline
-Low & 7.1 & E-W & 0.231 & 3.02 $\times 10^4$\\
-Low & 7.1 & N-S & 0.231 & 2.22 $\times 10^4$\\
-Mid & 6.8 & E-W & 0.2361 & 2.84 $\times 10^4$\\
-Mid & 6.8 & N-S & 0.2361 & 2.17 $\times 10^4$\\
-High & 6.5 & E-W & 0.204 & 5.24 $\times 10^4$\\
-High & 6.5 & N-S & 0.241 & 3.11 $\times 10^4$\\
+Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$\\
+Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$\\
+Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$\\
+Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$\\
+High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$\\
+High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$\\
 \tableline

### 2016-05-18 ms.tex
reordering authors

@@
 \affilauthorlist{
-A.~P.~Beardsley\affils{ASU,UW}\myemail,
+A.~P.~Beardsley\affils{ASU}\myemail,
 B.~J.~Hazelton\affils{UW,UWeSci},
 I.~S.~Sullivan\affils{UW},
-J.~C.~Pober\affils{Brown,UW},
 P.~Carroll\affils{UW},
 N.~Barry\affils{UW},
+M.~Rahimi\affils{UMelbourne},
+B.~Pindor\affils{UMelbourne,CAASTRO},
+C.~M.~Trott\affils{Curtin,CAASTRO},
+Daniel~C.~Jacobs\affils{ASU},
 M.~F.~Morales\affils{UW}, 
-Daniel~C.~Jacobs\affils{ASU},
+J.~C.~Pober\affils{Brown,UW},
 G.~Bernardi\affils{SKASA,RU,CfA},
@@
 S. Paul\affils{RRI},
-B.~Pindor\affils{UMelbourne,CAASTRO},
 T.~Prabu\affils{RRI}, 
 P.~Procopio\affils{UMelbourne,CAASTRO},
-M.~Rahimi\affils{UMelbourne},
 J.~Riding\affils{UMelbourne,CAASTRO},
@@
 S.~J.~Tingay\affils{Curtin,CAASTRO}, 
-C.~M.~Trott\affils{Curtin,CAASTRO},
 M.~Waterson\affils{Curtin,ANU},

### 2016-05-19 ms.tex
promoting jacks author placement

@@
 C.~M.~Trott\affils{Curtin,CAASTRO},
+J.~Line\affils{UMelbourne,CAASTRO},
 Daniel~C.~Jacobs\affils{ASU},
@@
 E.~Lenc\affils{USydney,CAASTRO},
-J.~Line\affils{UMelbourne,CAASTRO},
 A.~Loeb\affils{CfA},

### 2016-05-19 ms.tex
added rts-chips data to limit table, switched to deluxetable

@@
 
-\begin{table}
-\begin{center}
-\caption[EoR power spectrum limits]{Upper limits on the EoR power spectrum for our three 
+\begin{deluxetable}{ccccccc}
+\tabletypesize{\footnotesize}
+%\tablecolumns{7}
+\tablewidth{\columnwidth}
+\tablecaption{Upper limits on the EoR power spectrum for our three 
 sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
 confidence level.
+Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$.
+The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
 \label{tbl:limits}
 }
-\begin{tabular}{ccccc}
-\tableline\tableline
-Sub-band & $z_0$ & Polarization & $k$ (h Mpc$^{-1}$) & $\Delta^2_{\text{UL}}$ (mK$^2$) \\
-\tableline
-Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$\\
-Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$\\
-Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$\\
-Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$\\
-High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$\\
-High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$\\
-\tableline
-\end{tabular}
-\end{center}
-\end{table}
+\tablehead{
+& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
+Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
+}
+\startdata
+Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
+Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.154 & 9.3 $\times 10^4$ \\
+Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
+Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.154 & 6.8 $\times 10^4$ \\
+High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
+High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.154 & 8.1 $\times 10^4$ \\
+\enddata
+\end{deluxetable}
 

### 2016-05-19 ms.tex
updated chips limits with latest

@@
 Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
-Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.154 & 9.3 $\times 10^4$ \\
+Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.15 & 4.0 $\times 10^4$ \\
 Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
-Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.154 & 6.8 $\times 10^4$ \\
+Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.15 & 3.0 $\times 10^4$ \\
 High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
-High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.154 & 8.1 $\times 10^4$ \\
+High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.15 & 3.2 $\times 10^4$ \\
 \enddata

### 2016-05-25 ms.tex
Updated caption to slice figure to mention RTS-CHIPS lines
Updated limit table for new CHIPS values

@@
 foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
-appear as expected. 
+appear as expected. The thin black line in both right panels is the equivalent power slice from the RTS-CHIPS comparison pipeline, which is discussed in Section~\ref{subsec:ref_pipe}.
 \label{fig:slices}
@@
 Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
-Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.15 & 4.0 $\times 10^4$ \\
+Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.12 & 2.5 $\times 10^4$ \\
 Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
-Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.15 & 3.0 $\times 10^4$ \\
+Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.14 & 2.2 $\times 10^4$ \\
 High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
-High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.15 & 3.2 $\times 10^4$ \\
+High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.12 & 2.3 $\times 10^4$ \\
 \enddata

### 2016-05-26 ms.tex
Updated upper limit table, this time with correct values

@@
 Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
-Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.12 & 2.5 $\times 10^4$ \\
+Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.16 & 3.2 $\times 10^4$ \\
 Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
-Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.14 & 2.2 $\times 10^4$ \\
+Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.14 & 2.6 $\times 10^4$ \\
 High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
-High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.12 & 2.3 $\times 10^4$ \\
+High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.14 & 2.5 $\times 10^4$ \\
 \enddata

### 2016-05-26 ms.tex
Add files via upload
Updated ms.tex with Cath's comments and some text for the ref pipeline section. All changes/suggestions made with \textbf{}.

@@
 mixing, throwing power from spectrally smooth foregrounds to higher Fourier modes 
-\citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2014, Liu:2014a, Liu:2014b, 
+\citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2012, Liu:2014a, Liu:2014b, 
 Hazelton:2013, Pober:2013, Vedantham:2012, Morales:2012, Datta:2010}. Despite this 
@@
 prep; D.~A.~Mitchell et al. 2016, in prep; D.~C.~Jacobs et al. 2016, in review; ][]{Trott:2016, 
-Dillon:2013, Trott:2012}.
+Dillon:2013, Trott:2014}.
 
@@
 describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our 
-efforts to apply the analysis pipeline to a deep data integration, and we discuss future work 
+efforts to apply the analysis pipeline to a deep data integration \textbf{and compare with a reference pipeline for robust estimation}, and we discuss future work 
 in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM 
@@
 beamformer which uses physical delays to ``point" the antenna. The MWA contains 128 of 
-these antennas, with a tightly packed core of radius 50 m, and extending out to a radius 
+these antennas, with a tightly packed core of radius 50 m, and extending out to a radius \textbf{of}
 1.5 km for higher resolution calibration and imaging.
@@
 give an overview below.
+\textbf{As a point of comparison, and to demonstrate robustness of the results, we compute the output power spectra with an independent calibration and power spectrum estimation pipeline, and demonstrate consistency.}
 
@@
 central fine channel of each coarse band because it corresponds to the DC mode of that 
-sub-band and can easily float, washing out useful information.
+sub-band and can easily float, washing out useful information. \textbf{Please reword this sentence. It is not clear what "float" means here. Can you be more specific?}
 
@@
 \textcolor{red}{Needs a better section title}
-
-The two dimensional power spectrum is a useful figure of merit (FoM) as we improve and 
+\textbf{Analysis Methods for Testing Data Quality}
+
+The two dimensional power spectrum is a useful figure of merit (FoM) \textbf{(the PS is more of a tool than a FoM)} as we improve and 
 refine our analysis pipeline. Foregrounds and systematics often manifest with characteristic 
@@
 model, meaning that our calibration solutions in general are more accurate.
+\textbf{Consider adding a reference and a sentence about Jack's paper here.
+Her performed quite a few of these type of tests for understanding the impact of having an incomplete point source model.}
 
@@
 and negative, indicating that any differences are below the three hour noise level.
+\textbf{Why is the region in the EoR window red here, particularly when the lower plot shows noise-like differences?}
 
@@
 highlight lessons learned from the comparison.
+
+\textbf{The RTS uses a fundamentally different calibration and foreground subtraction approach than FHD, as well as a different input point source model.
+The primary differences lie in the bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model.
+The calibration model uses a model with 1000 sources, for which ionospheric corrections are estimated and applied, before peeling of those sources from the dataset.
+The bandpass calibration is fundamentally different to FHD...
+**BART: please also include a mention of the 150m cable reflection and why we may not expect to see it with RTS**.
+The CHIPS power spectrum estimator applies a full maximum-likelihood estimator to the data.
+In its full form, the data are weighted by the thermal noise, and a model for the residual point source signal, within a full frequency-dependent description of the instrument.
+For this comparison, the foreground weighting is not used, in order for a direct comparison with the weighting scheme used by eppsilon.}
+
+\textbf{Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS pipeline successfully calibrated and included 1,003.
+The remainder failed to calibrate successfully, potentially due to adverse ionospheric conditions.
+The data were divided into the same three redshift bins, and the 2D and 1D power spectra formed.
+Table \ref{tbl:limits} displays comparison 2-sigma upper limits, demonstrating broad consistency between the pipelines.
+The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$eppsilon, owing to the different structure of the foreground leakage for the two pipelines.
+Figure \ref{fig:slices}, which shows the resulting FHD$+$eppsilon slices in $k_\parallel$ and $k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS.
+The comparison pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model being subtracted from the data.
+Aside from this area, the two pipelines show consistent results.
+Figure \ref{fig:ps_comparison} compares the 1D power from both pipelines for the three central redshifts studied in this work.
+The magenta line reproduces the FHD$+$eppsilon results from Figure \ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS results (with coarse band harmonics included).
+Despite the differences in the two pipelines, they produce consistent power across a range of scales, supporting the robustness of the results.}
 

### 2016-06-02 ms.tex
Addressing Caths comments, updating a couple references

@@
 several analysis pipelines under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
-prep; D.~A.~Mitchell et al. 2016, in prep; D.~C.~Jacobs et al. 2016, in review; ][]{Trott:2016, 
+prep; D.~A.~Mitchell et al. 2016, in prep; ][]{Jacobs:2016, Trott:2016, 
 Dillon:2013, Trott:2014}.
@@
 describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our 
-efforts to apply the analysis pipeline to a deep data integration \textbf{and compare with a reference pipeline for robust estimation}, and we discuss future work 
+efforts to apply the analysis pipeline to a deep data integration and compare with a reference pipeline for robust estimation, and we discuss future work 
 in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM 
@@
 beamformer which uses physical delays to ``point" the antenna. The MWA contains 128 of 
-these antennas, with a tightly packed core of radius 50 m, and extending out to a radius \textbf{of}
+these antennas, with a tightly packed core of radius 50 m, and extending out to a radius of
 1.5 km for higher resolution calibration and imaging.
@@
 defined two independent reference analysis pipelines. The details of this strategy are 
-outlined in D.~C.~Jacobs et al. 2016 (in review). This study is based on the FHD-to-
-\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution (FHD
-\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
+outlined in \citealt{Jacobs:2016}. This study is based on the FHD-to-
+\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution 
+(FHD\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
 Propagated Power Spectrum with Interleaved Observed Noise (\eppsilon
@@
 give an overview below.
-\textbf{As a point of comparison, and to demonstrate robustness of the results, we compute the output power spectra with an independent calibration and power spectrum estimation pipeline, and demonstrate consistency.}
+As a point of comparison, and to demonstrate robustness of the results, we compute the output power spectra with an independent calibration and power spectrum estimation pipeline, and demonstrate consistency.
 
@@
 flagging, averages in time and freqeuncy, and writes to disk. For this step we use the 
-\cotter package, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://
+\cotter package \citep{Offringa:2015}, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://
 aoflagger.sourceforge.net/}} to perform RFI flagging \citep{Offringa:2010}.
@@
 problem has since been resolved, but exists in our data. We therefore flag the first two 
-seconds of each observation to avoid any potentially mis-pointed data. Finally, we flag the 
-central fine channel of each coarse band because it corresponds to the DC mode of that 
-sub-band and can easily float, washing out useful information. \textbf{Please reword this sentence. It is not clear what "float" means here. Can you be more specific?}
+seconds of each observation to avoid any potentially mis-pointed data. 
+Finally, we flag the central fine channel of each coarse band. This channel corresponds
+to the sub-band DC mode, which has been observed to contain anomalous power likely
+due to very low level rounding errors in the polyphase filter bank of the digital receivers.
 
@@
 
-\section{Novel Analysis Methods}\label{sec:techniques}
-\textcolor{red}{Needs a better section title}
-\textbf{Analysis Methods for Testing Data Quality}
+\section{Analysis Methods for Testing Data Quality}\label{sec:techniques}
 
@@
 
-The resulting hierarchical catalog is shown in Figure~\ref{fig:master_catalog}. The EoR0 
-field corresponds to the red FHD source patch. All sources above the horizon and within a 
-primary beam value greater than 1\% maximum (including sidelobes) are included in both 
-our calibration and foreground subtraction models.
-
 \begin{figure*}
@@
 \end{figure*}
+
+The resulting hierarchical catalog is shown in Figure~\ref{fig:master_catalog}. The EoR0 
+field corresponds to the red FHD source patch. All sources above the horizon and within a 
+primary beam value greater than 1\% maximum (including sidelobes) are included in both 
+our calibration and foreground subtraction models.
 
@@
 model, meaning that our calibration solutions in general are more accurate.
-\textbf{Consider adding a reference and a sentence about Jack's paper here.
-Her performed quite a few of these type of tests for understanding the impact of having an incomplete point source model.}
 
@@
 
+J.~L.~B.~Line, et al (2016, in review) performed similar analysis, but with an emphasis on the
+positional accuracy of catalog entries. By using simulations of visibilities they were able to 
+isolate the effect of using perfect versus offset source positions. They confirmed the
+importance of a complete and accurate point source catalog in order to retain a clean EoR
+window.
+
 \subsection{Diffuse Foreground Model Subtraction}
@@
 diffuse subtracted from the model power without. The entire plot is negative (red) because 
-we only added power with the diffuse model. The bottom panel is the difference in residual 
+we only added power with the diffuse model. 
+Even the EoR window is red (albeit at a much lower level than the wedge) because of power
+leakage from non-uniform spectral sampling and from the dynamic range limit of the 
+Blackman-Harris window function.
+The bottom panel is the difference in residual 
 power. The wedge is completely positive (blue), indicating that the diffuse model 
 successfully subtracted from the dirty visibilities. The differences in the window are positive 
-and negative, indicating that any differences are below the three hour noise level.
-\textbf{Why is the region in the EoR window red here, particularly when the lower plot shows noise-like differences?}
+and negative, indicating that 
+the differences in the foreground model in this region are below the three hour noise level.
 
@@
 
-As demonstrated in D.~C.~Jacobs et al. 2016 (in review), comparison between independent 
+As demonstrated in \citealt{Jacobs:2016}, comparison between independent 
 analysis pipelines is essential to evaluate the validity of algorithms under active development. 

### 2016-06-02 ms.tex
Wrote caption for PS comparison plot, broke up comparison text for easier version tracking

@@
 foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
-appear as expected. The thin black line in both right panels is the equivalent power slice from the RTS-CHIPS comparison pipeline, which is discussed in Section~\ref{subsec:ref_pipe}.
+appear as expected. The thin black line in both right panels is the equivalent power slice from the RTS$+$CHIPS comparison pipeline, which is discussed in Section~\ref{subsec:ref_pipe}.
 \label{fig:slices}
@@
 Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$.
-The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
+The last two columns, RTS$+$CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
 \label{tbl:limits}
@@
 \tablehead{
-& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
+& & & \multicolumn{2}{c}{FHD$+$\eppsilon} & \multicolumn{2}{c}{RTS$+$CHIPS} \\
 Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
@@
 
-\textbf{The RTS uses a fundamentally different calibration and foreground subtraction approach than FHD, as well as a different input point source model.
-The primary differences lie in the bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model.
-The calibration model uses a model with 1000 sources, for which ionospheric corrections are estimated and applied, before peeling of those sources from the dataset.
-The bandpass calibration is fundamentally different to FHD...
-**BART: please also include a mention of the 150m cable reflection and why we may not expect to see it with RTS**.
-The CHIPS power spectrum estimator applies a full maximum-likelihood estimator to the data.
-In its full form, the data are weighted by the thermal noise, and a model for the residual point source signal, within a full frequency-dependent description of the instrument.
-For this comparison, the foreground weighting is not used, in order for a direct comparison with the weighting scheme used by eppsilon.}
-
-\textbf{Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS pipeline successfully calibrated and included 1,003.
-The remainder failed to calibrate successfully, potentially due to adverse ionospheric conditions.
-The data were divided into the same three redshift bins, and the 2D and 1D power spectra formed.
-Table \ref{tbl:limits} displays comparison 2-sigma upper limits, demonstrating broad consistency between the pipelines.
-The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$eppsilon, owing to the different structure of the foreground leakage for the two pipelines.
-Figure \ref{fig:slices}, which shows the resulting FHD$+$eppsilon slices in $k_\parallel$ and $k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS.
-The comparison pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model being subtracted from the data.
-Aside from this area, the two pipelines show consistent results.
-Figure \ref{fig:ps_comparison} compares the 1D power from both pipelines for the three central redshifts studied in this work.
-The magenta line reproduces the FHD$+$eppsilon results from Figure \ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS results (with coarse band harmonics included).
-Despite the differences in the two pipelines, they produce consistent power across a range of scales, supporting the robustness of the results.}
+The RTS uses a fundamentally different calibration and foreground subtraction approach than 
+FHD, as well as a different input point source model. The primary differences lie in the 
+bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
+calibration model uses a model with 1000 sources, for which ionospheric corrections are 
+estimated and applied, before peeling of those sources from the dataset. The bandpass 
+calibration is fundamentally different to FHD... \textbf{**BART: please also include a mention of 
+the 150m cable reflection and why we may not expect to see it with RTS**.} The CHIPS power 
+spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
+data are weighted by the thermal noise, and a model for the residual point source signal, 
+within a full frequency-dependent description of the instrument. For this comparison, the 
+foreground weighting is not used, in order for a direct comparison with the weighting scheme 
+used by \eppsilon.
+
+Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
+pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
+successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
+same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
+displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
+pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
+owing to the different structure of the foreground leakage for the two pipelines. 
+Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
+$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
+pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
+being subtracted from the data. Aside from this area, the two pipelines show consistent 
+results. Figure \ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
+three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
+results from Figure \ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
+results (with coarse band harmonics included). Despite the differences in the two pipelines, 
+they produce consistent power across a range of scales, supporting the robustness of the 
+results.
 
@@
 \caption{
-\textcolor{red}{Caption!}
+Here we compare the upper limits from the FHD$+$\eppsilon pipeline with those from the 
+RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure \ref{fig:1d_ps}, and the blue line
+is the power plus two sigma thermal error bars line generated by CHIPS. CHIPS does not 
+excise the coarse band harmonic lines, and so we see their strong effect where there are 
+gaps in the magenta lines. The most notable differences are the ability of the RTS$+$CHIPS pipe
+to access lower $k$ modes, while the FHD$+$\eppsilon pipe suppresses moe power before and
+after the first coarse band harmonic. While the different analysis methods result in slightly
+different upper limits, they are generally in agreement. 
 \label{fig:ps_comparison}

### 2016-06-02 ms.tex
Minor edits for style consistency

@@
 Early in our analysis it became apparent that the bandpass of each MWA antenna requires 
-more free parameters than those described in equation~\ref{eq:cal1}. In particular, differing 
+more free parameters than those described in Equation~\ref{eq:cal1}. In particular, differing 
 beamformer to receiver cables lead to different bandpass shapes due to signal attenuation. 
@@
 \includegraphics[width=\columnwidth]{mwacs_ratio.pdf}
-\caption{Power spectrum ratio difference, according to equation~\ref{eq:diff_ratio}. This 
+\caption{Power spectrum ratio difference, according to Equation~\ref{eq:diff_ratio}. This 
 metric shows the difference in the fractional E-W residual 2D power spectrum, comparing 
@@
 being subtracted from the data. Aside from this area, the two pipelines show consistent 
-results. Figure \ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
+results. Figure~\ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
 three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
-results from Figure \ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
+results from Figure~\ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
 results (with coarse band harmonics included). Despite the differences in the two pipelines, 
@@
 Here we compare the upper limits from the FHD$+$\eppsilon pipeline with those from the 
-RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure \ref{fig:1d_ps}, and the blue line
+RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure~\ref{fig:1d_ps}, and the blue line
 is the power plus two sigma thermal error bars line generated by CHIPS. CHIPS does not 

### 2016-06-03 ms.tex
Slight rewording for clarification
Attempt at writing RTS bandpass cal sentences.

@@
 seconds of each observation to avoid any potentially mis-pointed data. 
-Finally, we flag the central fine channel of each coarse band. This channel corresponds
+Finally, we flag the central 40 kHz channel of each coarse band. This channel corresponds
 to the sub-band DC mode, which has been observed to contain anomalous power likely
@@
 
-The two dimensional power spectrum is a useful figure of merit (FoM) \textbf{(the PS is more of a tool than a FoM)} as we improve and 
+The two dimensional power spectrum is a useful figure of merit (FoM) as we improve and 
 refine our analysis pipeline. Foregrounds and systematics often manifest with characteristic 
@@
 estimated and applied, before peeling of those sources from the dataset. The bandpass 
-calibration is fundamentally different to FHD... \textbf{**BART: please also include a mention of 
-the 150m cable reflection and why we may not expect to see it with RTS**.} The CHIPS power 
+calibration is fundamentally different to FHD.
+The bandpass for each antenna is fit to a 2nd order polynomial within each 1.28~MHz coarse 
+band individually. The delay of the 150~m cable reflection discussed earlier is comparable
+to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
+solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
+data \citep{Jacobs:2016}.
+The CHIPS power 
 spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 

### 2016-06-03 ms.tex
crossing ts and dotting lower case js

@@
 \usepackage{xspace}
+\usepackage{hyperref}
+\hypersetup{
+     colorlinks   = true,
+     allcolors    = blue
+}
 
@@
 \DeclareAffil{ASU}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
+\DeclareAffil{email}{e-mail: Adam.Beardsley@asu.edu}
 \DeclareAffil{UW}{University of Washington, Department of Physics, Seattle, WA 98195, USA}
@@
 \affilauthorlist{
-A.~P.~Beardsley\affils{ASU}\myemail,
+A.~P.~Beardsley\affils{ASU,email},
 B.~J.~Hazelton\affils{UW,UWeSci},
@@
 defined two independent reference analysis pipelines. The details of this strategy are 
-outlined in \citealt{Jacobs:2016}. This study is based on the FHD-to-
-\eppsilon pipe, which is in turn based on the Fast Holographic Deconvolution 
+outlined in \citealt{Jacobs:2016}. This study is based on the FHD-to-\eppsilon 
+pipe, which is in turn based on the Fast Holographic Deconvolution 
 (FHD\footnote{\url{https://github.com/EoRImaging/FHD}}, \citealt{Sullivan:2012}) and Error 
@@
 
-In the first calibration step we allow our complex gains to account for any direction-
-independent response on a per antenna, per frequency channel, per polarization basis. To 
-define our gains in this way, we have made two simplifications. First we push all direction-
-dependence of the antenna response into the model of the primary beam. FHD is capable 
+In the first calibration step we allow our complex gains to account for any direction-independent 
+response on a per antenna, per frequency channel, per polarization basis. To 
+define our gains in this way, we have made two simplifications. First we push all 
+direction-dependence of the antenna response into the model of the primary beam. FHD is capable 
 of using separate models for each antenna, though this has not yet been implemented for 
@@
 carry the model through the entire pipeline, and only subtract just before squaring to power 
-spectrum units, allowing to form power spectra of the dirty, model, and residual data.
+spectrum units, allowing us to form power spectra of the dirty, model, and residual data.
 
@@
 reflection line for the three hour golden set integration, the lower noise level in this deeper 
-integration shows it is not completely removed. Future analysis will require higher signal-to-
-noise on the reflection fitting, which may require combining snapshots for calibration 
+integration shows it is not completely removed. Future analysis will require higher 
+signal-to-noise on the reflection fitting, which may require combining snapshots for calibration 
 solutions.
@@
 calibration is fundamentally different to FHD.
-The bandpass for each antenna is fit to a 2nd order polynomial within each 1.28~MHz coarse 
+The bandpass for each antenna is fitted to a 2nd order polynomial within each 1.28~MHz coarse 
 band individually. The delay of the 150~m cable reflection discussed earlier is comparable
@@
 This work was supported by NSF grants AST-1410484 and AST-1206552.
-JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award 
-AST-1302774. This scientific work makes use of the Murchison Radio-astronomy 
+DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship
+under award AST-1401708.
+This scientific work makes use of the Murchison Radio-astronomy 
 Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the 

### 2016-06-10 ms.tex
Addressing NHWs comments

@@
 complete by $z \approx 6$, a result which was confirmed independent of model by 
-\citealt{McGreer:2015}. Deep optical and infrared galaxy surveys are also beginning to 
+\citealt{McGreer:2015}.
+Using a $z_{\mathrm{end}}>6$ prior, the most recent analysis of \emph{Planck} data 
+found a reionization redshift $z_{\mathrm{re}} = 8.8 \pm 0.9$ for a redshift-symmetric model
+($z_{\mathrm{re}} = 8.5 \pm 0.9$ for redshift-asymmetric), and a duration of $\Delta z < 2.8$
+\citep{Planck:2016}.
+Deep optical and infrared galaxy surveys are also beginning to 
 reach the redshifts necessary to further constrain reionization \citep[e.g.][]{Bouwens:2014}, 
@@
 While the 21 cm EoR signal is priority, the MWA is a general observatory serving several 
-science programs beyond cosmology including galactic and extragalactic surveys, time 
+science programs beyond cosmology including Galactic and extragalactic surveys, time 
 domain astrophysics, solar monitoring, and ionospheric science. The array was thus 
@@
 the field, which digitize the signal and perform a first stage coarse frequency 
-channelization of the data (1.28 MHz sub-bands)\citep{Prabu:2015}. This channelization 
+channelization of the data (1.28 MHz coarse bands)\citep{Prabu:2015}. This channelization 
 applies a filter shape and aliases edge channels, which will later be flagged in our analysis. 
-The observer now selects 24 sub-bands (30.72 MHz total bandwidth) to pass onto the 
+The observer now selects 24 coarse bands (30.72 MHz total bandwidth) to pass onto the 
 correlator via fiber optic link. The correlator further channelizes the data to 10 kHz 
@@
 repeated until the field is too low in the sky to track. We have identified three EoR fields 
-relatively devoid of galactic emission and bright extragalactic sources for observing: 
-``EoR0" (RA $=0.00$ h, dec $= -27^\circ$), ``EoR1" (RA $=4.00$ h, dec $= -27^\circ$), 
-and ``EoR2" (RA $=11.33$ h, dec $= -10^\circ$). In addition, we observe these fields in 
+relatively devoid of Galactic emission and bright extragalactic sources for observing: 
+``EoR0" (Right Ascension (RA) $=0.00$ h, Declination (Dec) $= -27^\circ$), ``EoR1" (RA $=4.00$ h, Dec $= -27^\circ$), 
+and ``EoR2" (RA $=11.33$ h, Dec $= -10^\circ$). In addition, we observe these fields in 
 high and low bands centered at 182 MHz ($z\approx6.8$) and 154 MHz ($z\approx8.2$) 
@@
 The preprocessing step converts the data from the non-standard memory dump format 
-from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, performs 
+from the correlator's GPUs to a standard UVFITS format \citep{Greisen:2012}, 
+phases the data to the center of the pointing,
+performs 
 flagging, averages in time and freqeuncy, and writes to disk. For this step we use the 
@@
 Finally, we flag the central 40 kHz channel of each coarse band. This channel corresponds
-to the sub-band DC mode, which has been observed to contain anomalous power likely
+to the coarse band DC mode, which has been observed to contain anomalous power likely
 due to very low level rounding errors in the polyphase filter bank of the digital receivers.
@@
 principle these terms would introduce baseline dependent gains, rather than antenna 
-dependent. The MWA has not yet seen evidence of these terms, and so we currently 
+dependent. We have not yet seen evidence of these terms in MWA data, and so we currently 
 neglect them in our solutions.
@@
 dependent deviations. We also found it necessary to include terms dependent on the 
-beamformer to receiver cable length, which we will discuss in Subsection~\ref{sec:cables}.
+length of the cable connecting the beamformers to the receivers, which we will discuss in Subsection~\ref{sec:cables}.
 
@@
 combining images in the sense that it preserves all information for parameter estimation 
-\citep{Morales:2009,Bhatnagar:2008}. We use a simulation based beam model for MWA 
+\citep{Morales:2009,Bhatnagar:2008}. We use a simulation-based primary beam model for MWA 
 antennas developed by \citealt{Sutinjo:2015}. At this stage we also average in frequency by 
-a factor of two by gridding pairs of frequency channels to the same $uv$ plane, resulting in 
+a factor of two by gridding pairs of frequency channels to the same $(u,v)$ plane, resulting in 
 a frequency resolution of 160 kHz.
 
-The gridded $uv$ data are then Fourier transformed to create sky-frame images. To avoid 
+The gridded $(u,v)$ data are then Fourier transformed to create sky-frame images. To avoid 
 aliasing we image out 90$^\circ$ from phase center (gridding resolution of a half 
@@
 pixels to interpolate to, and use the same set for all snapshots on a given field. The final 
-cropped field of view for this work is a 21$^\circ$ square centered at RA~$=0$ h, dec~
+cropped field of view for this work is a 21$^\circ$ square centered at RA~$=0$ h, Dec~
 $=-27^\circ$.
@@
 we conceptually group it with the power spectrum step. This is because all steps of the 
-pipeline up to here have been performed on a per-snapshot basis (no communication 
+pipeline up to this point have been performed on a per-snapshot basis (no communication 
 between snapshots beyond foreground modeling), and the integration step can be used to 
@@
 sight. The Fourier transform along the $r_{||}$ dimension is treated separately due to 
-incomplete $uv$ sampling and flagged frequency channels, which leads to structure in the 
+incomplete $(u,v)$ sampling and flagged frequency channels, which leads to structure in the 
 frequency sampling along any given $k_{\perp}$ pixel. We thus adopt the Lomb-Scargle 
 least-squares method to determine the orthogonal eigenfunctions given our sampling 
-function and estimating the total power in each $k_{||}$ mode \citep{Scargle:1982}. In 
+function and estimate the total power in each $k_{||}$ mode \citep{Scargle:1982}. In 
 addition, because the spectrally smooth foregrounds contain vastly more power than the 
@@
 \begin{center}
-\includegraphics[width=.9\columnwidth]{example_ps.pdf}
+\includegraphics[width=\columnwidth]{example_ps.pdf}
 \caption{
 An example two dimensional, E-W polarization residual power spectrum formed using the 
-three hour golden data set. The foreground wedge dominates the region below the solid 
+three hour golden data set
+from August 23, 2013. The foreground wedge dominates the region below the solid 
 black horizon line, while regions above are mostly noise-like with the exception of horizontal 
@@
 referred to as the coarse band harmonics. We see vertical streaks at high $k_{||}$ and high 
-$k_{\perp}$. These are due to sparse $uv$ sampling beyond the dense core of the MWA 
-(starting $\sim70\lambda$), and the foreground power getting thrown to high spectral 
+$k_{\perp}$. These are due to sparse $(u,v)$ sampling beyond the dense core of the MWA 
+(starting $\sim70\lambda$), and the foreground power mixing to high spectral 
 modes. Between the coarse band lines and to the left of the vertical streaks we see regions 
@@
 
-The two dimensional power spectrum is a useful figure of merit (FoM) as we improve and 
+The two-dimensional power spectrum is a useful figure of merit (FoM) as we improve and 
 refine our analysis pipeline. Foregrounds and systematics often manifest with characteristic 
@@
 more free parameters than those described in Equation~\ref{eq:cal1}. In particular, differing 
-beamformer to receiver cables lead to different bandpass shapes due to signal attenuation. 
+lengths of cable connecting the beamformers to the receivers
+ lead to different bandpass shapes due to signal attenuation. 
 We therefore allow the amplitude bandpass factor to depend on cable length, $B_{\alpha}
@@
 \begin{center}
-\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_pre.pdf}}
+\subfigure{\includegraphics[width=\columnwidth]{fourth_line_pre.pdf}}
 ~
-\subfigure{\includegraphics[width=.9\columnwidth]{fourth_line_post.pdf}}
+\subfigure{\includegraphics[width=\columnwidth]{fourth_line_post.pdf}}
 \caption{
@@
 \subsection{Gridding Kernel Resolution}
-A similar, low level effect which had the potential to contaminate the EoR window is shown 
+A similar, low-level effect which had the potential to contaminate the EoR window is shown 
 in Figure~\ref{fig:beam_res}. The spectra shown are the \emph{model} spectra -- calculated 
@@
 \begin{center}
-\subfigure{\includegraphics[width=.9\columnwidth]{before_beam_resolution_golden.pdf}}
+\subfigure{\includegraphics[width=\columnwidth]{before_beam_resolution_golden.pdf}}
 ~
-\subfigure{\includegraphics[width=.9\columnwidth]{after_beam_resolution_golden.pdf}}
+\subfigure{\includegraphics[width=\columnwidth]{after_beam_resolution_golden.pdf}}
 \caption{
@@
 comparable to an expected EoR signal, and a faint super-horizon line appears at high 
-$k_{||}$. \emph{Bottom:} Model power spectrum after increasing the gridding kernel 
+$k_{||}$. 
+The black arrow indicates the location and direction of the faint line.
+\emph{Bottom:} Model power spectrum after increasing the gridding kernel 
 resolution from 0.04 wavelengths to 0.007 wavelengths. The floor is now far below the 
@@
 smaller than the half wavelength grid corresponding to horizon to horizon imaging. 
-However, as a baseline migrates in $\emph{uv}$ coordinates across frequencies, it 
+However, as a baseline migrates in $(u,v)$ coordinates across frequencies, it 
 undergoes discrete steps between kernel values used. This effectively results in small 
-baseline position errors which shift periodically in frequency, resulting in power being thrown 
-up into the window and a relatively strong harmonic at the frequency of the shifting (the faint 
+baseline position errors which shift periodically in frequency, resulting in power being mixed 
+into the window and a relatively strong harmonic at the frequency of the shifting (the faint 
 line in the upper left of the window). While we illustrate this effect with a model power 
@@
 We resolved this issue by increasing the resolution at which we form the kernel. While the 
-most accurate answer is to model at infinite resolution, it is not feasible to do so 
-computationally. Instead we chose a resolution at which the effect no longer materially 
+most accurate answer is to model at infinite resolution, it is not computationally feasible to do 
+so. Instead we chose a resolution at which the effect no longer materially 
 impacts the power spectrum. With experimentation we found a kernel resolution of 0.007 
@@
 panel of Figure~\ref{fig:beam_res}. The contamination within the EoR window now drops 
-significantly below the predicted cosmological signal levels.
+significantly below the predicted cosmological signal levels. This improvement in beam
+model resolution came at the cost of 20\% increase in memory usage for our imaging
+pipeline.
 
@@
 primary beam will not be sufficient to suppress the power spectrum wedge and unlock the 
-EoR window \citep{Pober:2016, Thyagarajan:2015, Thyagarajan:2015b}. In principle we 
+EoR window \citep{Thyagarajan:2015b, Thyagarajan:2015, Pober:2016}. In principle we 
 can repeat the model building described above using additional MWA observations pointed 
@@
 within the primary field of view of the MWA. Though the EoR0 field was chosen to be 
-relatively devoid of galactic emission, we find this diffuse structure still highly contaminating 
+relatively devoid of Galactic emission, we find this diffuse structure still highly contaminating 
 due to the very high sensitivity of the MWA at large scales. For computational purposes we 
-have divided the galactic emission into two regimes -- the faint clouds in our main lobe, and 
+have divided the Galactic emission into two regimes -- the faint clouds in our main lobe, and 
 the bright plane and other structures in the sidelobes. While the latter has been studied by 
@@
 model. By forcing our model to contain no spectral structure we mitigate the risk of 
-subtracting cosmological signal. Future iterations of this model will contain a spectral index 
+subtracting cosmological signal.
+
+Future iterations of this model will contain a spectral index 
 and multiple polarization components.
+Lenc, et al. (in review) demonstrated the presence of strong polarized large-scale structures 
+in the EoR0 field at 154 MHz with varying Faraday depths. They observed rotations in the
+Stokes Q--U plane due to ionospheric conditions, which will need to be taken into account
+in our future diffuse models.
 
@@
 smoothed to degree scales to emphasize the large scale structure and approximate an 
-MWA snapshot natural weighting. The color scale is in units of Jy/str.
+MWA snapshot natural weighting.
 \label{fig:diffuse}
@@
 \begin{center}
-\subfigure{\includegraphics[width=.9\columnwidth]{diffuse_diff_model.pdf}}
+\subfigure{\includegraphics[width=\columnwidth]{diffuse_diff_model.pdf}}
 ~
-\subfigure{\includegraphics[width=.9\columnwidth]{diffuse_diff_residual.pdf}}
+\subfigure{\includegraphics[width=\columnwidth]{diffuse_diff_residual.pdf}}
 \caption{
@@
 This numbering scheme is shown graphically in Figure~\ref{fig:pointing}.
-Early in the night ($-5$ through $-3$) the bulk of the galactic plane 
+Early in the night ($-5$ through $-3$) the bulk of the Galactic plane 
 was still above the horizon, and despite being very far from our primary field of view, highly 
 contaminated our observations through the sidelobes of the instrument. We then have 
-relatively well behaved pointings, with the EoR window dominated by noise, until the final 
-pointing of the night when we can see evidence of the galaxy rising again indicated by 
+relatively well-behaved pointings, with the EoR window dominated by noise, until the final 
+pointing of the night when we can see evidence of the Galaxy rising again indicated by 
 strong lines of power at the edge of the foreground wedge. We saw the same contamination 
 on all days of observation and decided to cut all $-5$, $-4$, $-3$, and $+4$ pointings from 
-our data set. In principle it may be possible to model the galactic disk well enough to 
-account for its presence, but with a lack of sufficient galactic model, beam model, and the 
+our data set. In principle it may be possible to model the Galactic disk well enough to 
+account for its presence, but with a lack of sufficient Galactic model, beam model, and the 
 analysis tools to include it, we leave this to future work.
@@
 polarization) for a single day, August 26, 2013. The early pointings are heavily contaminated 
-by the galaxy in the sidelobes, the window becomes more clear near zenith, and we can 
-see trace contamination at the end of the night (pointing +4) when the galaxy has risen 
+by the Galaxy in the sidelobes, the window becomes more clear near zenith, and we can 
+see trace contamination at the end of the night (pointing +4) when the Galaxy has risen 
 again.
@@
 calibration. This is encouraging because future analysis could use this metric before 
-processing the snapshots, saving valuable computing resources.
+processing the snapshots, saving valuable computing resources\footnote{Because
+calibration involves generating model visibilities for each snapshot, approximately half
+the computational cost of the entire imaging pipeline is required to obtain 
+calibration solutions.}.
 
@@
 generally flat, with the exception of some outliers and almost all of pointing $+3$. We 
-suspect that the excess N-S power in the later pointing is due to the galaxy leaking back 
+suspect that the excess N-S power in the later pointing is due to the Galaxy leaking back 
 into the sidelobe of the N-S polarization, but not in the other. Again, we make the cut shown 
@@
 a clean data set. As mentioned earlier, more sophisticated analysis could allow us to 
-recover data cut from this study in the future (e.g. modeling and removing the galaxy in 
+recover data cut from this study in the future (e.g. modeling and removing the Galaxy in 
 observations pointing far off zenith).
@@
 exceptionally bright foregrounds at large scales. On the high end we are seeing the residual
-of the vertical streaks due to poor sampling at large $uv$. While the increased noise would
+of the vertical streaks due to poor sampling at large $(u,v)$. While the increased noise would
 mean that we will down weight the bins at large $k_{\perp}$, the contamination is even
@@
 investigation, but improved spectral dependence in both the point source catalog and the 
-diffuse model, as well as the addition of an all-sky galactic model, will continue to improve 
+diffuse model, as well as the addition of an all-sky Galactic model, will continue to improve 
 the foreground subtraction and further unlock the EoR window.

### 2016-06-13 ms.tex
Fixed small typesetting bug in abstract

@@
 integration of 32 hours of MWA data. This data set is used to place a systematic-limited 
-upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ mK
-$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
+upper limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ 
+mK$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
 modest improvement (factor of 1.4) over previous MWA results. While our result is 

### 2016-06-27 ms.tex
spacing
BMG comment

@@
 due to the very high sensitivity of the MWA at large scales. For computational purposes we 
-have divided the Galactic emission into two regimes -- the faint clouds in our main lobe, and 
+have divided the diffuse emission into two regimes -- the faint clouds in our main lobe, and 
 the bright plane and other structures in the sidelobes. While the latter has been studied by 
@@
 The RTS uses a fundamentally different calibration and foreground subtraction approach than 
-FHD, as well as a different input point source model. The primary differences lie in the 
+FHD, as well as a different input point source model. 
+The primary differences lie in the 
 bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
@@
 data \citep{Jacobs:2016}.
+
 The CHIPS power 

### 2016-06-27 ms.tex
NT comments

@@
 A.~R.~Neben\affils{MIT},
-N.~Thyagarajan\affils{ASU},
+Nithyanandan~Thyagarajan\affils{ASU},
 D.~Oberoi\affils{Tata}, 
@@
 \citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2012, Liu:2014a, Liu:2014b, 
-Hazelton:2013, Pober:2013, Vedantham:2012, Morales:2012, Datta:2010}. Despite this 
+Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}. Despite this 
 setback, the EoR window is preserved above the wedge, and the field is pushing forward with 
@@
 $k_{||}$ transform. This has the effect of trading off lower effective bandwidth for higher 
-dynamic range.
+dynamic range \citep[e.g.][]{Thyagarajan:2016, Thyagarajan:2013}.
 
@@
 better accounts for the instrumental response, perhaps by increasing signal to noise 
-through multiple-snapshot solutions or refined antenna response models. Studies of the 
+through multiple-snapshot solutions or refined antenna response models. 
+Through simulation, \citealt{Thyagarajan:2016} recently demonstrated the necessity of
+ precise foregrounds and instrumental models in order to retain a clean EoR window.
+Studies of the 
 beam are underway \citep[e.g.][]{Neben:2015}, and will likely help to further isolate the 

### 2016-06-27 ms.tex
BJH comments. Have question out to Mahsa re: peeling bug. Will update fig. 13 with MFM comments

@@
 behaved point spread function while retaining a dense core for EoR sensitivity 
-\citep{Beardsley:2013}. This is in contrast to more pointed EoR experiments like PAPER, 
+\citep{Beardsley:2013}. 
+A full description of the science capabilities of the array is found in
+\citealt{Bowman:2013}.
+The high imaging capability of the MWA enables us to calibrate and subtract foregrounds
+based on sky models, leveraging the full capability of the observatory for the
+EoR experiment. 
+This strategy is in contrast to more pointed EoR experiments like PAPER, 
 which utilize a highly redundant layout to enhance sensitivity. Redundant arrays can 
-leverage symmetries of the instrument for quick calibration and analysis, but have poor 
-point spread functions, making foregrounds more difficult to characterize. Conversely we 
-use the high imaging capability of the MWA to calibrate and subtract foregrounds based on 
-sky models. A full description of the science capabilities of the array is found in 
-\citealt{Bowman:2013}.
+exploit symmetries of the instrument for quick calibration and analysis, but have poor 
+point spread functions, making foregrounds more difficult to characterize.
 
@@
 Our final data cut was made when inspecting the residual continuum images output from 
-FHD. We calculate a fractional residual flux RMS in the following way. For each snapshot 
+FHD. We test for residual flux at source locations by calculating a fractional residual flux RMS 
+in the following way. For each snapshot 
 continuum image, we find the residual flux in the pixels of all sources greater than 0.5 Jy 
@@
 $k_{\perp}$ (solid) and $k_{||}$ (dashed). \emph{Top right:} Residual power as a function
-of $k_{\perp}$ for fixed $k_{||}$. The grey boxes show regions which will be excluded from
-the one dimensional averages. The red dashed line shows the 1-$\sigma$ noise level, and
+of $k_{\perp}$ for fixed $k_{||}$, averaged in rings from the full 3D power cube (blue). The grey boxes show regions which will be excluded from
+the one dimensional averages. The red line shows the 1-$\sigma$ noise level, and
 the vertical black dashed line shows the intersection of this slice with the wedge. 
-\emph{Bottom right:} Residual power as a function of $k_{||}$ for fixed $k_{\perp}$. The strong
+\emph{Bottom right:} Residual power as a function of $k_{||}$ for fixed $k_{\perp}$, again averaged in rings from full 3D power cube (blue). The strong
 foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
@@
 While the MWA analysis is not yet at that level of maturity, there is room for rapid 
-improvement. The dashed red line in Figure~\ref{fig:1d_ps} indicate the noise level possible 
+improvement. The red lines in Figure~\ref{fig:1d_ps} indicate the noise level possible 
 to reach with this data set if systematics can be overcome.

### 2016-06-27 ms.tex
New acknowledgement section per DLKs email

@@
 under award AST-1401708.
-This scientific work makes use of the Murchison Radio-astronomy 
-Observatory, operated by CSIRO. We acknowledge the Wajarri Yamatji people as the 
-traditional owners of the Observatory site. Support for the MWA comes from the U.S. 
-National Science Foundation (grants AST-0457585, PHY-0835713, CAREER-0847753, and 
-AST-0908884), the Australian Research Council (LIEF grants LE0775621 and LE0882938), 
-the U.S. Air Force Office of Scientific Research (grant FA9550-0510247), and the Centre for 
-All-sky Astrophysics (an Australian Research Council Centre of Excellence funded by grant 
-CE110001020). Support is also provided by the Smithsonian Astrophysical Observatory, the 
-MIT School of Science, the Raman Research Institute, the Australian National University, 
-and the Victoria University of Wellington (via grant MED-E1799 from the New Zealand 
-Ministry of Economic Development and an IBM Shared University Research Grant). The 
-Australian Federal government provides additional support via the Commonwealth Scientific 
-and Industrial Research Organisation (CSIRO), National Collaborative Research 
-Infrastructure Strategy, Education Investment Fund, and the Australia India Strategic 
-Research Fund, and Astronomy Australia Limited, under contract to Curtin University. We 
-acknowledge the iVEC Petabyte Data Store, the Initiative in Innovative Computing and the 
-CUDA Center for Excellence sponsored by NVIDIA at Harvard University, and the 
-International Centre for Radio Astronomy Research (ICRAR), a Joint Venture of Curtin 
-University and The University of Western Australia, funded by the Western Australian State 
-government.
+This scientific work makes use of the Murchison Radio-astronomy Observatory, operated by 
+CSIRO. We acknowledge the Wajarri Yamatji people as the traditional owners of the 
+Observatory site. Support for the operation of the MWA is provided by the Australian 
+Government (NCRIS), under a contract to Curtin University administered by Astronomy 
+Australia Limited. We acknowledge the Pawsey Supercomputing Centre which is supported 
+by the Western Australian and Australian Governments.
 

### 2016-06-27 ms.tex
MFM comments. Have question out to Masha re: peeling bug.

@@
 21cm EoR machines is on its way with the Hydrogen Epoch of Reionization Array (HERA
-\footnote{http://reionization.org}, D.~R.~DeBoer, et al. 2016, in prep), which will further 
+\footnote{http://reionization.org}, \citealt{DeBoer:2016}), which will further 
 refine the power spectrum measurement in early build-out stages, but will ultimately be 
@@
 behaved point spread function while retaining a dense core for EoR sensitivity 
-\citep{Beardsley:2013}. 
+\citep{Beardsley:2013}.\footnote{A drone flyover view of the array layout is available on YouTube at \url{https://youtu.be/yDWdTUzTUMo}.}
 A full description of the science capabilities of the array is found in
@@
 the field, which digitize the signal and perform a first stage coarse frequency 
-channelization of the data (1.28 MHz coarse bands)\citep{Prabu:2015}. This channelization 
-applies a filter shape and aliases edge channels, which will later be flagged in our analysis. 
+channelization of the data (1.28 MHz coarse bands; \citealt{Prabu:2015}). This step 
+applies a filter shape and aliases channels on the edge of the coarse bands, which will later be flagged in our analysis. 
 The observer now selects 24 coarse bands (30.72 MHz total bandwidth) to pass onto the 
@@
 Besides RFI, we manually flag data to remove three other effects. As mentioned in 
-Section~\ref{sec:MWA}, the edges of the coarse bands contain high levels of aliasing from 
+Section~\ref{sec:MWA}, the edges of the coarse bands contain aliasing from 
 the filter applied in the digital receivers. We flag two 40 kHz channels on either side of the 
@@
 a frequency resolution of 160 kHz.
+
+The data are gridded into separate cubes for even/odd interleaved time samples. 
+The sum of the even and odd cubes contains power from the sky as well as noise,
+while the difference between the two contains only noise power. Subtracting the power
+spectrum of the difference from that of the sum yields an unbiased estimate of the sky power
+\citep{Jacobs:2016}.
 
@@
 \emph{Top:} Single polarization dirty power spectrum formed from the golden data set, 
-before implementing cable reflection fitting into the calibration loop. The black arrow points 
+before implementing cable reflection fitting into the calibration loop. 
+The small gray arrows point to the bands resulting from the periodic coarse band sampling.
+The black arrow points 
 to a horizontal band at $k_{||} \approx 0.7$~h~Mpc$^{-1}$, which cannot be accounted for 
@@
 and efficiency, the kernel is pre-calculated at a high resolution, then a nearest neighbor 
-lookup table is used to approximate the beam values at discrete pixels. The kernel 
+lookup table is used to approximate the beam values at discrete pixels. 
+This is a common practice in most analysis software packages.
+The kernel 
 resolution used in the top panel of Figure~\ref{fig:beam_res} was 0.04 wavelengths -- much 
@@
 primary beam will not be sufficient to suppress the power spectrum wedge and unlock the 
-EoR window \citep{Thyagarajan:2015b, Thyagarajan:2015, Pober:2016}. In principle we 
-can repeat the model building described above using additional MWA observations pointed 
-away from our field of interest. But until that work is complete we supplement the extent of 
+EoR window \citep{Thyagarajan:2015b, Thyagarajan:2015, Pober:2016}. 
+We are in the process of repeating the model building described above using additional
+MWA observations pointed away from our field of interest.
+Until that work is complete we supplement the extent of 
 our point source model using additional catalogs. We accomplish this through a hierarchical 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{master_catalog.png}
+\includegraphics[width=\textwidth]{master_catalog.pdf}
 \caption{
 Hierarchical catalog used for foreground subtraction. This catalog combines the source lists 
-from our own FHD catalog, the MWACS catalog, Culgoora sources, and the MRC, 
-prioritizing in that order. The EoR0 field corresponds to the red FHD patch, while we use the 
+from the KGS catalog, the MWACS catalog, Culgoora sources, and the MRC, 
+prioritizing in that order. The EoR0 field corresponds to the red KGS patch, while we use the 
 other catalogs to fill in the sidelobes of the MWA. The size of each dot is proportional to the 
@@
 The resulting hierarchical catalog is shown in Figure~\ref{fig:master_catalog}. The EoR0 
-field corresponds to the red FHD source patch. All sources above the horizon and within a 
+field corresponds to the red KGS source patch. All sources above the horizon and within a 
 primary beam value greater than 1\% maximum (including sidelobes) are included in both 
@@
 
+Another potential cause of the foreground leakage into the EoR window is insufficient
+calibration quality -- particularly the spectral shape of the instrumental bandpass.
+Investigations are underway to combine snapshot observations for higher signal-to-noise
+calibration solutions, as well as more sophisticated parameterization of the gain model in
+Equation~\ref{eq:cal2} to account for more physical effects such as dependence on
+ambient temperature variation.
+
 Moving up in the window, between the first two coarse band harmonic lines we can see an 
@@
 vertical dashed line to show the slice used to plot power as a function of $k_{||}$ for a fixed 
-$k_{\perp}$ (bottom right). In the $k_{\perp}$ power plot we can see leakage at low and high
-$k_{\perp}$. On the low end this is due to the width of the coarse band harmonics and the
-exceptionally bright foregrounds at large scales. On the high end we are seeing the residual
-of the vertical streaks due to poor sampling at large $(u,v)$. While the increased noise would
+$k_{\perp}$ (bottom right). 
+In the $k_{\perp}$ power plot we can see leakage at high $k_{\perp}$ from the residual of the 
+vertical streaks due to poor sampling at large $(u,v)$. While the increased noise would
 mean that we will down weight the bins at large $k_{\perp}$, the contamination is even
 larger, meaning it would bias our estimate even though those bins are down weighted.
-We exclude bins with $u<10\lambda$ and $u>70\lambda$, shown with grey boxes.
+The low end of $k_{\perp}$ contains exceptionally bright foregrounds at large scales, which,
+due to the width of the coarse band harmonics, contaminate most of the $k_{||}$ modes. 
+With both these regimes in consideration, 
+we exclude bins with $u<10\lambda$ and $u>70\lambda$, shown with gray boxes.
 Between these two regimes are many bins consistent with the noise level, which we include
@@
 $k_{\perp}$ (solid) and $k_{||}$ (dashed). \emph{Top right:} Residual power as a function
-of $k_{\perp}$ for fixed $k_{||}$, averaged in rings from the full 3D power cube (blue). The grey boxes show regions which will be excluded from
+of $k_{\perp}$ for fixed $k_{||}$, averaged in rings from the full 3D power cube (blue). The gray boxes show regions which will be excluded from
 the one dimensional averages. The red line shows the 1-$\sigma$ noise level, and
@@
 foreground contamination is evident at low $k_{||}$, and the coarse band harmonic lines
-appear as expected. The thin black line in both right panels is the equivalent power slice from the RTS$+$CHIPS comparison pipeline, which is discussed in Section~\ref{subsec:ref_pipe}.
+appear as expected. The thin gray line in both right panels is the equivalent power slice from the RTS$+$CHIPS comparison pipeline, which is discussed in Section~\ref{subsec:ref_pipe}.
 \label{fig:slices}
@@
 Here we compare the upper limits from the FHD$+$\eppsilon pipeline with those from the 
-RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure~\ref{fig:1d_ps}, and the blue line
-is the power plus two sigma thermal error bars line generated by CHIPS. CHIPS does not 
+RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure~\ref{fig:1d_ps}, and the gray lines
+are the power plus two sigma thermal error bars lines generated by CHIPS. 
+Due to the logarithmic binning used by CHIPS, some bins are empty, resulting in gaps in the
+spectra.
+CHIPS does not 
 excise the coarse band harmonic lines, and so we see their strong effect where there are 
@@
 overcome, it has the potential to quickly compete with other more pointed experiments and 
-analysis styles. Here we have identified a crucial region of power spectrum space that is 
+analysis styles. 
+More broadly, imaging analyses will be necessary to perform cross-correlation studies
+with complimentary probes such as galaxy surveys or other intensity mapping experiments
+ \citep[e.g.][]{DeBoer:2016, Vrbanec:2016, Beardsley:2015, Silva:2015, Dore:2014, Lidz:2009}.
+Here we have identified a crucial region of power spectrum space that is 
 currently contaminated, with suggestions for improvement in future analysis. With improved 

### 2016-06-27 ms.tex
JCP comments

@@
 systematic contamination to reduce the data to a cosmological measurement. We introduce 
-several novel analysis techniques such as cable reflection calibration, high resolution 
+several novel analysis techniques such as cable reflection calibration, hyper-resolution 
 gridding kernels, diffuse foreground model subtraction, and quality control methods. Each 
@@
 relationship between observed frequency and line-of-sight distance, it can be used to map 
-the full three dimensional space of the epoch. (For reviews, see \citealt{Furlanetto:2006} 
-and \citealt{Morales:2010}.) The first generation of instruments with primary science goals 
+the full three dimensional space of the epoch. (For reviews, see \citealt{Furlanetto:2006}, 
+\citealt{Morales:2010}, \citealt{Zaroubi:2013}, and \citealt{Pritchard:2012}) The first generation of instruments with primary science goals 
 to detect the 21cm EoR signal have been built, including the GMRT (Giant Metrewave 
 Radio Telescope, \citealt{Paciga:2013}), LOFAR (LOw Frequency Array\footnote{http://
-www.lofar.org}, \citealt{Yatawatta:2013}), PAPER (Precision Array for Probing the Epoch of 
+www.lofar.org}, \citealt{vanHaarlem:2013, Yatawatta:2013}), PAPER (Precision Array for Probing the Epoch of 
 Reionization\footnote{http://eor.berkeley.edu}, \citealt{Parsons:2010}), and the MWA 
-(Murchison Widefield Array\footnote{http://www.mwatelescope.org}, \citealt{Tingay:2013}). 
+(Murchison Widefield Array\footnote{http://www.mwatelescope.org}, \citealt{Tingay:2013, Bowman:2013}). 
 Due to relatively low signal to noise, these instruments aim for a statistical measurement of 
@@
 This paper serves two purposes: to demonstrate several new analysis techniques and their 
-impact on power spectrum estimation, and to present the first attempt at a deep integration 
+impact on power spectrum estimation, and to present the first deep integration 
 power spectrum from the MWA. Using a three hour test set of data, we introduce several 
@@
 describe several novel techniques in our analysis, in Section~\ref{sec:deep} we discuss our 
-efforts to apply the analysis pipeline to a deep data integration and compare with a reference pipeline for robust estimation, and we discuss future work 
+efforts to apply the analysis pipeline to a deep data integration and compare with an alternative analysis pipeline for robust estimation, and we discuss future work 
 in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM 
@@
 EoR experiment. 
-This strategy is in contrast to more pointed EoR experiments like PAPER, 
+This strategy is in contrast to more targeted EoR experiments like PAPER, 
 which utilize a highly redundant layout to enhance sensitivity. Redundant arrays can 
@@
 
-The data for this work includes two sets. First we use a set of 94 high band observations of 
+The data for this work includes two sets. First we use a set of 94 two-minute high band observations of 
 the EoR0 field from August 23, 2013, which were taken early in telescope operations and 
@@
 as a ``golden data set'', which is used to build analysis tools and compare early results. All 
-techniques demonstrated here will use this golden data set. In Section~\ref{sec:deep} we 
+techniques demonstrated here will use this golden data set \cite[e.g.][]{Jacobs:2016, Trott:2016, Pober:2016, Dillon:2015}. In Section~\ref{sec:deep} we 
 will use a larger data set to move toward a deep integration. This data set consists of all 
@@
 direction-dependence of the antenna response into the model of the primary beam. FHD is capable 
-of using separate models for each antenna, though this has not yet been implemented for 
-the MWA due to lack of individual models. The second simplification is to ignore any cross 
+of using separate models for each antenna, though this has not been implemented in this 
+work. The second simplification is to ignore any cross 
 terms between our different axes, for example a mutual coupling between two antennas. In 
@@
 selecting the mode where the reflection amplitude is largest. 
+This fitting produces a single reflection coefficient for each antenna with nominal cable
+length of 150 meters.
 
@@
 wavelengths was sufficient. The resulting model power spectrum is shown in the bottom 
-panel of Figure~\ref{fig:beam_res}. The contamination within the EoR window now drops 
-significantly below the predicted cosmological signal levels. This improvement in beam
+panel of Figure~\ref{fig:beam_res}. 
+The contamination within the EoR window now drops significantly lower. Of course, without
+knowing the exact level of the cosmological signal, we cannot know if this level is sufficiently 
+low. This effect may need to be revisited if the EoR power spectrum is lower than 
+predicted.
+The improvement in beam
 model resolution came at the cost of 20\% increase in memory usage for our imaging
@@
 \emph{Top:} Window power for each observation in our data set. The window power is 
-calculated from the delay spectrum of uncalibrated data as a fast quality metric. Each color 
+calculated from the delay spectrum of uncalibrated data as a fast quality metric. 
+Because uncalibrated data is used, the units are arbitrary.
+Each color 
 is a distinct day of observing, and the vertical dashed lines represent pointing shifts, with 
@@
 of cosmic evolution over the span of our measured redshift range, we limit observations to 
-about 8 MHz, or $\Delta z \sim 0.4$ at our frequency. We do this by dividing the band into 
+about 8 MHz, or $\Delta z \sim 0.3$ at our frequency. We do this by dividing the band into 
 three overlapping sub-bands of 15.36 MHz each, which, after applying the Blackman-Harris 
@@
 necessary to completely mask out the wedge, consistent with \citealt{Dillon:2015}. We
-implement the buffer by extending the horizon line by 15 degrees. This line is shown as the
+implement the buffer by increasing the slope of the horizon line by 14\%.
+This line is shown as the
 dashed diagonal line in the left panel of Figure~\ref{fig:slices}.
@@
 gaps in the magenta lines. The most notable differences are the ability of the RTS$+$CHIPS pipe
-to access lower $k$ modes, while the FHD$+$\eppsilon pipe suppresses moe power before and
+to access lower $k$ modes, while the FHD$+$\eppsilon pipe suppresses more power before and
 after the first coarse band harmonic. While the different analysis methods result in slightly

### 2016-06-29 ms.tex
SJT comments

@@
 mK$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$, consistent with other published limits, and a 
-modest improvement (factor of 1.4) over previous MWA results. While our result is 
-systematic limited, we identify several strategies to overcome these systematics in future 
-analysis.
+modest improvement (factor of 1.4) over previous MWA results. 
+From this deep analysis we have identified a list of improvements to be made to our EoR
+data analysis strategies. These improvements will be implemented in the future and detailed
+in upcoming publications.
 \end{abstract}
@@
 
-Several probes are being used to investigate the EoR, but to date, a direct detection eludes 
-researchers. Studies of the polarization of the CMB have placed integrated constraints on 
+Several probes are being used to investigate the EoR. 
+Studies of the polarization of the CMB have placed integrated constraints on 
 the timing of reionization \citep[e.g.][]{Planck:2015b, Planck:2015, WMAP9}. Meanwhile, 
@@
 \citealt{Morales:2010}, \citealt{Zaroubi:2013}, and \citealt{Pritchard:2012}) The first generation of instruments with primary science goals 
-to detect the 21cm EoR signal have been built, including the GMRT (Giant Metrewave 
+to detect the highly redshift 21cm signal have been built, including the GMRT (Giant Metrewave 
 Radio Telescope, \citealt{Paciga:2013}), LOFAR (LOw Frequency Array\footnote{http://
@@
 21cm EoR machines is on its way with the Hydrogen Epoch of Reionization Array (HERA
-\footnote{http://reionization.org}, \citealt{DeBoer:2016}), which will further 
+\footnote{http://reionization.org}, \citealt{DeBoer:2016}), 
+and the low frequency Square Kilometer Array (SKA1-Low \citealt{Mellema:2013}),
+which will further 
 refine the power spectrum measurement in early build-out stages, but will ultimately be 
@@
 \citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2012, Liu:2014a, Liu:2014b, 
-Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}. Despite this 
-setback, the EoR window is preserved above the wedge, and the field is pushing forward with 
-several analysis pipelines under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
+Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}. Nevertheless, 
+the EoR window is preserved above the wedge, and 
+several analysis pipelines are under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
 prep; D.~A.~Mitchell et al. 2016, in prep; ][]{Jacobs:2016, Trott:2016, 
@@
 techniques to a deep integration of data from the first semester of MWA observations 
-(August, 2013 -- November, 2013) on a single EoR field and redshift range, $6.2<z<7.5$. 
-While not expecting to detect the EoR with less than a hundred hours of observations, this 
+(August, 2013 -- November, 2013), with a total of 32 hours on a single EoR field and redshift range, $6.2<z<7.5$.
+
+Our best result is a limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ 
+mK$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$. This is lower than the GMRT 40 hour
+limit ($\Delta^2 \le 6.15 \times 10^4$ mK$^2$ at $z=8.6$; \citealt{Paciga:2013}), but 
+signficantly higher than the latest PAPER result which 
+integrated nearly 1,000 hours ($\Delta^2 \le 502$ mK$^2$ at $z=8.4$; \citealt{Ali:2015}).
+Several EoR experiments are reaching sensitivity levels where very low systematics
+become dominant. The PAPER team saw evidence that antenna cross-talk and foreground
+leakage was limiting their result at several scales. The LOFAR team has seen excess noise
+and diffuse foreground suppression due to calibration \citep{Patil:2016}. It is essential
+for EoR experiments to understand and overcome these systematics in order to reach
+a cosmological detection.
+
+While not expecting to detect the EoR with less than a hundred hours of observations, our 
 intermediate integration will serve to identify and diagnose systematics, allowing for 
-improved analysis in future work.
+improved analysis in future work. We list several directions to improve our modeling of
+foregrounds and the instrumental response, which in turn will improve our calibration
+and foreground subtraction. Our strategy to perform periodic deep integrations allows us
+to continue uncovering systematics, refine algorithms and data analysis, and understand
+the subtleties of the instrument to execute this challenging experiment.
 
@@
 efforts to apply the analysis pipeline to a deep data integration and compare with an alternative analysis pipeline for robust estimation, and we discuss future work 
-in Section~\ref{sec:discussion}. Throughout this paper we use a $\Lambda$CDM 
+in Section~\ref{sec:discussion}, including a summary of planned improvements
+to the analysis. Throughout this paper we use a $\Lambda$CDM 
 cosmology with $\Omega_m=0.73$, $\Omega_\Lambda=0.27$, and $h = 0.7$, consistent 
@@
 a primary science goal of detecting the 21cm EoR power spectrum. The remote Australian 
-outback offers relative isolation from man-made radio frequency interference (RFI) such as 
+outback offers relative isolation from human-made radio frequency interference (RFI) such as 
 FM radio, or TV stations. A recent study of the RFI environment at the Murchison Radio 
@@
 reducing the number of free parameters in this step we increase our signal to noise on 
-calibration solutions and avoid absorbing unmodeled confusion source flux into our gain 
+calibration solutions and avoid absorbing unmodeled confusion source flux density into our gain 
 solutions which has been shown to contaminate the EoR window \citep{Barry:2016}. 
+Recently, \citealt{Patil:2016} demonstrated excess noise and a suppression of diffuse
+foregrounds in LOFAR images after calibration and subtraction of bright discrete
+foreground sources. They suggested a multi-frequency calibration solution as a potential
+solution to these systematics, similar to the scheme implemented here. Indeed we have
+not seen evidence of these systematics through simulations and direct propagation of
+our noise \citep[Hazelton et al. 2016, in prep.]{Barry:2016}.
 
@@
 expected EoR signal, we apply a Blackman-Harris window function prior to the $r_{||}$ to 
-$k_{||}$ transform. This has the effect of trading off lower effective bandwidth for higher 
+$k_{||}$ transform. This has the effect of trading lower effective bandwidth for higher 
 dynamic range \citep[e.g.][]{Thyagarajan:2016, Thyagarajan:2013}.
@@
 {Hurley-Walker:2014}, the Culgoora catalog \citep{Slee:1977}, and the Molonglo Reference Catalog 
-\citep[MRC, ][]{Large:1981}. Source fluxes are prioritized in this order based on our 
-confidence in their predicted flux at 182 MHz. We first cluster the source lists to avoid 
-redundant sources, using a 3.5 arcmin neighborhood radius, then select the flux from the 
+\citep[MRC, ][]{Large:1981}. Source flux densities are prioritized in this order based on our 
+confidence in their predicted flux density at 182 MHz. We first cluster the source lists to avoid 
+redundant sources, using a 3.5 arcmin neighborhood radius, then select the flux density from the 
 highest priority catalog. Spectral indices were obtained from the MWACS and Culgoora 
@@
 MRC matches or MRC-SUMSS matches. All other sources were given a spectral index of 
-$-0.8$. The spectral index was used to extrapolate the flux from the catalog frequency to 
+$-0.8$. The spectral index was used to extrapolate the flux density from the catalog frequency to 
 182 MHz, but a uniform spectral index of $-0.8$ is used within our band when forming 
@@
 other catalogs to fill in the sidelobes of the MWA. The size of each dot is proportional to the 
-182~MHz flux of the source, clipped at 20~Jy.
+182~MHz flux density of the source, clipped at 20~Jy.
 \label{fig:master_catalog}
@@
 images is done in a uniformly weighted frame to minimize the effect of double instrument 
-convolution (once when the data is taken, again when we use the output as a model). We 
+convolution (once when the data are taken, again when we use the output as a model). We 
 then form a pseudo Stokes I image by adding beam-weighted East-West and North-South 
@@
 for each independent observation. FHD treats each pixel in the image as a point source at 
-the pixel location with total flux equal to the flux density of the diffuse image times the area 
+the pixel location with total flux density equal to the surface brightness of the diffuse image times the area 
 of the pixel and creates model visibilities for each snapshot in the same way that it imports 
@@
 subtraction in Figure~\ref{fig:diffuse_diff}. The top panel shows the model power with the 
-diffuse subtracted from the model power without. The entire plot is negative (red) because 
-we only added power with the diffuse model. 
+diffuse subtracted from the model power without. 
+Because our diffuse model added power to the full foreground model, the entire plot is
+negative (red).
 Even the EoR window is red (albeit at a much lower level than the wedge) because of power
@@
 
-We use the jackknife method -- dividing the data into many subgroups -- to filter out bad 
-data and detect patterns. A powerful grouping is to divide the data into the observation day 
+We use the jackknife method to filter out bad data and detect patterns. This involves dividing
+the data into many subgroups and forming power spectra. The goal is to find observational
+parameters which affect the quality of the data, such as the day or time of night.
+A powerful grouping is to divide the data into the observation day 
 and ``pointing" (which direction the antennas were pointed while tracking the EoR0 field). 
@@
 Our final data cut was made when inspecting the residual continuum images output from 
-FHD. We test for residual flux at source locations by calculating a fractional residual flux RMS 
+FHD. We test for residual brightness at source locations by calculating a fractional residual brightness RMS 
 in the following way. For each snapshot 
-continuum image, we find the residual flux in the pixels of all sources greater than 0.5 Jy 
-subtracted within half-beam power and scale by the integrated flux of the sources. This 
-gives us a list of fractional residual fluxes for the snapshot, which we then use to calculate 
-an RMS. We found that most snapshots had residual flux RMS $<10\%$ with some outliers, 
+continuum image, we find the residual brightness in the pixels of all sources greater than 0.5 Jy 
+subtracted within half-beam power and scale by the integrated flux density of the sources. This 
+gives us a list of fractional residual brightnesses for the snapshot, which we then use to calculate 
+an RMS. We found that most snapshots had residual brightness RMS $<10\%$ with some outliers, 
 which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
-additional 95 observations. The cause of the high residual flux RMS is yet unknown and is 
+additional 95 observations. The cause of the high residual brightness RMS is yet unknown and is 
 not localized by observation day, LST, pointing, or any other jackknife we have performed.
@@
 data. This is an aggressive cut, with the aim of removing all poor quality data and retaining 
-a clean data set. As mentioned earlier, more sophisticated analysis could allow us to 
+a data set as clean as we can determine from our data quality checks. As mentioned earlier, more sophisticated analysis could allow us to 
 recover data cut from this study in the future (e.g. modeling and removing the Galaxy in 
@@
 features can be seen in these spectra. In all cases the foreground wedge is prominent, with 
-extra power at large scales (low $k_{\perp}$). This is indication that our diffuse model can 
+extra power at large scales (low $k_{\perp}$). This is an indication that our diffuse model can 
 improve for deeper subtraction.
@@
 has a strong signal to noise on the power spectrum. Our results are also consistent with the 
-GMRT limit of $\Delta^2\le6.15\times10^4$~mK$^2$ at $z=8.6$ \citep{Paciga:2013}, though 
+40 hour GMRT limit of $\Delta^2\le6.15\times10^4$~mK$^2$ at $k=0.5\, h$~Mpc$^{-1}$ and $z=8.6$ \citep{Paciga:2013}, though 
 probe significantly different periods of the EoR. The frontrunner in terms of an upper limit is 
 the PAPER experiment \citep{Ali:2015, Jacobs:2015, Parsons:2014}. The PAPER-64 limit of 
-$\Delta^2\le502$~mK$^2$ at $z=8.4$ is about one and a half orders of magnitude lower 
+$\Delta^2\le502$~mK$^2$ at $z=8.4$ from a 135 day observing campaign is about one and a half orders of magnitude lower 
 than our best limit in power units, though again probing a significantly different redshift. 
@@
 improvement. The red lines in Figure~\ref{fig:1d_ps} indicate the noise level possible 
-to reach with this data set if systematics can be overcome.
-
-While this analysis has not reached full potential, it represents the deepest power spectrum 
+to reach with these data if systematics can be overcome.
+
+\subsection{Summary of planned analysis improvements}
+Through the reduction of the first season of MWA high band EoR observations, we have
+identified several opportunities to improve our analysis. Here we compile a list of future
+improvements and their potential impact on the power spectrum results. Broadly speaking,
+these improvements emphasize a need to better understand the foregrounds and the 
+instrument, and are likely to be relevant to imaging based analyses in general.
+
+\textbf{Extended point source model.} The hierarchical catalog used here was a definite
+improvement over the MWACS catalog alone. This point source model will continue
+to improve with the release of the GLEAM Survey, as well as dedicated MWA observations 
+to target sources in the sidelobes of the EoR fields. Improving the foreground catalog
+in our sidelobes will be crucial in controlling the foreground leakage into the EoR window
+\citep{Pober:2016}. Incorporating these improved catalogs
+into our analysis will improve both the foreground subtraction and the calibration.
+
+\textbf{Diffuse emission model.} The diffuse model here contained no spectral information
+and represented only the Stokes I polarization. Nevertheless subtracting this model removed
+90\% of the residual power in the foreground wedge. Adding a spectral index and multiple
+polarization components to the model will improve this subtraction even further.
+As Lenc, et al. 2016 (in review) demonstrated, substantial polarized diffuse structure
+exists in the EoR0 field. The contributions to Stokes Q and U depend on the ionospheric
+conditions, which will be accounted for in future analyses to appropriately model this
+emission. 
+In addition the diffuse model will be extended to an all-sky model. It is evident from the
+jackknives shown in Figure~\ref{fig:jackknife} that strong emission near the horizon is
+leaking into our power spectra during off-zenith observations. By modeling and subtracting
+this emission we may be able to recover these observations in future analyses.
+
+\textbf{Primary beam model.} In order to properly model the instrument response to the sky
+we also need an accurate primary beam model. This is especially important for EoR
+power spectrum measurements because the (often bright) near-horizon emission resides
+at the edge of the foreground wedge 
+\citep{Pober:2016, Thyagarajan:2015, Thyagarajan:2015b}, but the low elevation beam
+can be difficult to model at the necessary precision \citep{Thyagarajan:2016}. 
+\citealt{Asad:2016} demonstrated the need for a polarized primary beam model in order
+to mitigate the risk of diffuse polarized emission leaking into Stokes I, conflating with a 
+potential cosmological measurement. The MWA
+primary beam model is continuously improving to incorporate mutual coupling between the 
+phased dipoles, and embedded element patterns for each of the 32 dipoles on each antenna 
+\citep{Sutinjo:2015}. Other methods are also being pursued to directly measure the full beam 
+response in situ using the ORBCOMM satellite constellation \citep{Neben:2015}, and 
+drone-flown calibrator sources (Jacobs, et al. in prep). The latter method is similar to
+the strategy \citealt{Virone:2014} used to verify SKA beam patterns.
+
+\textbf{Calibration.} The most limiting factor in our analysis is likely to be insufficiently
+precise calibration solutions, which can cause foreground power to leak into the EoR window,
+as we see in the integrated 2D power spectra (Figure~\ref{fig:2d_ps_subband}).
+Because our calibration is based on sky and instrument models, the improvements
+described above will improve our calibration. We also plan to combine many snapshot
+observations when estimating gains, achieving higher signal to noise, which in turn will
+enable more sophisticated parameterizations of the antenna bandpasses. This will require
+an overhaul of the data flow depicted in Figure~\ref{fig:pipe} because snapshots will need
+to be combined in the calibration step, but preliminary investigations have shown that the
+gains are stable enough to be fit across several hours of observation.
+
+While the analysis presented here has not reached full potential, it represents the deepest power spectrum 
 integration to date produced by an imaging pipeline. Imaging involves many difficulties (e.g. 

### 2016-06-29 ms.tex
Fixed integration time for PAPER result.

@@
 signficantly higher than the latest PAPER result which 
-integrated nearly 1,000 hours ($\Delta^2 \le 502$ mK$^2$ at $z=8.4$; \citealt{Ali:2015}).
+integrated over 700 hours ($\Delta^2 \le 502$ mK$^2$ at $z=8.4$; \citealt{Ali:2015}).
 Several EoR experiments are reaching sensitivity levels where very low systematics

### 2016-06-29 ms.tex
Fixed details of residual flux density cut re: Pattis email

@@
 Our final data cut was made when inspecting the residual continuum images output from 
-FHD. We test for residual brightness at source locations by calculating a fractional residual brightness RMS 
+FHD. We test for residual flux density at source locations by calculating a fractional residual flux density RMS 
 in the following way. For each snapshot 
-continuum image, we find the residual brightness in the pixels of all sources greater than 0.5 Jy 
-subtracted within half-beam power and scale by the integrated flux density of the sources. This 
-gives us a list of fractional residual brightnesses for the snapshot, which we then use to calculate 
-an RMS. We found that most snapshots had residual brightness RMS $<10\%$ with some outliers, 
+continuum image, we find the residual flux density of all sources greater than 0.5 Jy 
+subtracted within half-beam power by integrating the brightness within the source pixel.
+We then scale by the integrated flux density of the sources, giving us a list of fractional
+residual flux densities for the snapshot, which we then use to calculate an RMS. We found
+that most snapshots had residual flux density RMS $<10\%$ with some outliers,
 which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
-additional 95 observations. The cause of the high residual brightness RMS is yet unknown and is 
+additional 95 observations. The cause of the high residual flux density RMS is yet unknown and is 
 not localized by observation day, LST, pointing, or any other jackknife we have performed.

### 2016-06-29 ms.tex
Another attempt at the residual flux density cut description

@@
 
-Our final data cut was made when inspecting the residual continuum images output from 
-FHD. We test for residual flux density at source locations by calculating a fractional residual flux density RMS 
-in the following way. For each snapshot 
-continuum image, we find the residual flux density of all sources greater than 0.5 Jy 
-subtracted within half-beam power by integrating the brightness within the source pixel.
-We then scale by the integrated flux density of the sources, giving us a list of fractional
-residual flux densities for the snapshot, which we then use to calculate an RMS. We found
+Our final data cut was made when inspecting the snapshot residual continuum images output from 
+FHD. 
+We estimate a proxy for the residual flux density from foreground sources by calculating
+the RMS of the fractional residual flux densities for all subtracted sources greater than
+0.5 Jy within half-beam power. The fractional residual flux density is measured as the ratio
+of the residual image pixel value (Jy) at the source position to the integrated flux density
+of the source.
+We found
 that most snapshots had residual flux density RMS $<10\%$ with some outliers,

### 2016-06-29 ms.tex
JDB comments

@@
 Due to relatively low signal to noise, these instruments aim for a statistical measurement of 
-the EoR in the form of a cosmological power spectrum. Meanwhile, the second generation 
-21cm EoR machines is on its way with the Hydrogen Epoch of Reionization Array (HERA
+the EoR in the form of a cosmological power spectrum. 
+Complementary to power spectrum experiments are efforts to detect the sky-average global
+21-cm signal from the EoR \citep[e.g.][]{Bowman:2010, Sokolowski:2015, Patra:2013, Voytek:2014}.
+Meanwhile, the second generation of
+21cm EoR interferometers is on its way with the Hydrogen Epoch of Reionization Array (HERA
 \footnote{http://reionization.org}, \citealt{DeBoer:2016}), 
@@
 behaved point spread function while retaining a dense core for EoR sensitivity 
-\citep{Beardsley:2013}.\footnote{A drone flyover view of the array layout is available on YouTube at \url{https://youtu.be/yDWdTUzTUMo}.}
+\citep{Beardsley:2013, Bowman:2006}.\footnote{A drone flyover view of the array layout is available on YouTube at \url{https://youtu.be/yDWdTUzTUMo}.}
 A full description of the science capabilities of the array is found in
@@
 (starting $\sim70\lambda$), and the foreground power mixing to high spectral 
-modes. Between the coarse band lines and to the left of the vertical streaks we see regions 
+modes \citep{Bowman:2009}. Between the coarse band lines and to the left of the vertical streaks we see regions 
 which contain both positive and negative (indicated by blue on the color bar) pixels. These 
@@
 repeatedly form power spectra to test and refine our analysis. While an exhaustive catalog 
-of these improvements would be unsuited for this article (and likely bore the reader), we 
+of these improvements is outside the scope of this paper, we 
 demonstrate the utility of the 2D power spectrum as a FoM with a few key techniques we 
@@
 positional accuracy of catalog entries. By using simulations of visibilities they were able to 
-isolate the effect of using perfect versus offset source positions. They confirmed the
+isolate the effect of using perfect versus offset source positions. In their simulations source 
+position offsets of $14\%$ of the synthesized
+beam-width had significant impact on foreground subtraction, confirming the
 importance of a complete and accurate point source catalog in order to retain a clean EoR
@@
 of the pixel and creates model visibilities for each snapshot in the same way that it imports 
-a catalog of point sources.
+a catalog of point sources. This is similar to the strategy employed by 
+\citealt{Thyagarajan:2015} to model diffuse structure.
 
@@
 Up to this point we have only discussed testing and analysis on the three hour golden data 
-set. We next turn towards a deep integration, incorporating the techniques described above. 
+set. We next turn towards a deeper integration, incorporating the techniques described above. 
 We start with all MWA observations taken on the EoR0 field at 182~MHz between August 
@@
 on all days of observation and decided to cut all $-5$, $-4$, $-3$, and $+4$ pointings from 
-our data set. In principle it may be possible to model the Galactic disk well enough to 
-account for its presence, but with a lack of sufficient Galactic model, beam model, and the 
-analysis tools to include it, we leave this to future work.
+our data set. In principle it may be possible to model the Galactic plane well enough to 
+account for its presence, but we leave this to future work.
 
@@
 
-Motivated by the hand grading done with power spectrum jackknives, we developed 
+Motivated by the manual classification done with power spectrum jackknives, we developed 
 another metric to quickly predict power spectrum quality for each snapshot in our data set. 
@@
 features can be seen in these spectra. In all cases the foreground wedge is prominent, with 
-extra power at large scales (low $k_{\perp}$). This is an indication that our diffuse model can 
+extra power at large scales (low $k_{\perp}$). This is an indication that our diffuse model needs to 
 improve for deeper subtraction.
@@
 0.25$ h Mpc$^{-1}$, contains purely positive bins, indicating non-noise-like power. The 
-cause for this seeming leakage is yet unknown, but will ultimately limit our integration in this 
+cause for this seeming leakage is yet unknown, and limits our integration in this 
 analysis. One suspected origin of this contamination was individual snapshots with high 
@@
 These regions are encouraging because they have the potential to continue integrating down
-with more data. Improved suppression of the coarse band harmonic and cable reflection lines
+with more data without further analysis improvements. Further suppression of the coarse band harmonic and cable reflection lines
 will also improve the limits presented here.
@@
 noise, and therefore our upper limit, in this regime. However, until the leakage at low $k$ is 
-understood, progress at higher $k$ is susceptible to running into the same systematic. 
-While a longer integration may improve the upper limit in the short term, the hope for an 
-eventual detection lies in understanding the contaminants at low $k$.
+understood, progress at higher $k$ is susceptible to running into the same systematic
+with longer integrations.
 
@@
 which is not surprising given that this integration contains about ten times more data, but 
-has a strong signal to noise on the power spectrum. Our results are also consistent with the 
+is systematic limited. Our results are also consistent with the 
 40 hour GMRT limit of $\Delta^2\le6.15\times10^4$~mK$^2$ at $k=0.5\, h$~Mpc$^{-1}$ and $z=8.6$ \citep{Paciga:2013}, though 
@@
 than our best limit in power units, though again probing a significantly different redshift. 
-While the MWA analysis is not yet at that level of maturity, there is room for rapid 
-improvement. The red lines in Figure~\ref{fig:1d_ps} indicate the noise level possible 
+The MWA analysis is rapidly improving as we uncover and mitigate systematics to realize
+the full sensitivity of the telescope.
+The red lines in Figure~\ref{fig:1d_ps} indicate the noise level possible 
 to reach with these data if systematics can be overcome.
@@
 efficient gridding and mapmaking, foreground modeling), but if systematics can be 
-overcome, it has the potential to quickly compete with other more pointed experiments and 
+overcome, it has the potential to compete with other more targeted experiments and 
 analysis styles. 
@@
 with complimentary probes such as galaxy surveys or other intensity mapping experiments
- \citep[e.g.][]{DeBoer:2016, Vrbanec:2016, Beardsley:2015, Silva:2015, Dore:2014, Lidz:2009}.
+ \citep[e.g.][]{DeBoer:2016, Vrbanec:2016, Beardsley:2015, Silva:2015, Dore:2014, Lidz:2009}, which will ultimately unlock the full potential of 21cm observations.
 Here we have identified a crucial region of power spectrum space that is 

### 2016-06-29 ms.tex
EL comments

@@
 performs 
-flagging, averages in time and freqeuncy, and writes to disk. For this step we use the 
+flagging, averages in time and frequency, and writes to disk. For this step we use the 
 \cotter package \citep{Offringa:2015}, which in turn calls the \texttt{AOFLAGGER}\footnote{\url{http://
@@
 foreground model. This step results in independent complex gains for each antenna, 
-frequency channel, and polarization. In the second step we impose restrictions on these 
+80~kHz frequency channel, and polarization. In the second step we impose restrictions on these 
 gains motivated by our understanding of the spectral response of the instrument. By 
@@
 In the first calibration step we allow our complex gains to account for any direction-independent 
-response on a per antenna, per frequency channel, per polarization basis. To 
+response on a per antenna, per 80~kHz frequency channel, per polarization basis. To 
 define our gains in this way, we have made two simplifications. First we push all 
@@
 \citep{Morales:2009,Bhatnagar:2008}. We use a simulation-based primary beam model for MWA 
-antennas developed by \citealt{Sutinjo:2015}. At this stage we also average in frequency by 
+antennas developed by \citealt{Sutinjo:2015} 
+which incorporates an average embedded element pattern for the dipoles, as well as mutual
+coupling between dipoles within an antenna.
+At this stage we also average in frequency by 
 a factor of two by gridding pairs of frequency channels to the same $(u,v)$ plane, resulting in 
@@
 smoothed to degree scales to emphasize the large scale structure and approximate what 
-the MWA instrument observes with a natural weight.
+the MWA instrument observes with a natural weighting.
 
@@
 smoothed to degree scales to emphasize the large scale structure and approximate an 
-MWA snapshot natural weighting.
+MWA snapshot natural weighting. Note that the negative brightness values are a 
+consequence of not sampling the zero-spacing part of the $(u,v)$ plane.
 \label{fig:diffuse}
@@
 Studies of the 
-beam are underway \citep[e.g.][]{Neben:2015}, and will likely help to further isolate the 
+beam are underway \citep[e.g.][]{Neben:2015, Sutinjo:2015}, and will likely help to further isolate the 
 foreground contaminates in our power spectra. The foreground model is a constant area of 
@@
 spectrum in units of mK$^2$ to be roughly flat over the scales probed by the MWA, PAPER, 
-and GMRT, we can glean a view of the current state of the field. The results from this 
-analysis are a modest improvement over the previous best MWA results \citep{Dillon:2015}, 
+and GMRT, we can glean a view of the current state of the field. 
+The best result from this analysis is an upper limit on the power spectrum of 
+$\Delta^2 \le 2.7 \times 10^4$~mK$^2$ at $k=0.27\, h$~Mpc$^{-1}$ and $z=7.1$.
+This is a modest improvement over the previous best MWA results \citep{Dillon:2015}, 
 which is not surprising given that this integration contains about ten times more data, but 

### 2016-06-30 ms.tex
Updated plot reference after color change

@@
 three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
-results from Figure~\ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
+results from Figure~\ref{fig:1d_ps}, while the gray line plots the equivalent RTS$+$CHIPS 
 results (with coarse band harmonics included). Despite the differences in the two pipelines, 

### 2016-07-01 ms.tex
Updated RTS-CHIPS comparison section

@@
 FHD, as well as a different input point source model. 
-The primary differences lie in the 
-bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
-calibration model uses a model with 1000 sources, for which ionospheric corrections are 
-estimated and applied, before peeling of those sources from the dataset. The bandpass 
-calibration is fundamentally different to FHD.
-The bandpass for each antenna is fitted to a 2nd order polynomial within each 1.28~MHz coarse 
-band individually. The delay of the 150~m cable reflection discussed earlier is comparable
-to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
+The primary differences lie in the use of ionospheric corrections, the
+bandpass calibration, and the lack of a diffuse model. 
+RTS accomplishes the interferometric calibration in two steps: a
+direction-independent calibration to a single compound calibrator
+created by combining the 1000 apparently brightest sources in the sky,
+followed by an individual calibration and subtraction of those sources
+inside the Calibration Measurement Loop (CML, \citealt{Mitchell:2008}).
+The CML estimates individual ionospheric corrections for all sources and
+performs a full direction-dependent calibration for the 5 very
+brightest ones. These tasks
+are distributed over independent parallel threads for each 1.28~MHz
+coarse channel.
+
+The bandpass calibration is also fundamentally different to FHD. The bandpass for each antenna is 
+fitted to a 3rd order polynomial within each 1.28 MHz coarse band and each direction and 
+polarization individually. The delay of the 150~m cable reflection discussed earlier is 
+comparable to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
 solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
 data \citep{Jacobs:2016}.
+
+The source catalog used with RTS was a combined cross-match created with the Positional 
+Update and Matching Algorithm (PUMA, J.~L.~B.~Line et al. 2016, in review). Full details of PUMA and 
+this cross-matched catalog can be found in Line et al. 2016, but we include a brief 
+description here. PUMA is designed to cross-match low radio-frequency ($\lesssim 1\,$GHz) 
+catalogs. It utilizes a Bayesian probabilistic positional cross-match approach based on~
+\citealt{Budavari:2008}, combined with criteria based on catalog resolution and fitting the 
+spectral energy distribution to a power-law. These criteria allow for surveys with differing 
+resolutions, which can introduce confusing sources into the matched process.
+Primarily the source catalog was based on the MWA Commissioning Survey
+\citep[MWACS, ][]{Hurley-Walker:2014}, which was cross-matched to the $74\,$MHz Very 
+Large Array Low Frequency Sky Survey redux~\citep[VLSSr, ][]{Lane:2012}, the Molonglo 
+Reference Catalogue~\citep[MRC, ][]{Large:1981}, the $843\,$MHz Sydney University 
+Molonglo Sky Survey~\citep[SUMSS,][]{Mauch:2003}; and the $1.4\,$GHz NRAO VLA Sky 
+Survey~\citep[NVSS,][]{Condon:1998}. MWACS covers approximately 
+$20.5^h < \textrm{RA} < 8.5^h$,  $-ˆ’58^\circ < \delta < -ˆ’14^\circ$, so to complete the sky 
+coverage needed, MRC was used as a base catalogue outside of the MWACS coverage and 
+was matched to VLSSr, SUMSS and NVSS.
+
+Since RTS has the added step of individual source peeling, there is a
+greater possibility for numerical calibration failure. Before passing to CHIPS, a simple quality
+assurance step is considered, which is based upon the variance of residual visibilities in each
+1.28~MHz coarse band. 
+Observations with divergent or
+unstable calibrations were readily identified by variances far outside
+the otherwise observed distribution of values.
+Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
+pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
+successfully, potentially due to adverse ionospheric conditions.
 
@@
 used by \eppsilon.
-
-Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
-pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
-successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
-same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
+The data were divided into the 
+same three redshift bins, and the 2D and 1D power spectra formed.
+
+Table \ref{tbl:limits} 
 displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
@@
 results.
-
-% ADAM: Motivation why a pipeline is being discussed
-% MAHSA: Summary of RTS to power spectrum (e.g. calibration, etc)
-% MAHSA QA: - bad day, forward reference Jordan et al, Beam nulls - fixed for future analysis
-% CATH: Plots
-%     by pointing - diff zenith vs +2 
-%	2D PS vs redshift
-%	1D
 

### 2016-07-07 ms.tex
Added CAASTRO affil for Mahsa

@@
 N.~Barry\affils{UW},
-M.~Rahimi\affils{UMelbourne},
+M.~Rahimi\affils{UMelbourne,CAASTRO},
 B.~Pindor\affils{UMelbourne,CAASTRO},

### 2016-07-08 ms.tex
JSD comments

@@
 the full three dimensional space of the epoch. (For reviews, see \citealt{Furlanetto:2006}, 
-\citealt{Morales:2010}, \citealt{Zaroubi:2013}, and \citealt{Pritchard:2012}) The first generation of instruments with primary science goals 
+\citealt{Morales:2010}, \citealt{Zaroubi:2013}, \citealt{Loeb:2013}, and \citealt{Pritchard:2012}) The first generation of instruments with primary science goals 
 to detect the highly redshift 21cm signal have been built, including the GMRT (Giant Metrewave 
@@
 \citep{Thyagarajan:2015b, Thyagarajan:2015, Trott:2012, Liu:2014a, Liu:2014b, 
-Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}. Nevertheless, 
-the EoR window is preserved above the wedge, and 
+Hazelton:2013, Pober:2013, Thyagarajan:2013, Vedantham:2012, Morales:2012, Datta:2010}, 
+while others are investigating the spectral structure of point sources themselves \cite[e.g.][]{Offringa:2016}.
+The EoR window is still expected to be preserved above the wedge, and 
 several analysis pipelines are under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
 prep; D.~A.~Mitchell et al. 2016, in prep; ][]{Jacobs:2016, Trott:2016, 
-Dillon:2013, Trott:2014}.
+Dillon:2015b, Dillon:2013, Trott:2014}.
 
@@
 coarse band harmonic lines. 
+The vertical streaks at high $k_{||}$ and high $k_{\perp}$ are due to sparse $(u,v)$ sampling
+beyond the dense core of the MWA.
 \label{fig:example_ps}
@@
 of 6.8. The right panels show the high band, centered at 190.1 MHz, or a redshift of 6.5. 
+The top row corresponds to East-West instrumental polarization, while the bottom row 
+shows North-South polarization.
 The contours show the window used for averaging to one dimension.
@@
 the measured power is shown with solid blue, the 1-$\sigma$ noise level is shown with 
-thin red, and the 2-$\sigma$ upper limit for each bin is shown with dashed magenta. 
+thin red, and the 2-$\sigma$ upper limit for each bin is shown with magenta. 
 Where our unbiased estimator is negative, the absolute value is shown, but with a dotted 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{1D_spectra.pdf}
+\includegraphics[width=\textwidth]{1D_spectra.png}
 \caption[1D deep power spectra]{
@@
 corresponding to the bin size used in the average. Where the measured signal is negative 
-we plot the absolute value with a dotted line. The thin red line is the 1-$\sigma$ noise level, and 
-the dashed magenta line is the 2-$\sigma$ upper limit for each $k$ bin. 
+we plot the absolute value with a dotted line. 
+The gray boxes show the $\pm 2\sigma$ error bars on the measured power spectrum.
+Where the boxes meet the horizontal axis we are consistent with zero.
+The thin red line is the 1-$\sigma$ noise level, and 
+the magenta line is the 2-$\sigma$ upper limit for each $k$ bin. 
 A fiducial theoretical model for a fully neutral IGM from \citet{Furlanetto:2006} is shown
@@
 which is not surprising given that this integration contains about ten times more data, but 
-is systematic limited. Our results are also consistent with the 
+is systematics limited. Our results are also consistent with the 
 40 hour GMRT limit of $\Delta^2\le6.15\times10^4$~mK$^2$ at $k=0.5\, h$~Mpc$^{-1}$ and $z=8.6$ \citep{Paciga:2013}, though 

### 2016-08-01 ms.tex
Updated Carroll et al 2016 reference
Fixed citealt->citet

@@
 observations of highly redshifted quasars have placed upper bounds on redshifts by which 
-reionization is complete. For example, \citealt{Fan:2006a} showed that reionization must be 
+reionization is complete. For example, \citet{Fan:2006a} showed that reionization must be 
 complete by $z \approx 6$, a result which was confirmed independent of model by 
-\citealt{McGreer:2015}.
+\citet{McGreer:2015}.
 Using a $z_{\mathrm{end}}>6$ prior, the most recent analysis of \emph{Planck} data 
@@
 cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}, and 
-\citealt{Pober:2015} was able to place constraints on physical reionization models. 
+\citet{Pober:2015} was able to place constraints on physical reionization models. 
 However, much work is to be done to understand the data produced by these arrays. 
@@
 limit ($\Delta^2 \le 6.15 \times 10^4$ mK$^2$ at $z=8.6$; \citealt{Paciga:2013}), but 
-signficantly higher than the latest PAPER result which 
+significantly higher than the latest PAPER result which 
 integrated over 700 hours ($\Delta^2 \le 502$ mK$^2$ at $z=8.4$; \citealt{Ali:2015}).
@@
 FM radio, or TV stations. A recent study of the RFI environment at the Murchison Radio 
-Observatory can be found in \citealt{Offringa:2015}.
+Observatory can be found in \citet{Offringa:2015}.
 
@@
 A full description of the science capabilities of the array is found in
-\citealt{Bowman:2013}.
+\citet{Bowman:2013}.
 The high imaging capability of the MWA enables us to calibrate and subtract foregrounds
@@
 
-The technical design of the MWA is reviewed in \citealt{Tingay:2013}, and we highlight a 
+The technical design of the MWA is reviewed in \citet{Tingay:2013}, and we highlight a 
 few key characteristics that will become important in our analysis of the data. Each 
@@
 defined two independent reference analysis pipelines. The details of this strategy are 
-outlined in \citealt{Jacobs:2016}. This study is based on the FHD-to-\eppsilon 
+outlined in \citet{Jacobs:2016}. This study is based on the FHD-to-\eppsilon 
 pipe, which is in turn based on the Fast Holographic Deconvolution 
@@
 solutions which has been shown to contaminate the EoR window \citep{Barry:2016}. 
-Recently, \citealt{Patil:2016} demonstrated excess noise and a suppression of diffuse
+Recently, \citet{Patil:2016} demonstrated excess noise and a suppression of diffuse
 foregrounds in LOFAR images after calibration and subtraction of bright discrete
@@
 
-FHD utilizes the StEFCal algorithm described in \citealt{Salvini:2014} to find the minimum 
+FHD utilizes the StEFCal algorithm described in \citet{Salvini:2014} to find the minimum 
 $\chi^2$ estimate with respect to the complex gains. The result of this operation is 
@@
 \citep{Morales:2009,Bhatnagar:2008}. We use a simulation-based primary beam model for MWA 
-antennas developed by \citealt{Sutinjo:2015} 
+antennas developed by \citet{Sutinjo:2015} 
 which incorporates an average embedded element pattern for the dipoles, as well as mutual
@@
 our coordinates to cosmological units according to the relationships given in 
-\citealt{Morales:2004}, where angular and frequency units $(\theta_x,\theta_y,f)$ map to 
+\citet{Morales:2004}, where angular and frequency units $(\theta_x,\theta_y,f)$ map to 
 cosmological distance units $(r_x,r_y,r_z)$. Often $r_z$ is referred to as the line of sight 
@@
 cable. 
-A similar approach was taken at lower frequencies in \citealt{Ewall-Wice:2016}.
+A similar approach was taken at lower frequencies in \citet{Ewall-Wice:2016}.
 The full gain model is expressed as
@@
 the golden data set to build our model. The process of building the catalog is presented in 
-P.~A.~Carroll et al. 2016 (in review). They applied machine learning classification methods 
+\citet{Carroll:2016}. They applied machine learning classification methods 
 to select reliable detections from the full deconvolution FHD mode, culminating in the KGS 
@@
 a catalog of point sources. This is similar to the strategy employed by 
-\citealt{Thyagarajan:2015} to model diffuse structure.
+\citet{Thyagarajan:2015} to model diffuse structure.
 
@@
 The final mask we apply is the wedge. We found that a small buffer beyond the horizon was
-necessary to completely mask out the wedge, consistent with \citealt{Dillon:2015}. We
+necessary to completely mask out the wedge, consistent with \citet{Dillon:2015}. We
 implement the buffer by increasing the slope of the horizon line by 14\%.
@@
 
-As demonstrated in \citealt{Jacobs:2016}, comparison between independent 
+As demonstrated in \citet{Jacobs:2016}, comparison between independent 
 analysis pipelines is essential to evaluate the validity of algorithms under active development. 
@@
 catalogs. It utilizes a Bayesian probabilistic positional cross-match approach based on~
-\citealt{Budavari:2008}, combined with criteria based on catalog resolution and fitting the 
+\citet{Budavari:2008}, combined with criteria based on catalog resolution and fitting the 
 spectral energy distribution to a power-law. These criteria allow for surveys with differing 
@@
 through multiple-snapshot solutions or refined antenna response models. 
-Through simulation, \citealt{Thyagarajan:2016} recently demonstrated the necessity of
+Through simulation, \citet{Thyagarajan:2016} recently demonstrated the necessity of
  precise foregrounds and instrumental models in order to retain a clean EoR window.
@@
 can be difficult to model at the necessary precision \citep{Thyagarajan:2016}. 
-\citealt{Asad:2016} demonstrated the need for a polarized primary beam model in order
+\citet{Asad:2016} demonstrated the need for a polarized primary beam model in order
 to mitigate the risk of diffuse polarized emission leaking into Stokes I, conflating with a 
@@
 drone-flown calibrator sources (Jacobs, et al. in prep). The latter method is similar to
-the strategy \citealt{Virone:2014} used to verify SKA beam patterns.
+the strategy \citet{Virone:2014} used to verify SKA beam patterns.
 

### 2016-08-01 ms.tex
Added reference to Greig 2016

@@
 Using the first generation of instruments, several upper limits have been placed on the 21 
-cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}, and 
-\citet{Pober:2015} was able to place constraints on physical reionization models. 
+cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}.
+Furthermore, \citet{Pober:2015} and \citet{Greig:2016} were able to place constraints on physical reionization models. 
 However, much work is to be done to understand the data produced by these arrays. 

### 2016-08-01 ms.tex
bolded change from previous commit
Addressing minor comments from referee

@@
 cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}.
-Furthermore, \citet{Pober:2015} and \citet{Greig:2016} were able to place constraints on physical reionization models. 
+\textbf{Furthermore,} \citet{Pober:2015} \textbf{and \citet{Greig:2016} were} able to place constraints on physical reionization models. 
 However, much work is to be done to understand the data produced by these arrays. 
@@
 The EoR window is still expected to be preserved above the wedge, and 
-several analysis pipelines are under active development \citep[e.g. B.~J.~Hazelton et al. 2016, in 
+several analysis pipelines are under active development 
+\textbf{to exploit this foreground isolation}
+\citep[e.g. B.~J.~Hazelton et al. 2016, in 
 prep; D.~A.~Mitchell et al. 2016, in prep; ][]{Jacobs:2016, Trott:2016, 
@@
 found to be particularly well behaved. The MWA EoR collaboration has designated this set 
-as a ``golden data set'', which is used to build analysis tools and compare early results. All 
-techniques demonstrated here will use this golden data set \cite[e.g.][]{Jacobs:2016, Trott:2016, Pober:2016, Dillon:2015}. In Section~\ref{sec:deep} we 
+as a ``golden data set'', which is used to build analysis tools and compare early results 
+\textbf{\cite[e.g.][]{Jacobs:2016, Trott:2016, Pober:2016, Dillon:2015}.} All 
+techniques demonstrated here will use this golden data set. In Section~\ref{sec:deep} we 
 will use a larger data set to move toward a deep integration. This data set consists of all 
@@
 not seen evidence of these systematics through simulations and direct propagation of
-our noise \citep[Hazelton et al. 2016, in prep.]{Barry:2016}.
+our noise \citep[\textbf{B.~J.}~Hazelton et al. 2016, in prep.]{Barry:2016}.
 
@@
 where $g_i(\nu)$ and $g_j(\nu)$ are the complex gains for antennas $i$ and $j$ 
-respectively. Because we are treating polarizations independently, we allow the antenna 
+respectively,
+\textbf{and $V_{ij}(\nu)$ is the true visibility which we aim to recover through calibration.}
+Because we are treating polarizations independently, we allow the antenna 
 subscript to run over both East-West (E-W) and North-South (N-S) polarizations.
@@
 catalog pulling from our early KGS catalog, the MWA Commissioning Survey\footnote{The 
-more complete GLEAM Survey \citep[][Hurley-Walker et al., in collaboration review]
+more complete GLEAM Survey \citep[][\textbf{N.}~Hurley-Walker et al., in review]
 {Wayth:2015} was not available at the time of analysis.} \citep[MWACS, ][]
@@
 and multiple polarization components.
-Lenc, et al. (in review) demonstrated the presence of strong polarized large-scale structures 
+\textbf{E.}~Lenc, et al. (in review) demonstrated the presence of strong polarized large-scale structures 
 in the EoR0 field at 154 MHz with varying Faraday depths. They observed rotations in the
@@
 Update and Matching Algorithm (PUMA, J.~L.~B.~Line et al. 2016, in review). Full details of PUMA and 
-this cross-matched catalog can be found in Line et al. 2016, but we include a brief 
+this cross-matched catalog can be found in Line et al. (2016), but we include a brief 
 description here. PUMA is designed to cross-match low radio-frequency ($\lesssim 1\,$GHz) 
@@
 polarization components to the model will improve this subtraction even further.
-As Lenc, et al. 2016 (in review) demonstrated, substantial polarized diffuse structure
+As \textbf{E.}~Lenc, et al. 2016 (in review) demonstrated, substantial polarized diffuse structure
 exists in the EoR0 field. The contributions to Stokes Q and U depend on the ionospheric
@@
 response in situ using the ORBCOMM satellite constellation \citep{Neben:2015}, and 
-drone-flown calibrator sources (Jacobs, et al. in prep). The latter method is similar to
+drone-flown calibrator sources (\textbf{D.~C.}~Jacobs, et al. in prep). The latter method is similar to
 the strategy \citet{Virone:2014} used to verify SKA beam patterns.

### 2016-08-02 ms.tex
nearly finished with minor referee comments

@@
 direction). The visibilities are gridded using the primary beam as the gridding kernel, placing 
-the data in the holographic frame, which has been shown to be the optimal frame for 
+the data in the \textbf{``holographic frame,"} which has been shown to be the optimal \textbf{weighting scheme} for 
 combining images in the sense that it preserves all information for parameter estimation 
@@
 
+\textbf{The pipeline as described up to this point is applied to both the calibrated data
+and the foreground model. At this point we subtract the model from the data to form
+residual data as well. All three sets of data (dirty, model, and residual) are carried through 
+the remaining steps to form corresponding power spectra.}
+
 After squaring and dividing by our observation window function \citep{Bowman:2006}, we 
@@
 mathematically equivalent to cross multiplying the even and odd cubes. The three 
-dimensional power spectrum cube can next be averaged in annuli to form two dimensional 
+dimensional power spectrum cube can next be averaged in annuli 
+\textbf{of constant $k_{\perp}$ and $k_{||}$ (i.e. orthogonal to the $k_{||}$ axis)}
+to form two dimensional 
 power spectra, or spherical shells to form one dimensional power spectra where we will 
@@
 beyond the dense core of the MWA.
+\textbf{The right axis shows the delay (Fourier dual to frequency) corresponding to the 
+$k_||$ axis, and the top axis shows the baseline length (in wavelengths) corresponding
+to the $k_{\perp}$ axis.}
 \label{fig:example_ps}
@@
 (starting $\sim70\lambda$), and the foreground power mixing to high spectral 
-modes \citep{Bowman:2009}. Between the coarse band lines and to the left of the vertical streaks we see regions 
+modes \citep{Bowman:2009}. 
+\textbf{We provide axes more closely related to the measurements to assist in connecting
+these instrumental effects. The right axis shows delay (Fourier dual to frequency), and the
+top axis shows baseline length measured in wavelengths.}
+Between the coarse band lines and to the left of the vertical streaks we see regions 
 which contain both positive and negative (indicated by blue on the color bar) pixels. These 
@@
 to select reliable detections from the full deconvolution FHD mode, culminating in the KGS 
-catalog. The work here uses an early iteration of the KGS catalog that was available at the 
+catalog\footnote{\textbf{KGS is an abbreviation of KATALOGSS, the KDD (Knowledge 
+Discovery in Databases) Astrometry, Trueness, and Apparent Luminosity of Galaxies in 
+Snapshot Surveys}}. The work here uses an early iteration of the KGS catalog that was available at the 
 time of analysis.
@@
 visibilities was higher when using the full hierarchical catalog. In order to put both residual 
-2D power spectra onto the same scale for comparison, we first divide each pixel by the 
+2D power spectra onto the same scale for comparison, we first divide each 
+\textbf{$(k_{\perp},k_{||})$ cell}
+by the 
 corresponding dirty power spectrum pixel, then subtract to arrive at a ratio difference. 
@@
 earth to improve the point spread function (PSF) of the instrument. This integrating of 
-images is done in a uniformly weighted frame to minimize the effect of double instrument 
+images is done \textbf{with uniform weighted data} to minimize the effect of double instrument 
 convolution (once when the data are taken, again when we use the output as a model). We 
@@
 were identical as well. We compare the model and residual power spectra by direct 
-subtraction in Figure~\ref{fig:diffuse_diff}. The top panel shows the model power with the 
-diffuse subtracted from the model power without. 
+subtraction in Figure~\ref{fig:diffuse_diff}. 
+The top panel shows \textbf{our foreground model power spectrum
+minus the model power spectrum when including diffuse}. 
 Because our diffuse model added power to the full foreground model, the entire plot is
@@
 effect of subtracting a diffuse foreground model. The calibration is identical with and without 
-the diffuse model, so the dirty power spectra are identical. The diffuse model adds a large 
-amount of power to the model (top), and the residual power (bottom) is significantly lower in 
-the wedge when using the diffuse model (positive difference), demonstrating a successful 
-subtraction. While this first attempt at a diffuse model was rudimentary, it shows promise as 
-it successfully removed 90\% of the residual power. 
+the diffuse model, so the dirty power spectra are identical. 
+\textbf{In the top panel the model power spectrum difference is almost entirely negative 
+(red), indicating that the diffuse model added a large amount of power to the foreground 
+model. The bottom panel shows the residual power spectrum difference is positive in the 
+wedge (blue), demonstrating a successful subtraction.}
+While this first attempt at a diffuse model was rudimentary, it 
+\textbf{successfully removed 90\% of the residual power. }
 \label{fig:diffuse_diff}

### 2016-08-03 ms.tex
Added back in omitted words
Adding error plot and corresponding description in the paper.

@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{example_2derror.pdf}
+\caption{
+\textbf{
+Error level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
+short baseline length (low $k_{\perp}$) due to the dense MWA core. The array is more
+sparse at longer baselines, and the noise increases. The second $k_{||}$ bin has slightly
+lower noise than the rest of the $k_{||}$ modes due to the interaction between the
+Lomb-Scargle periodogram with the Blackman-Harris window function applied to the data.
+}
+\label{fig:example_2derror}
+}
+\end{center}
+\end{figure}
+
+\textbf{Figure~\ref{fig:example_2derror} shows the error level corresponding to the two 
+dimensional power spectrum in Figure~\ref{fig:example_ps}. These errors
+are found by propagating noise measured from calibrated visibilities through the entire
+pipeline. The dense core of the MWA results in relatively low noise at low $k_\perp$.
+As the $(u,v)$ density of the array decreases at longer baselines, the noise increases.
+The noise is mostly constant across $k_{||}$ because the Fourier transform distributes
+the noise in frequency to all modes equally \citep{Morales:2004}.
+The exception is the second $k_{||}$ bin, which has slightly lower noise than the rest of the 
+$k_{||}$ modes. This is a result of the Lomb-Scargle periodogram interacting with the
+Blackman-Harris window function we apply to the data. In the case of $k_{||}=0$
+(shown as the bottom bin on the log plot), the
+cosine term carries all the information and has a noise level $\sqrt{2}$ lower than any other
+sine or cosine term individually. The first non-zero $k_{||}$ mode is highly covariant with the 
+bottom bin due to the window function. Therefore the noise on this mode's cosine term is 
+lower than other higher order cosines. With the added contribution from the sine term, this
+mode contains the lowest level of noise.
+}
+
 \section{Analysis Methods for Testing Data Quality}\label{sec:techniques}
@@
 subtraction in Figure~\ref{fig:diffuse_diff}. 
-The top panel shows \textbf{our foreground model power spectrum
+The top panel shows \textbf{our point source foreground model power spectrum
 minus the model power spectrum when including diffuse}. 

### 2016-08-03 referee_response.txt
Adding responses to referee so far

Major comments
---------------
---The authors emphasize the diagnostic importance of the kperp-kpara plot, and I appreciate the care with which such plots were discussed. However, I found the absence of a kpara-kperp error plot to be rather conspicuous. I would imagine that an error plot would also be enormously informative, and I'd like to see one included, along with a short discussion of its features.

We have added an error plot in Section 3.3 (now Figure 3), along with a paragraph at the end of the section describing the structure.

======================================================================

---11th paragraph of Section 3.1. "At this stage we also average in frequency by a factor of two..." Is there a specific motivation for this? Or is it just a convenient way to reduce the data volume?

======================================================================

---After Eq. (5): "After fitting for all other parameters, we fit for the reflection mode". Why do this instead of a global fit for all the parameters, which would presumably give a better overall fit? I've noticed that with the form of the g-hat, if A_i,1 and A_i,2 are zero, the reflection mode parameters are degenerate with the "normal" calibration parameters. Is the separate fit a desire to avoid the near-degeneracy that results when A_i,1 and A_i,2 are small?

======================================================================

---Penultimate paragraph of Section 4.2. This reminds me of the Hazelton et al. (2013) paper about multi-baseline wedge effects. It would seem like the current paper is suggesting that the Hazelton et al. effect can be reduced with a fine kernel resolution. However, Hazelton et al. seem to imply that their effect is fundamental and unavoidable. Can the authors explicitly clarify this?

======================================================================

---2nd paragraph of Section 4.3. "All other sources were given a spectral index of -0.8". What motivated this choice?

======================================================================

---Penultimate paragraph of Section 4.3. The authors find that using the two different foreground models gave different flux scales. Is there a sense in which the flux scale has converged?

======================================================================

---Figures 9 and 10. Figure 10 seems to indicate that there is a "+5" pointing. Why is it not included in Figure 9?

======================================================================

---Figure 11, bottom panel. Since the "+3" portion seems so tightly clustered and is only excluded from the analysis due to some consistent offset, might this be fixable by adjusting calibration parameters?

======================================================================

---8th paragraph of Section 5.2. I think the vertical lines caused by incomplete uv coverage needs more explanation/discussion. A thinning uv coverage alone should not result in the vertical streaks. It needs to be coupled with increased leakage from within the wedge. The fact that reduced uv coverage causes vertical streaks is therefore also a result of how the power spectrum is estimated (since that + the instrument is what determines the leakage). As an example, one could go with a "scorched earth" style analysis, sacrificing sensitivity to preserve the EoR window by doing single-baseline delay spectrum analyses for the longer baselines. The foregrounds would be contained within the wedge under such a procedure, independent of uv-coverage (since we're already at the extreme of analyzing one baseline at a time). The form of one's power spectrum estimator must therefore play a role here.

======================================================================

---Along the same lines as the previous point, might an accounting of covariances between different power spectrum cells also help here, perhaps allowing for decreased leakage?

======================================================================

---5th from last paragraph of Section 5.2. Why an increase in slope of 14% of the horizon line? I'm curious as to the thinking here, particularly versus the alternative I've seen in the literature where a constant delay buffer is added to the horizon line.

======================================================================

---Figure 15. Why does the FHD + eppsilon pipeline not go to as high k as RTS + CHIPS? Is there some limitation that prevents the highest k regions from being explored?

======================================================================

---It would be helpful in the discussion section to give a sense for what data and results we can look forward to. As an outsider, for example, I am curious as to whether there is more data "in the can" that is just waiting to be analyzed, or whether any new results will come from data taken once the MWA expansion is past its construction/commissioning phase.

======================================================================

Minor comments
---------------
---Throughout: the authors seem to use \citealt{} or \citep{} for all citations, but when the citation is part of the sentence, \citet{} to be used (so that publication year but not the author name is enclosed in parentheses).

This has been fixed in the updated draft.

======================================================================

---4th paragraph of introduction: Greig et al. also placed constraints on physical models, I think.

Yes, thank you for pointing that out. This citation has been added.

======================================================================

---Final sentence of 4th paragraph of introduction: The two halves of the sentence don't really have a logical connection to each other. I was confused for a moment because I thought there was a missing part to sentence. In particular, when I read "...and several analysis pipelines are under active development" I thought the authors meant that there were specific efforts to preserve the EoR window, but I think it's just generic pipeline development.

We have rephrased to “… and several analysis pipelines are under active development to exploit this foreground isolation” to emphasize that the pipelines cited are following the EoR window framework.

======================================================================

---Similarly, in the last paragraph of Section 2, when the authors say "(e.g., Jacobs et al. 2016...)", I'm not sure what the "for example" is referring to. I'm not sure how those other works demonstrated that "all techniques demonstrated here will use this golden data set"?

Those citations were misplaced and meant for the previous sentence. This has been fixed.

======================================================================

---Equation 1: V_ij is never defined as the "true" visibility.

It is now defined in the sentence after the equation.

======================================================================

---11th paragraph of Section 3.1 and first paragraph of Section 3.3: what does "frame" mean? Is this a technical term? I'm not familiar with it.

“Holographic frame” is now introduced as a term referring to the specific weighting scheme that yields optimal maps. We also removed another use of “frame” in Sec 4.4 when referring to weighting.

======================================================================

---Section 3.3: even though it can be inferred from the description in Section 3.2, it would be helpful to readers to mention the foreground subtraction step in Section 3.3 to make it clear where it fits into the power spectrum pipeline.

We have injected a paragraph to Section 3.3 to mention the foreground subtraction. This is now the third paragraph of the section.

======================================================================

---Section 3.3, 3rd paragraph: "The three dimensional power spectrum cube can next be averaged in annuli to form..." For readers who may not be accustomed to P(kperp, kpara) spectra, it would be good to be more specific here. (E.g., annuli oriented in which direction?)

This is now clarified as the annuli of constant (kperp, kpar), (i.e. orthogonal to the kpar axis).

======================================================================

---In all kperp-kpara plots: The units "ns" and "lambda" are given, but it's never stated what quantities (i.e., "delay" and "baseline length", respectively) are plotted.

We have added a description of these axes in the penultimate paragraph of Section 3.3 (and in the caption of Figure 2).

======================================================================

---I don't think "KGS" is ever defined.

It is now spelled out in a footnote when we introduce the catalog.

======================================================================

---Just before Equation 6. "Pixel" is a bit of a confusing term here. Perhaps something like "kperp-kpara cell" might be more appropriate?

This has been changed.

======================================================================

---An inconsistency in citation style. Why is "J. L. B. Line" always given his initials while everyone else is cited by last name only?

Our understanding is that unpublished references should include the initials, while published references do not (http://journals.aas.org/authors/references.html#Unpublished). However, when double checking we noticed a couple unpublished references that were missing the initials, and have now added them.

======================================================================

---Penultimate paragraph of Section 4.4. What does "total residual power" mean? Can we be more precise? Is it the power integrated over the whole kperp-kpara plane? If so, the relevant k scales of integration need to be specified.

======================================================================

---Last paragraph of Section 4.4. I am having trouble understanding the sentence "The top panel shows the model power with the diffuse subtracted from the model power without". Can we rephrase? Also, I'm a little confused by what "model power with the diffuse subtracted" means. Isn't the diffuse power "added" to the model on top of the point sources?

This was worded in a very confusing way. The sentence now reads: “The top panel shows our point source foreground model power spectrum minus the model power spectrum when including diffuse.”

======================================================================

---Figure 8 caption: I don't understand the meaning of the parenthetical remark "(positive difference)".

This sentence had a lot of words to orient the reader between the color scheme corresponding to positive/negative, and which power spectrum was subtracted from which. We have broken it up into two sentences to be more clear.

======================================================================

---Figure 8 caption (but also in the text): is it not a bit optimistic to say that the diffuse modeling "shows promise" just because 90% of power is removed? 90% sounds impressive if we think in linear terms, but on a logarithmic scale (which is what counts), it's just one order of magnitude out of many.

We have removed the subjective language.

======================================================================

---Final paragraph of the paper. It's not quite true that imaging is necessary for cross-correlation. One could also take the images from other surveys and use them to predict visibilities, allowing for a cross-correlation in visibility space.

While this is technically true (and interesting), it does not avoid the challenges inherent in imaging. In order to achieve the visibility correlation, one would need to simulate the measured visibilities with their phase to high accuracy. In the literature we often lump all instrumental effects into the "A" matrix operating on a sky vector resulting in a set of measurements, assuming the calibration will fix all the small instrumental effects and make the real A match the model A. For a cross-correlation one would need to simulate with the real A, including phase corrections at the level needed for imaging. This can be sidestepped in power spectrum measurements because localization is irrelevant, but it is essential for cross-correlation, and the calibration uncertainties leaks back in in the difference between simulating with a model A and the real A. For all intents and purposes, cross-correlating in visibility space would still be an imaging analysis. There is actually a paper in the works (M.F. Morales et al) which will very carefully explore the definition and trade-offs of imaging analysis.

### 2016-08-04 referee_response.txt
Addressing more referee major comments

@@
 
+Yes, this is done to reduce data volume. We have added a sentence explaining this, and pointing out that it does not affect our sensitivity.
+
 ======================================================================
@@
 Is the separate fit a desire to avoid the near-degeneracy that results when A_i,1 and A_i,2 are small?
+
+That’s essentially it.
+We found that if we don’t first subtract the polynomial fit, our reflection fits were dominated by the low order terms, and the results did not make physical sense.
+Even though the degeneracy should be low (the reflection ripple is quite fine compared to other parameters), the relatively huge amount of power in the polynomial terms was completely obscuring the reflection fits.
+We have added a sentence to this effect in the text.
 
@@
 Can the authors explicitly clarify this?
+
+This effect is distinct from other wedge features discussed in the literature, and we have added a paragraph (3rd paragraph of Sec 4.2) pointing this out.
+The main difference is that this effect is due to the computational limits of the analysis itself, whereas other effects are inherent in the data.
+In the specific case of Hazelton et al.
+(2013), the effect is due to multiple baselines migrating in and out of uv cells, and the effective weighting of a given cell is frequency dependent.
+While the exact mixing would be dependent on the gridding kernel used, it would still exist in the limit of infinitely precise models because the frequency dependent weighting is due to the inherent chromaticity of the instrument.
 
@@
 ---Figure 15. Why does the FHD + eppsilon pipeline not go to as high k as RTS + CHIPS? Is there some limitation that prevents the highest k regions from being explored?
+
+This is simply due to the frequency averaging FHD+eppsilon does at the gridding step, which RTS+CHIPS does not do. This is now explained in the caption of Fig. 15.
 

### 2016-08-04 ms.tex
Addressing more referee major comments

@@
 a frequency resolution of 160 kHz. 
+\textbf{This is done to reduce the data volume, and has little impact on our results because
+our sensitivity to the EoR is extremely low at the corresponding line-of-sight $k$ modes
+\citep{Beardsley:2013}}
 
@@
 The exception is the second $k_{||}$ bin, which has slightly lower noise than the rest of the 
-$k_{||}$ modes. This is a result of the Lomb-Scargle periodogram interacting with the
-Blackman-Harris window function we apply to the data. In the case of $k_{||}=0$
-(shown as the bottom bin on the log plot), the
-cosine term carries all the information and has a noise level $\sqrt{2}$ lower than any other
-sine or cosine term individually. The first non-zero $k_{||}$ mode is highly covariant with the 
-bottom bin due to the window function. Therefore the noise on this mode's cosine term is 
-lower than other higher order cosines. With the added contribution from the sine term, this
-mode contains the lowest level of noise.
+$k_{||}$ modes. 
+As explained in Hazelton et al. (in prep.) this is a result of the Lomb-Scargle periodogram 
+interacting with the Blackman-Harris window function we apply to the data. Most of the bins 
+have the noise equally distributed between cosine and sine terms, with the exception of the 
+$k_{||}=0$ bin where the cosine term carries all the information. Due to the correlations 
+introduced by the Blackman-Harris window function the first non-zero $k_{||}$ mode is highly 
+covariant with the bottom bin ? therefore the noise on this mode's cosine term is lower than 
+other higher order cosines.
 }
@@
 The reflection coefficient, $R_{i,0}$ is allowed to be complex, while the reflection delay, 
-$\tau_i$ is real. After fitting for all other parameters, we fit for the reflection mode. This is 
+$\tau_i$ is real. After fitting for all other parameters, we fit for the reflection mode. 
+\textbf{We found that if we did not first fit and remove the polynomial terms, our reflection
+fits would be dominated by the large power in the smooth structure, resulting in solutions that
+did not match physical reality.
+The reflection fitting is}
 done for antennas with suspected reflections, the most offensive of which is seen in the 
@@
 of integration.
+
+\textbf{This effect is distinct from more fundamental wedge effects 
+\citep[e.g.][]{Morales:2012, Hazelton:2013} in that it is a result of the computational limitation
+of the analysis. The primary contribution to the foreground mode mixing is due to
+the loss of information as each baseline samples a range of $(u,v)$ modes. On the other
+hand, the effect discussed here is due to small positional offsets in the gridding kernel
+and only exists after gridding.}
 
@@
 excise the coarse band harmonic lines, and so we see their strong effect where there are 
-gaps in the magenta lines. The most notable differences are the ability of the RTS$+$CHIPS pipe
+gaps in the magenta lines. 
+\textbf{The RTS$+$CHIPS pipeline accesses larger $k$ modes because the data is
+processed at 80~kHz, whereas the FHD$+$\eppsilon pipeline averages to 160~kHz when
+gridding.}
+The most notable differences are the ability of the RTS$+$CHIPS pipe
 to access lower $k$ modes, while the FHD$+$\eppsilon pipe suppresses more power before and

### 2016-08-04 referee_response.txt
Addressed the remainder of major referee comments. Just one more minor comment to go.

@@
 
+This is the median spectral index of sources based on studies below 1.4 GHz. We now mention this and cite the appropriate references.
+
 ======================================================================
@@
 ---Penultimate paragraph of Section 4.3. The authors find that using the two different foreground models gave different flux scales. Is there a sense in which the flux scale has converged?
+
+This is a bit subtle, but the flux scale difference is in the calibrated data, not in the model itself.
+The difference is quite small (part in 10^3 in mK^2 units), but gets amplified when we show straight difference plots like we use for the diffuse subtraction demonstration.
+KGS did not find a significant difference in flux scale of the catalog itself, but using a more complete sky model requires lower amplitude (and more accurate) gains to match the visibilities to the model.
+We have clarified this point in the text.
 
@@
 
+This observing campaign did not actually contain data from a +5 pointing, because that is the point that the EoR1 field has risen higher than EoR0 so we switch fields.
+We have removed the +5 pointing from the cartoon and explain in the caption.
+
 ======================================================================
@@
 Since the "+3" portion seems so tightly clustered and is only excluded from the analysis due to some consistent offset, might this be fixable by adjusting calibration parameters?
+
+While it may be possible to recover more pointings in future analysis, it is likely to require both improved calibration and foreground/instrument modeling.
+The window power statistic is robust against calibration, and the excess power we see in the N-S polarization at this pointing is likely due to bright large scale structure in our sidelobes (which are different in the two polarizations).
+We would need to properly model and remove this power in order to use this pointing.
+The potential to recover pointings is mentioned in Sec.
+5.1 (end of 2nd paragraph), and discussed more thoroughly in Sec.
+6.1.
 
@@
 
+This is a good point, but we feel the explanation is better suited for the pipeline section. In the penultimate paragraph of Section 3.3 we now go into more detail of the streaks seen in Fig 2.
+
 ======================================================================
@@
 ---Along the same lines as the previous point, might an accounting of covariances between different power spectrum cells also help here, perhaps allowing for decreased leakage?
+
+Indeed, and this is under development in the eppsilon pipeline. We now mention this at the same place as the previous point.
 
@@
 I'm curious as to the thinking here, particularly versus the alternative I've seen in the literature where a constant delay buffer is added to the horizon line.
+
+The cut in kpar and the increased wedge slope effectively achieve the same thing as the constant delay buffer.
+Our wedge slope is actually a bit more aggressive than one would get from the delay buffer because we saw leakage consistently above the “horizon” (previous 3 hour integrations were on the cusp of reaching the noise level to see this).
 
@@
 As an outsider, for example, I am curious as to whether there is more data "in the can" that is just waiting to be analyzed, or whether any new results will come from data taken once the MWA expansion is past its construction/commissioning phase.
+
+We have injected a paragraph (2nd to last of the paper) providing this information.
+There is plenty of data available, but real progress will be made through understanding the systematics discussed in the paper.
 

### 2016-08-04 ms.tex
Addressed the remainder of major referee comments. Just one more minor comment to go.

@@
 $k_{\perp}$. These are due to sparse $(u,v)$ sampling beyond the dense core of the MWA 
-(starting $\sim70\lambda$), and the foreground power mixing to high spectral 
-modes \citep{Bowman:2009}. 
+(starting $\sim70\lambda$), 
+\textbf{which results in non-uniform spectral sampling after gridding. This in turn
+causes foreground power to mix to high spectral modes} \citep{Bowman:2009}. 
+\textbf{The frequency dependent sampling creates a point spread function in the $k_{||}$
+for each $(u,v)$ cell. In principle covariance weighting along the frequency dimension
+may be able to mitigate this leakage \citep[e.g.][]{Liu:2011}, and an \eppsilon implementation 
+is under development.}
 \textbf{We provide axes more closely related to the measurements to assist in connecting
@@
 MRC matches or MRC-SUMSS matches. All other sources were given a spectral index of 
-$-0.8$. The spectral index was used to extrapolate the flux density from the catalog frequency to 
+$-0.8$, \textbf{the previously determined median spectral index of sources below 1.4 GHz
+\citep{Oort:1988, Hunstead:1991, DeBreuck:2000, Mauch:2003}.}
+The spectral index was used to extrapolate the flux density from the catalog frequency to 
 182 MHz, but a uniform spectral index of $-0.8$ is used within our band when forming 
@@
 for our two runs differed. In particular we saw the overall flux scale of the calibrated 
-visibilities was higher when using the full hierarchical catalog. In order to put both residual 
+visibilities was higher when using the full hierarchical catalog,
+\textbf{owing to a more complete sky model requiring lower amplitude gains to describe the data.}
+In order to put both residual 
 2D power spectra onto the same scale for comparison, we first divide each 
@@
 increments the pointing label by one, and the zenith pointing is defined as zero.
+\textbf{While a +5 pointing (and beyond) is possible with the MWA, this observing campaign
+did not contain any such data because we instead switched to the EoR1 field at that time.}
 \label{fig:pointing}
@@
 
+\textbf{Between 2013 and the time of writing, the MWA has collected over two thousand 
+hours of data targeting the EoR fields. These observations include the three designated sky 
+fields and two frequency bands. In addition, observations are underway to further 
+characterize the sources in the instrument sidelobes. The second phase of the MWA
+will be commissioned in the latter half of 2016, and will include two sets of highly redundant
+cores of antennas. This hybrid configuration will enable a unique opportunity to study
+the calibration techniques used in imaging and delay spectrum analyses, furthering
+our understanding of the systematics limiting our current results.}
+
 While the analysis presented here has not reached full potential, it represents the deepest power spectrum 

### 2016-08-04 ms.tex
Updated some references

@@
 and multiple polarization components.
-\textbf{E.}~Lenc, et al. (in review) demonstrated the presence of strong polarized large-scale structures 
+\textbf{\citet{Lenc:2016}} demonstrated the presence of strong polarized large-scale structures 
 in the EoR0 field at 154 MHz with varying Faraday depths. They observed rotations in the
@@
 polarization components to the model will improve this subtraction even further.
-As \textbf{E.}~Lenc, et al. 2016 (in review) demonstrated, substantial polarized diffuse structure
+As \textbf{\citet{Lenc:2016}} demonstrated, substantial polarized diffuse structure
 exists in the EoR0 field. The contributions to Stokes Q and U depend on the ionospheric

### 2016-08-05 referee_response.txt
Finished addressing referee comments

@@
 
-Yes, this is done to reduce data volume. We have added a sentence explaining this, and pointing out that it does not affect our sensitivity.
+Yes, this is done to reduce data volume.
+We have added a sentence explaining this, and pointing out that it does not affect our sensitivity.
+(It does however, effect the kpar modes we access, which is the cause of the different k modes shown for FHD+eppsilon and RTS+CHIPS that you point out below.)
 
@@
 
+First, the 90% number turned out to be not quite right.
+When we returned to our calculation to answer this question, we realized we had mistakenly included the number from another test we did after “locking in” the analysis for this paper, where we included a Stokes Q model.
+The correct number should have been 70%, and has been updated in the paper (in all places it is mentioned).
+
+To answer the question at hand, the total residual power is calculated by squaring and summing the residual image cube.
+This is a naturally weighted image, so the weighting is exactly the inverse of our error figure (now Fig.
+2).
+While we include all scales measured by the instrument, it is dominated by the large perpendicular scales.
+This is now described in the paper.
+
 ======================================================================

### 2016-08-05 ms.tex
Finished addressing referee comments

@@
 introduced by the Blackman-Harris window function the first non-zero $k_{||}$ mode is highly 
-covariant with the bottom bin ? therefore the noise on this mode's cosine term is lower than 
+covariant with the bottom bin -- therefore the noise on this mode's cosine term is lower than 
 other higher order cosines.
@@
 than 50 wavelengths for calibration purposes. However, we add the diffuse model and 
-unmask short baselines when performing foreground subtraction, and have seen a 90\% 
-decrease in total residual power -- a strong indication that our diffuse model improves our 
+unmask short baselines when performing foreground subtraction.
+\textbf{We compare the total residual power in the images by squaring and summing
+the residual image cube from before and after the diffuse subtraction. 
+This includes all scales measured by the instrument, but because the image cubes are
+naturally weighted, the $\mathbf{k}$ space weighting is the inverse of 
+Figure~\ref{fig:example_2derror}, meaning $k_\perp \lesssim 0.05$ h Mpc$^{-1}$ dominates the
+average. We saw a 70\% reduction in residual power when including our diffuse model}
+ -- a strong indication that our diffuse model improves our 
 subtraction. Future iterations will incorporate the model in calibration and gradually improve 
@@
 While this first attempt at a diffuse model was rudimentary, it 
-\textbf{successfully removed 90\% of the residual power. }
+\textbf{successfully removed 70\% of the residual power. }
 \label{fig:diffuse_diff}
@@
 and represented only the Stokes I polarization. Nevertheless subtracting this model removed
-90\% of the residual power in the foreground wedge. Adding a spectral index and multiple
+70\% of the residual power in the foreground wedge. Adding a spectral index and multiple
 polarization components to the model will improve this subtraction even further.
@@
 cores of antennas. This hybrid configuration will enable a unique opportunity to study
-the calibration techniques used in imaging and delay spectrum analyses, furthering
-our understanding of the systematics limiting our current results.}
+the calibration techniques used in imaging and delay spectrum analyses, providing
+another view of the systematics limiting our current results.}
 

### 2016-08-05 ms.tex
Couple of minor wording tweaks from JDB

@@
 \textbf{
-Error level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
+Uncertainty level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
 short baseline length (low $k_{\perp}$) due to the dense MWA core. The array is more
@@
 
-\textbf{Figure~\ref{fig:example_2derror} shows the error level corresponding to the two 
-dimensional power spectrum in Figure~\ref{fig:example_ps}. These errors
+\textbf{Figure~\ref{fig:example_2derror} shows the uncertainty level corresponding to the two 
+dimensional power spectrum in Figure~\ref{fig:example_ps}. These levels
 are found by propagating noise measured from calibrated visibilities through the entire
@@
 As the $(u,v)$ density of the array decreases at longer baselines, the noise increases.
-The noise is mostly constant across $k_{||}$ because the Fourier transform distributes
-the noise in frequency to all modes equally \citep{Morales:2004}.
+The noise is mostly constant across $k_{||}$ because the thermal noise amplitude is
+relatively constant over frequency and the Fourier transform distributes the noise power
+across all modes \citep{Morales:2004}.
 The exception is the second $k_{||}$ bin, which has slightly lower noise than the rest of the 

### 2016-08-08 ms.tex
Small changes as requested by MFM

@@
 \affilauthorlist{
-A.~P.~Beardsley\affils{ASU,email},
+A.~P.~Beardsley\affils{ASU,UW,email},
 B.~J.~Hazelton\affils{UW,UWeSci},
@@
 Radio Telescope, \citealt{Paciga:2013}), LOFAR (LOw Frequency Array\footnote{http://
-www.lofar.org}, \citealt{vanHaarlem:2013, Yatawatta:2013}), PAPER (Precision Array for Probing the Epoch of 
+www.lofar.org}, \citealt{vanHaarlem:2013, Yatawatta:2013}), PAPER (\textbf{Donald C. Backer} Precision Array for Probing the Epoch of 
 Reionization\footnote{http://eor.berkeley.edu}, \citealt{Parsons:2010}), and the MWA 
@@
 $k_{||}$ modes. 
-As explained in Hazelton et al. (in prep.) this is a result of the Lomb-Scargle periodogram 
+As explained in B.~J.~Hazelton et al. (in prep.) this is a result of the Lomb-Scargle periodogram 
 interacting with the Blackman-Harris window function we apply to the data. Most of the bins 
@@
 visibilities was higher when using the full hierarchical catalog,
-\textbf{owing to a more complete sky model requiring lower amplitude gains to describe the data.}
+\textbf{owing to a more complete sky model requiring lower amplitude gains to describe the data. 
+This difference is on order a part in $10^3$ in mK$^2$ units, but is largely amplified
+when observing the difference in the power spectra.}
 In order to put both residual 

### 2016-08-12 referee_response.txt
Couple of minor wording tweaks from JDB
Added intro to referee response and pdf

@@
+Dear Editor and Referee,
+
+We would like to thank the referee for providing a helpful review of our manuscript “First Season MWA EoR Power Spectrum Results at Redshift 7” by myself and others (Submission AAS01756).
+Below we provide responses to all comments from the referee.
+The most significant changes are:
+
+- A new figure showing the 2D noise levels to correspond to the 2D power plots we show (Fig. 2).
+- A correction to the residual power improvement when using a diffuse model (discussed below).
+- Updated references.
+- Many expanded explanations on items pointed out by the referee.
+
+We feel the changes have strengthened the article and made it more accessible to the intended audience.
+
+On behalf of the coauthors,
+
+Adam Beardsley
+Arizona State University
+
+======================================================================
+Specific responses
+======================================================================
+
 Major comments
@@
 This is a naturally weighted image, so the weighting is exactly the inverse of our error figure (now Fig.
-2).
+3).
 While we include all scales measured by the instrument, it is dominated by the large perpendicular scales.

### 2016-08-22 ms.tex
Removed bold faced changes in prep for arxiv submission.

@@
 Radio Telescope, \citealt{Paciga:2013}), LOFAR (LOw Frequency Array\footnote{http://
-www.lofar.org}, \citealt{vanHaarlem:2013, Yatawatta:2013}), PAPER (\textbf{Donald C. Backer} Precision Array for Probing the Epoch of 
+www.lofar.org}, \citealt{vanHaarlem:2013, Yatawatta:2013}), PAPER (Donald C. Backer Precision Array for Probing the Epoch of 
 Reionization\footnote{http://eor.berkeley.edu}, \citealt{Parsons:2010}), and the MWA 
@@
 cm EoR signal \citep{Ali:2015, Dillon:2014, Parsons:2014, Jacobs:2015, Paciga:2013}.
-\textbf{Furthermore,} \citet{Pober:2015} \textbf{and \citet{Greig:2016} were} able to place constraints on physical reionization models. 
+Furthermore, \citet{Pober:2015} and \citet{Greig:2016} were able to place constraints on physical reionization models. 
 However, much work is to be done to understand the data produced by these arrays. 
@@
 several analysis pipelines are under active development 
-\textbf{to exploit this foreground isolation}
+to exploit this foreground isolation
 \citep[e.g. B.~J.~Hazelton et al. 2016, in 
@@
 as a ``golden data set'', which is used to build analysis tools and compare early results 
-\textbf{\cite[e.g.][]{Jacobs:2016, Trott:2016, Pober:2016, Dillon:2015}.} All 
+\cite[e.g.][]{Jacobs:2016, Trott:2016, Pober:2016, Dillon:2015}. All 
 techniques demonstrated here will use this golden data set. In Section~\ref{sec:deep} we 
@@
 not seen evidence of these systematics through simulations and direct propagation of
-our noise \citep[\textbf{B.~J.}~Hazelton et al. 2016, in prep.]{Barry:2016}.
+our noise \citep[B.~J.~Hazelton et al. 2016, in prep.]{Barry:2016}.
 
@@
 respectively,
-\textbf{and $V_{ij}(\nu)$ is the true visibility which we aim to recover through calibration.}
+and $V_{ij}(\nu)$ is the true visibility which we aim to recover through calibration.
 Because we are treating polarizations independently, we allow the antenna 
@@
 direction). The visibilities are gridded using the primary beam as the gridding kernel, placing 
-the data in the \textbf{``holographic frame,"} which has been shown to be the optimal \textbf{weighting scheme} for 
+the data in the ``holographic frame," which has been shown to be the optimal weighting scheme for 
 combining images in the sense that it preserves all information for parameter estimation 
@@
 a frequency resolution of 160 kHz. 
-\textbf{This is done to reduce the data volume, and has little impact on our results because
+This is done to reduce the data volume, and has little impact on our results because
 our sensitivity to the EoR is extremely low at the corresponding line-of-sight $k$ modes
-\citep{Beardsley:2013}}
+\citep{Beardsley:2013}.
 
@@
 
-\textbf{The pipeline as described up to this point is applied to both the calibrated data
+The pipeline as described up to this point is applied to both the calibrated data
 and the foreground model. At this point we subtract the model from the data to form
 residual data as well. All three sets of data (dirty, model, and residual) are carried through 
-the remaining steps to form corresponding power spectra.}
+the remaining steps to form corresponding power spectra.
 
@@
 dimensional power spectrum cube can next be averaged in annuli 
-\textbf{of constant $k_{\perp}$ and $k_{||}$ (i.e. orthogonal to the $k_{||}$ axis)}
+of constant $k_{\perp}$ and $k_{||}$ (i.e. orthogonal to the $k_{||}$ axis)
 to form two dimensional 
@@
 beyond the dense core of the MWA.
-\textbf{The right axis shows the delay (Fourier dual to frequency) corresponding to the 
+The right axis shows the delay (Fourier dual to frequency) corresponding to the 
 $k_||$ axis, and the top axis shows the baseline length (in wavelengths) corresponding
-to the $k_{\perp}$ axis.}
+to the $k_{\perp}$ axis.
 \label{fig:example_ps}
@@
 (starting $\sim70\lambda$), 
-\textbf{which results in non-uniform spectral sampling after gridding. This in turn
-causes foreground power to mix to high spectral modes} \citep{Bowman:2009}. 
-\textbf{The frequency dependent sampling creates a point spread function in the $k_{||}$
+which results in non-uniform spectral sampling after gridding. This in turn
+causes foreground power to mix to high spectral modes \citep{Bowman:2009}. 
+The frequency dependent sampling creates a point spread function in the $k_{||}$
 for each $(u,v)$ cell. In principle covariance weighting along the frequency dimension
 may be able to mitigate this leakage \citep[e.g.][]{Liu:2011}, and an \eppsilon implementation 
-is under development.}
-\textbf{We provide axes more closely related to the measurements to assist in connecting
+is under development.
+We provide axes more closely related to the measurements to assist in connecting
 these instrumental effects. The right axis shows delay (Fourier dual to frequency), and the
-top axis shows baseline length measured in wavelengths.}
+top axis shows baseline length measured in wavelengths.
 Between the coarse band lines and to the left of the vertical streaks we see regions 
@@
 \caption{
-\textbf{
 Uncertainty level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
@@
 Lomb-Scargle periodogram with the Blackman-Harris window function applied to the data.
-}
 \label{fig:example_2derror}
@@
 
-\textbf{Figure~\ref{fig:example_2derror} shows the uncertainty level corresponding to the two 
+Figure~\ref{fig:example_2derror} shows the uncertainty level corresponding to the two 
 dimensional power spectrum in Figure~\ref{fig:example_ps}. These levels
@@
 other higher order cosines.
-}
 
@@
 $\tau_i$ is real. After fitting for all other parameters, we fit for the reflection mode. 
-\textbf{We found that if we did not first fit and remove the polynomial terms, our reflection
+We found that if we did not first fit and remove the polynomial terms, our reflection
 fits would be dominated by the large power in the smooth structure, resulting in solutions that
 did not match physical reality.
-The reflection fitting is}
+The reflection fitting is
 done for antennas with suspected reflections, the most offensive of which is seen in the 
@@
 
-\textbf{This effect is distinct from more fundamental wedge effects 
+This effect is distinct from more fundamental wedge effects 
 \citep[e.g.][]{Morales:2012, Hazelton:2013} in that it is a result of the computational limitation
@@
 hand, the effect discussed here is due to small positional offsets in the gridding kernel
-and only exists after gridding.}
+and only exists after gridding.
 
@@
 to select reliable detections from the full deconvolution FHD mode, culminating in the KGS 
-catalog\footnote{\textbf{KGS is an abbreviation of KATALOGSS, the KDD (Knowledge 
+catalog\footnote{KGS is an abbreviation of KATALOGSS, the KDD (Knowledge 
 Discovery in Databases) Astrometry, Trueness, and Apparent Luminosity of Galaxies in 
-Snapshot Surveys}}. The work here uses an early iteration of the KGS catalog that was available at the 
+Snapshot Surveys}. The work here uses an early iteration of the KGS catalog that was available at the 
 time of analysis.
@@
 catalog pulling from our early KGS catalog, the MWA Commissioning Survey\footnote{The 
-more complete GLEAM Survey \citep[][\textbf{N.}~Hurley-Walker et al., in review]
+more complete GLEAM Survey \citep[][N.~Hurley-Walker et al., in review]
 {Wayth:2015} was not available at the time of analysis.} \citep[MWACS, ][]
@@
 MRC matches or MRC-SUMSS matches. All other sources were given a spectral index of 
-$-0.8$, \textbf{the previously determined median spectral index of sources below 1.4 GHz
-\citep{Oort:1988, Hunstead:1991, DeBreuck:2000, Mauch:2003}.}
+$-0.8$, the previously determined median spectral index of sources below 1.4 GHz
+\citep{Oort:1988, Hunstead:1991, DeBreuck:2000, Mauch:2003}.
 The spectral index was used to extrapolate the flux density from the catalog frequency to 
@@
 visibilities was higher when using the full hierarchical catalog,
-\textbf{owing to a more complete sky model requiring lower amplitude gains to describe the data. 
+owing to a more complete sky model requiring lower amplitude gains to describe the data. 
 This difference is on order a part in $10^3$ in mK$^2$ units, but is largely amplified
-when observing the difference in the power spectra.}
+when observing the difference in the power spectra.
 In order to put both residual 
 2D power spectra onto the same scale for comparison, we first divide each 
-\textbf{$(k_{\perp},k_{||})$ cell}
+$(k_{\perp},k_{||})$ cell
 by the 
@@
 earth to improve the point spread function (PSF) of the instrument. This integrating of 
-images is done \textbf{with uniform weighted data} to minimize the effect of double instrument 
+images is done with uniform weighted data to minimize the effect of double instrument 
 convolution (once when the data are taken, again when we use the output as a model). We 
@@
 and multiple polarization components.
-\textbf{\citet{Lenc:2016}} demonstrated the presence of strong polarized large-scale structures 
+\citet{Lenc:2016} demonstrated the presence of strong polarized large-scale structures 
 in the EoR0 field at 154 MHz with varying Faraday depths. They observed rotations in the
@@
 unmask short baselines when performing foreground subtraction.
-\textbf{We compare the total residual power in the images by squaring and summing
+We compare the total residual power in the images by squaring and summing
 the residual image cube from before and after the diffuse subtraction. 
@@
 Figure~\ref{fig:example_2derror}, meaning $k_\perp \lesssim 0.05$ h Mpc$^{-1}$ dominates the
-average. We saw a 70\% reduction in residual power when including our diffuse model}
+average. We saw a 70\% reduction in residual power when including our diffuse model
  -- a strong indication that our diffuse model improves our 
@@
 subtraction in Figure~\ref{fig:diffuse_diff}. 
-The top panel shows \textbf{our point source foreground model power spectrum
-minus the model power spectrum when including diffuse}. 
+The top panel shows our point source foreground model power spectrum
+minus the model power spectrum when including diffuse. 
 Because our diffuse model added power to the full foreground model, the entire plot is
@@
 the diffuse model, so the dirty power spectra are identical. 
-\textbf{In the top panel the model power spectrum difference is almost entirely negative 
+In the top panel the model power spectrum difference is almost entirely negative 
 (red), indicating that the diffuse model added a large amount of power to the foreground 
 model. The bottom panel shows the residual power spectrum difference is positive in the 
-wedge (blue), demonstrating a successful subtraction.}
+wedge (blue), demonstrating a successful subtraction.
 While this first attempt at a diffuse model was rudimentary, it 
-\textbf{successfully removed 70\% of the residual power. }
+successfully removed 70\% of the residual power. 
 \label{fig:diffuse_diff}
@@
 increments the pointing label by one, and the zenith pointing is defined as zero.
-\textbf{While a +5 pointing (and beyond) is possible with the MWA, this observing campaign
-did not contain any such data because we instead switched to the EoR1 field at that time.}
+While a +5 pointing (and beyond) is possible with the MWA, this observing campaign
+did not contain any such data because we instead switched to the EoR1 field at that time.
 \label{fig:pointing}
@@
 gaps in the magenta lines. 
-\textbf{The RTS$+$CHIPS pipeline accesses larger $k$ modes because the data is
+The RTS$+$CHIPS pipeline accesses larger $k$ modes because the data is
 processed at 80~kHz, whereas the FHD$+$\eppsilon pipeline averages to 160~kHz when
-gridding.}
+gridding.
 The most notable differences are the ability of the RTS$+$CHIPS pipe
@@
 polarization components to the model will improve this subtraction even further.
-As \textbf{\citet{Lenc:2016}} demonstrated, substantial polarized diffuse structure
+As \citet{Lenc:2016} demonstrated, substantial polarized diffuse structure
 exists in the EoR0 field. The contributions to Stokes Q and U depend on the ionospheric
@@
 response in situ using the ORBCOMM satellite constellation \citep{Neben:2015}, and 
-drone-flown calibrator sources (\textbf{D.~C.}~Jacobs, et al. in prep). The latter method is similar to
+drone-flown calibrator sources (D.~C.~Jacobs, et al. in prep). The latter method is similar to
 the strategy \citet{Virone:2014} used to verify SKA beam patterns.
@@
 
-\textbf{Between 2013 and the time of writing, the MWA has collected over two thousand 
+Between 2013 and the time of writing, the MWA has collected over two thousand 
 hours of data targeting the EoR fields. These observations include the three designated sky 
@@
 the calibration techniques used in imaging and delay spectrum analyses, providing
-another view of the systematics limiting our current results.}
+another view of the systematics limiting our current results.
 
